### 2020-10-05 BEMSSystemLevelRequirements.tex
Removed pdf and added tex file for 497 deliverable

% !TEX TS-program = pdflatex
% !TEX encoding = UTF-8 Unicode

% This is a simple template for a LaTeX document using the "article" class.
% See "book", "report", "letter" for other types of document.

\documentclass[12pt]{article} % use larger type; default would be 10pt

\usepackage[utf8]{inputenc} % set input encoding (not needed with XeLaTeX)

%%%%\usepackage[document]{ragged2e}

%%% Examples of Article customizations
% These packages are optional, depending on whether you want the features they provide.
% See the LaTeX Companion or other references for full information.

%%% PAGE DIMENSIONS
\usepackage{geometry} % to change the page dimensions
\geometry{letterpaper} % or letterpaper (US) or a5paper or....
\geometry{margin=1in} % for example, change the margins to 2 inches all round
% \geometry{landscape} % set up the page for landscape
%   read geometry.pdf for detailed page layout information

\usepackage{graphicx} % support the \includegraphics command and options
\graphicspath{
{figs/ipe/}
}
% \usepackage[parfill]{parskip} % Activate to begin paragraphs with an empty line rather than an indent

%%% PACKAGES
\usepackage{booktabs} % for much better looking tables
\usepackage{array} % for better arrays (eg matrices) in maths
\usepackage{paralist} % very flexible & customisable lists (eg. enumerate/itemize, etc.)
\usepackage{epstopdf}
\usepackage{float}
\epstopdfsetup{suffix = {}}
\usepackage{siunitx}
\sisetup{unitsep = \cdot}
\usepackage{verbatim} % adds environment for commenting out blocks of text & for better verbatim
\usepackage{subfig} % make it possible to include more than one captioned figure/table in a single float
% These packages are all incorporated in the memoir class to one degree or another...

\usepackage{caption}        %Allows modification of captions
% \usepackage{indentfirst}    %Allows for indenting first paragraphs

\usepackage{hyperref}
\usepackage{todonotes}

%%% HEADERS & FOOTERS
\usepackage{fancyhdr} % This should be set AFTER setting up the page geometry
\pagestyle{fancy} % options: empty , plain , fancy
\renewcommand{\headrulewidth}{0pt} % customize the layout...
\lhead{}\chead{}\rhead{}
\lfoot{}\cfoot{\thepage}\rfoot{}

%%% SECTION TITLE APPEARANCE
\usepackage{sectsty}
\usepackage{tikz}
\usepackage[framemethod=TikZ]{mdframed}
\usepackage{enumerate}
\usepackage[shortlabels]{enumitem}
\allsectionsfont{\sffamily\mdseries\upshape} % (See the fntguide.pdf for font help)
% (This matches ConTeXt defaults)

%%% ToC (table of contents) APPEARANCE
\usepackage[nottoc,notlof,notlot]{tocbibind} % Put the bibliography in the ToC
\usepackage[titles,subfigure]{tocloft} % Alter the style of the Table of Contents
\renewcommand{\cftsecfont}{\rmfamily\mdseries\upshape}
\renewcommand{\cftsecpagefont}{\rmfamily\mdseries\upshape} % No bold!

%%% END Article customizations

%%% The "real" document content comes below...

\title{Development of an Intelligent Building Energy Management Platform}
\author{Brian Lauer \and Elliot Watkins \and \underline{Advisor}: Dr. Suruz Miah
}
%\date{} % Activate to display a given date or no date (if empty),
         % otherwise the current date is printed

% \setlength{\parindent}{4em} % this should indent paragraphs

\begin{document}
\maketitle

\section{Project Description}
% Significance of the project 
The Internet of Things is a large network of embedded devices like sensors, wearables, and appliances capable of receiving control commands and reporting data over the Internet. Many industries take advantage of this infrastructure to improve process flow and efficiency. One of these industries is the commercial and industrial sector which often employ building automation or management systems to help better manage processes or devices in a building like air conditioning systems, lights or industrial machines. Technological advancements have allowed devices to become connected to a building network through communication protocols like WiFi, Ethernet, Modbus, or BACnet which enables them to be more easily controlled from a central system.
\medbreak\noindent
Our overall goal will be to create a platform in which users can login and access devices connected to a building's energy supply. This allow the user to closely monitor energy usage throughout a commercial or residential building. Additionally, the user will be able to control devices connected to the platform, allowing precise control over the building's energy use.
\medbreak\noindent
The minimum viable product of this project will be to connect to 1 or 2 devices via the the platform and control them. If time allows, we would like to have devices connected to wifi automatically connect to the platform for the user's convenience.

\section{System Architecture}

\subsection{Inputs}
This project will include input from users, smart power meter, devices, and a weather service. Users will be able to adjust the operation of a device (turn up the temperature of an AC unit, for instance) or turn a device on or off completely. Smart power meters will be able to connect the platform and give real-time updates of the building's overall power usage. We would also like to look into meters for individual appliances like AC units and furnaces. The connected devices themselves will continually communicate to the web server their current status. Finally, our platform will regularly receive weather updates from a weather services and warn the user about potential energy loss due to storms.

\subsection{BEMS Core}
A high level view of the operation of the software platform is shown in Figure \ref{fig:functionalBlockDiagram}. Incorporated into the platform will be a web server developed in Python with the Flask web framework. All external and internal HTTP (Hyper Text Transfer Protocol) requests will be processed through this web server in order to store device or user information in the SQLite database. An external request is defined as a request made by a user or device to, for example, update information in the database with a series of SQLite queries. Internal requests are made by other entities or processes running in parallel on the platform including software agents. Similar to BEMOSS, these agents will help to communicate with various devices supported by the platform like broadcasting a discovery service, sending control commands to devices, and regularly requesting data from devices. The platform will be developed and deployed on a Linux machine to encourage support for deployment on SBCs (Single Board Computers) like the Raspberry Pi or BeagleBone Blue to be conveniently stored in a secure location of a building or home like a server cabinet for instance.
\begin{figure}[H]
    \centering
    \includegraphics[scale=0.35]{figs/highLevelArchitecture.pdf}
    \caption{Caption}
    \label{fig:my_label}
\end{figure}
\medbreak\noindent
The SQLite database will be designed to store device information like the device IP address, MAC address, manufacturer name, and device name. A feature will be implemented to allow for customizing the device name. For example, a WeMo Switch connected to the building or home LAN (Local Area Network) could be renamed to "Lamp" or "Light". Secondly, a feature will be added to specify the room or location of each device within the building or home. This will aid any users of the software in distinguishing devices from each other. 
\medbreak\noindent
% Talk about time series feature
Functionality will be avilable in the final version of the platform to store time-series data like on/off status and power data in a database using Apache Cassandra, an open-source NoSQL database management system. This offers a convenient way to log data from device readings in real time. In the future, machine learning algorithms can be used alongside this database to help optimize energy usage.
\medbreak\noindent
A further addition to the software will be added in the form of support for Simscape models, an addon for Simulink to model electromechanical systems. Matlab scripts will be associated with each of these models to collect power data from various electrical models created with Simscape. Using TCP/IP, Matlab will send data from the associated models over the network to the platform to be stored in the Cassandra database.

\begin{figure}[H]
    \centering
    \includegraphics[scale=0.6]{figs/functionalBlockDiagram}
    \caption{High-level Functional Block Diagram}
    \label{fig:functionalBlockDiagram}
\end{figure}
\subsection{Outputs}
The BEMS Core will output all data from devices, smart power meter, and weather updates to the web server. The user will then be able to peruse all available data on any smart device connected to the network.
\section{End-Use Requirements}
By May 2021, users will be able to: remotely turn control devices and monitor energy usage by individual devices.
\medbreak\noindent
Some devices will have more complicated operation than on and off. For example, we plan to add a driver for a beaglebone blue that will include support for the motor drivers. This will require a speed control algorithm capable of precisely regulating motor speed through PWM.
\medbreak\noindent
Since we are writing most of the code in Python, we will use Python's matplotlib module to graph energy usage for a given time period. With the database we plan to implement, we could gather data for a user-defined time period and plot energy usage for that time period. For example, if the user selects a Wemo switch and inputs 10/3/2020 - 10/5/2020, a graph will be generated showing how much energy in kilowatt-hrs that Wemo switch has used.

By May, 2021, we want to have a modular design for the platform that will allow users to add drivers for new devices as they are developed. Once a new device driver is added, the platform will be able to interact with it how the user wants.

\section{Modes of Operation}
To operate properly, the software must include three main modes of operation:
\indent
\begin{enumerate}[leftmargin=*,start=0,label={\bfseries Mode~\#\arabic*:}]
    \item Device discovery mode: the software will be able to discover supported devices automatically upon a device joining the network. To reduce network traffic, the settings page will allow specifying which devices can be discovered.
    \item Manual device control mode: alter the state of devices manually through an easy to use interface in the web UI or through a command line based application accessible through the UI.
    \item Power reporting mode: a page will be available in the UI for reporting the overall power consumption of the building as well as individual device power consumption (if available). 
\end{enumerate}

\end{document}

### 2020-10-05 systemLevelFunctionalRequirements.tex
Updated system level functional requirements
Made a few small changes to systemLevelFunctionalRequirements.tex

--- 2020-10-05 BEMSSystemLevelRequirements.tex
@@
 Our overall goal will be to create a platform in which users can login and access devices connected to a building's energy supply.
-This allow the user to closely monitor energy usage throughout a commercial or residential building.
+This will allow the user to closely monitor energy usage throughout a commercial or residential building.
 Additionally, the user will be able to control devices connected to the platform, allowing precise control over the building's energy use.
 \medbreak\noindent
-The minimum viable product of this project will be to connect to 1 or 2 devices via the the platform and control them.
-If time allows, we would like to have devices connected to wifi automatically connect to the platform for the user's convenience.
+As shown in Figure \ref{fig:highLevelArchitecture}, the minimum viable product of this project will be to connect to 1 to 3 devices via the the platform and control them.
+If time allows, we would like to have devices connect to WiFi automatically for the user's convenience.
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[scale=0.35]{figs/highLevelArchitecture.pdf}
+    \caption{High Level Architecture of the Proposed System}
+    \label{fig:highLevelArchitecture}
+\end{figure}
 
@@
 We would also like to look into meters for individual appliances like AC units and furnaces.
-The connected devices themselves will continually communicate to the web server their current status.
-Finally, our platform will regularly receive weather updates from a weather services and warn the user about potential energy loss due to storms.
+The connected devices themselves will communicate to the web server their current status when needed.
+Finally, our platform will regularly receive weather updates from a weather service and warn the user about potential energy loss due to storms.
 
@@
     \centering
-    \includegraphics[scale=0.35]{figs/highLevelArchitecture.pdf}
-    \caption{Caption}
-    \label{fig:my_label}
+    \includegraphics[scale=0.4]{figs/functionalBlockDiagram}
+    \caption{High-level Functional Block Diagram}
+    \label{fig:functionalBlockDiagram}
 \end{figure}
@@
 % Talk about time series feature
-Functionality will be avilable in the final version of the platform to store time-series data like on/off status and power data in a database using Apache Cassandra, an open-source NoSQL database management system.
+Functionality will be available in the final version of the platform to store time-series data like on/off status and power data in a database using Apache Cassandra, an open-source NoSQL database management system.
 This offers a convenient way to log data from device readings in real time.
@@
 
-\begin{figure}[H]
-    \centering
-    \includegraphics[scale=0.6]{figs/functionalBlockDiagram}
-    \caption{High-level Functional Block Diagram}
-    \label{fig:functionalBlockDiagram}
-\end{figure}
 \subsection{Outputs}
@@
 The user will then be able to peruse all available data on any smart device connected to the network.
+
+\section{Modes of Operation}
+To operate properly, the software must include three main modes of operation:
+\indent
+\begin{enumerate}[leftmargin=*,start=0,label={\bfseries Mode~\#\arabic*:}]
+    \item Device discovery mode: the software will be able to discover supported devices automatically upon a device joining the network.
+To reduce network traffic, the settings page will allow specifying which devices can be discovered.
+    \item Manual device control mode: alter the state of devices manually through an easy to use interface in the web UI or through a command line based application accessible through the UI.
+    \item Power reporting mode: a page will be available in the UI for reporting the overall power consumption of the building as well as individual device power consumption (if available). 
+\end{enumerate}
+
 \section{End-Use Requirements}
@@
 
-By May, 2021, we want to have a modular design for the platform that will allow users to add drivers for new devices as they are developed.
+This will be implemented using a modular design for the platform that will allow users to add drivers for new devices as they are developed.
 Once a new device driver is added, the platform will be able to interact with it how the user wants.
 
-\section{Modes of Operation}
-To operate properly, the software must include three main modes of operation:
-\indent
-\begin{enumerate}[leftmargin=*,start=0,label={\bfseries Mode~\#\arabic*:}]
-    \item Device discovery mode: the software will be able to discover supported devices automatically upon a device joining the network.
-To reduce network traffic, the settings page will allow specifying which devices can be discovered.
-    \item Manual device control mode: alter the state of devices manually through an easy to use interface in the web UI or through a command line based application accessible through the UI.
-    \item Power reporting mode: a page will be available in the UI for reporting the overall power consumption of the building as well as individual device power consumption (if available). 
-\end{enumerate}
-
 \end{document}

### 2020-10-19 proposalPres.tex
Updated 497 documents and lab notebook

% Copyright 2004 by Till Tantau <tantau@users.sourceforge.net>.
%
% In principle, this file can be redistributed and/or modified under
% the terms of the GNU Public License, version 2.
%
% However, this file is supposed to be a template to be modified
% for your own needs. For this reason, if you use this file as a
% template and not specifically distribute it as part of a another
% package/program, I grant the extra permission to freely copy and
% modify this file as you see fit and even to delete this copyright
% notice. 
\UseRawInputEncoding
\documentclass{beamer}

% There are many different themes available for Beamer. A comprehensive
% list with examples is given here:
% http://deic.uab.es/~iblanes/beamer_gallery/index_by_theme.html
% You can uncomment the themes below if you would like to use a different
% one:
%\usetheme{AnnArbor}
%\usetheme{Antibes}
%\usetheme{Bergen}
%\usetheme{Berkeley}
%\usetheme{Berlin}
%\usetheme{Boadilla}
%\usetheme{boxes}
%\usetheme{CambridgeUS}
%\usetheme{Copenhagen}
%\usetheme{Darmstadt}
%\usetheme{default}
%\usetheme{Frankfurt}
%\usetheme{Goettingen}
%\usetheme{Hannover}
%\usetheme{Ilmenau}
%\usetheme{JuanLesPins}
%\usetheme{Luebeck}
\usetheme{Madrid}
%\usetheme{Malmoe}
%\usetheme{Marburg}
%\usetheme{Montpellier}
%\usetheme{PaloAlto}
%\usetheme{Pittsburgh}
%\usetheme{Rochester}
%\usetheme{Singapore}
%\usetheme{Szeged}
%\usetheme{Warsaw}

\usepackage{pgfgantt}
%\usepackage{todonotes}
\usepackage{media9}
\usepackage{subfigure}

% Customize Warsaw color 
\setbeamercolor*{palette primary}{use=structure,fg=white,bg=blue!50!black}
\setbeamercolor*{palette secondary}{use=structure,fg=white,bg=blue!60!black}
\setbeamercolor*{palette tertiary}{use=structure,fg=white,bg=blue!70!black}

% Customize Warsaw block title and background colors
\setbeamercolor{block title}{bg=red!50!black,fg=white}

\setbeamertemplate{bibliography item}{\insertbiblabel}  % insert bibliography numbers instead of symbol
\setbeamertemplate{caption}[numbered] % adds the figure or table number to the caption.

\title[System Level Requirements]{Development of Building Energy Management Platform}

% % A subtitle is optional and this may be deleted
% \subtitle{Product Proposal}

\author[B.~Lauer, E.~Watkins]{Brian~Lauer \and Elliot~Watkins \and
Advisor: Dr. Suruz Miah}
% - Give the names in the same order as the appear in the paper.
% - Use the \inst{?} command only if the authors have different
%   affiliation.

\institute[Bradley University] % (optional, but mostly needed)
{
  Department of Electrical and Computer Engineering\\
  Bradley University\\
  1501 W. Bradley Avenue\\
  Peoria, IL, 61625, USA
}
% - Use the \inst command only if there are several affiliations.
% - Keep it simple, no one is interested in your street address.

%\date[November~27,~2018]{Tuesday, November~27,~2018}
\date[October~19,~2020]{Thursday, October~19,~2020}
%\date[December~4,~2018]{Tuesday, December~4,~2016}

% - Either use conference name or its abbreviation.
% - Not really informative to the audience, more for people (including
%   yourself) who are reading the slides online

\logo{\hfill\href{http://www.bradley.edu}{\includegraphics[width=0.75cm]{figs/logoBU1-Print}}}  % place logo in every page

\subject{Building Energy Management}
% This is only inserted into the PDF information catalog. Can be left
% out.

% If you have a file called "university-logo-filename.xxx", where xxx
% is a graphic format that can be processed by latex or pdflatex,
% resp., then you can add a logo as follows:

% \pgfdeclareimage[height=0.5cm]{university-logo}{university-logo-filename}
% \logo{\pgfuseimage{university-logo}}

% Delete this, if you do not want the table of contents to pop up at
% the beginning of each subsection:
\AtBeginSubsection[]
{
  \begin{frame}<beamer>{Outline}
    \tableofcontents[currentsection,currentsubsection]
  \end{frame}
}

% Let's get started
\begin{document}

\begin{frame}
  \titlepage
\end{frame}

\begin{frame}{Outline} %
  \tableofcontents%[pausesections]
  % You might wish to add the option [pausesections]
\end{frame}

% Section and subsections will appear in the presentation overview
% and table of contents.
\section{Introduction}
%\section{Project Description}
\section{System Architecture}
\section{High Level Functionality}
\section{Modes of Operation}
\section{End-Use Requirements}

\begin{frame}{Introduction}{} %Elliot
    % Applications of Building Energy Management
    \begin{itemize}
        \item Why BEMS?
            \begin{itemize}
                \item Can help save on energy costs
                \item Less impact on environment
            \end{itemize}
        \item How can the IoT help?
            \begin{itemize}
                \item WiFi integrated into most buildings
                \item Our Web-based approach simplifies development and end-user experience
            \end{itemize}
        \item Overall Goal
            \begin{itemize}
                \item Create a platform in which users can login and access devices connected to a building’s energy supply
                \item Allow the user to closely monitor energy usage throughout a commercial or residential building.
            \end{itemize}
    \end{itemize}
\end{frame}

\begin{frame}{Introduction}{}
\centering
Play Video
\end{frame}

% System Architecture Diagram
\begin{frame}{System Architecture}{} %Elliot
    % High-Level Architecture Figure
    \begin{figure}
        \centering
        \includegraphics[scale=0.4]{figs/highLevelArchitecture.pdf}
        \caption{High level architecture}
        \label{fig:my_label}
    \end{figure}
\end{frame}

% System Architecture - Supported Devices
\begin{frame}{System Architecture - Supported Devices}{} %Elliot
    % What are we using to build this?
    \begin{itemize}
        \item WeMo Switch
            \begin{itemize}
                \item Turn on and off from web server
                \item Record power usage month to month
                \item Plot power usage for a given time frame using MatPlotLib library in Python
            \end{itemize}
        \item Embedded Computer
            \begin{itemize}
                \item Connect to BeagleBone Blue
                \item Control motor drivers from web server
            \end{itemize}
        \item Smart Meter
            \begin{itemize}
                \item Cannot physically implement this
                \item MATLAB has ability to simulate power meters
            \end{itemize}
    \end{itemize}
\end{frame}

\begin{frame}{System Architecture}{}
    \begin{figure}
        \centering
        \includegraphics[scale=0.4]{figs/functionalBlockDiagram.pdf}
        \caption{Functional block diagram of the BEMS}
        \label{fig:my_label}
    \end{figure}
\end{frame}

% System Architecture - Inputs
\begin{frame}{System Architecture - Inputs}{} %Elliot
    \begin{itemize}
        \item Users will adjust the operation of a device (turn up temperature of AC unit or turn on/off a light)
        \item Smart Power meters (BEMS core will need to receive power data from MATLAB scripts) will provide real-time power consumption for the entire building
        \item Connected devices will give status updates when prompted by the BEMS Core
        \item The BEMS core will scan a weather service website to receive updates on severe weather that may impact power transmission
    \end{itemize}
\end{frame}

% System Architecture - Web Server
\begin{frame}{System Architecture - BEMS Core}{} %Brian
    % What are we using to build this?
    \begin{itemize}
        \item Python and Javascript
            \begin{itemize}
                \item Python is used to control devices on the back end
                \item Javascript is used to run the web page (user interface)
            \end{itemize}
        \item Flask Web Framework
            \begin{itemize}
                \item Handles rendering device metadata and time-series data to the web page
                \item Routes URLs to view functions
            \end{itemize}
        \item Apache Cassandra and SQLite databases
            \begin{itemize}
                \item Apache Cassandra is a NoSQL database management system for storing time-series device data
                \item SQLite is a simple relational database management system that will be used to store device metadata
            \end{itemize}
        \item Bootstrap and JQuery
            \begin{itemize}
                \item Bootstrap is a CSS framework for creating modern web pages
                \item JQuery is a Javascript library to help with DOM traversal, event handling, and AJAX requests
            \end{itemize}
    \end{itemize}
\end{frame}

\begin{frame}{System Architecture - Outputs}{}
\begin{itemize}
    \item BEMS core will output all data from connected devices to be accessed through the web server via a browser (accessed by any device that can browse the web)
    \item All available data on any smart device will be able to be perused via the platform
\end{itemize}    
\end{frame}

\begin{frame}{Modes of Operation}{}
    \begin{itemize}
        \item \textbf{Mode \#0: Device discovery mode}: networked IoT devices will be automatically discovered on the local building network
        \item \textbf{Mode \#1: Manual device control mode}: the state of each active device will be controllable through an easy-to-use web interface and command line application
        \item \textbf{Mode \#2: Power reporting mode}: a page will be available for reporting overall building power consumption and individual device power consumption
    \end{itemize}
\end{frame}

\begin{frame}{End-Use Requirements}{}
    \begin{itemize}
        \item Device behavior should be implemented to seamlessly support different status configurations
        \item Users (building admins, employees, home owners) will have the ability to see a plot of the past energy usage of a device 
        \item Python's Matplotlib package will form the basis for the plotting functionality 
        \item Support for new devices should be easily developed through multiple layers of abstractions
    \end{itemize}    
\end{frame}

% You can reveal the parts of a slide one at a time
% with the \pause command:
%\begin{frame}{Second Slide Title}
%  \begin{itemize}
%  \item {
%    First item.
%    \pause % The slide will pause after showing the first item
%  }
  %\item {   
  %  Second item.
 % }
  % You can also specify when the content should appear
  % by using <n->:
 % \item<3-> {
 %   Third item.
 % }
%  \item<4-> {
%    Fourth item.
 % }
  % or you can use the \uncover command to reveal general
  % content (not just \items):
%  \item<5-> {
%    Fifth item. \uncover<6->{Extra text in the fifth item.}
%  }
%  \end{itemize}
%\end{frame}

%\section{Second Main Section}

% \subsection{Another Subsection}

% \begin{frame}{Blocks}
% \begin{block}{Block Title}
% You can also highlight sections of your %presentation in a block, with it's own %title
% \end{block}
% \begin{theorem}
% There are separate environments for %theorems, examples, definitions and proofs.
% \end{theorem}
% \begin{example}
% Here is an example of an example block.
% \end{example}
% \end{frame}

% Placing a * after \section means it will not show in the
% outline or table of contents.
% \section*{Summary}
% \begin{frame}{Summary} %Glenn
%   \begin{itemize}
%     \item Development of a platform to control devices
%     \item Ability to read device status (power usage, state)
%   \end{itemize}
% \end{frame}
% \begin{frame}{Summary}
%   \begin{itemize}
%   \item
%     The \alert{first main message} of your talk in one or two lines.
%   \item
%     The \alert{second main message} of your talk in one or two lines.
%   \item
%     Perhaps a \alert{third message}, but not more than that.
%   \end{itemize}

%   \begin{itemize}
%   \item
%     Outlook
%     \begin{itemize}
%     \item
%       Something you haven't solved.
%     \item
%       Something else you haven't solved.
%     \end{itemize}
%   \end{itemize}
% \end{frame}

% All of the following is optional and typically not needed. 
\appendix
\section<presentation>*{\appendixname}
\subsection<presentation>*{For Further Reading}

\begin{frame}[allowframebreaks]
  \frametitle<presentation>{References}

  \begin{thebibliography}{10}

  \setbeamertemplate{bibliography item}[online]

  \bibitem{bemoss}
  BEMOSS 3.5
  \newblock \url{https://github.com/bemoss/BEMOSS3.5}

  \bibitem{flask}
  Flask Documentation
  \newblock \url{https://flask.palletsprojects.com/en/1.1.x/}

  \bibitem{datastaxPython}
  Datastax Python 3 Cassandra Driver
  \newblock \url{https://docs.datastax.com/en/developer/python-driver/3.24/}

  \bibitem{apacheCassandra}
  Apache Cassandra Database
  \newblock \url{https://cassandra.apache.org/}
  \end{thebibliography}
\end{frame}

\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:

### 2020-11-26 proposalPres.tex
Uploaded proposal presentation

@@
 
-\title[System Level Requirements]{Development of Building Energy Management Platform}
+\title[Project Proposal]{Senior Capstone Project I\\\textbf{\underline{Project Proposal}}\\
+\vspace{0.25in}
+Project Title: Development of an Intelligent Building Energy Management Platform}
 
@@
 %\date[November~27,~2018]{Tuesday, November~27,~2018}
-\date[October~19,~2020]{Thursday, October~19,~2020}
+\date[November~30,~2020]{Monday, November~30,~2020}
 %\date[December~4,~2018]{Tuesday, December~4,~2016}
@@
 %\section{Project Description}
+\section{Background Study}
+\section{Functional Requirements}
 \section{System Architecture}
-\section{High Level Functionality}
-\section{Modes of Operation}
-\section{End-Use Requirements}
-
-\begin{frame}{Introduction}{} %Elliot
-    % Applications of Building Energy Management
-    \begin{itemize}
-        \item Why BEMS?
-            \begin{itemize}
-                \item Can help save on energy costs
-                \item Less impact on environment
-            \end{itemize}
-        \item How can the IoT help?
-            \begin{itemize}
-                \item WiFi integrated into most buildings
-                \item Our Web-based approach simplifies development and end-user experience
-            \end{itemize}
-        \item Overall Goal
-            \begin{itemize}
-                \item Create a platform in which users can login and access devices connected to a building’s energy supply
-                \item Allow the user to closely monitor energy usage throughout a commercial or residential building.
-            \end{itemize}
-    \end{itemize}
-\end{frame}
+\section{Preliminary Work}
+\section{Parts List}
+\section{Timeline and Milestones}
 
 \begin{frame}{Introduction}{}
-\centering
-Play Video
-\end{frame}
-
-% System Architecture Diagram
-\begin{frame}{System Architecture}{} %Elliot
     % High-Level Architecture Figure
@@
 
-% System Architecture - Supported Devices
-\begin{frame}{System Architecture - Supported Devices}{} %Elliot
-    % What are we using to build this?
+\begin{frame}{Introduction}{}
+    % Applications of Building Energy Management
     \begin{itemize}
-        \item WeMo Switch
+        \item BEMS Core will interface with as many devices as it has support for 
         \begin{itemize}
-                \item Turn on and off from web server
-                \item Record power usage month to month
-                \item Plot power usage for a given time frame using MatPlotLib library in Python
+            \item Wemo and Beaglebone will be fully functional by end of semester
+            \item User will be able to control these devices directly from the Web Server
         \end{itemize}
-        \item Embedded Computer
+        \item In the Spring, we hope to simulate a microgrid with MATLAB Simscape and an HVAC System with Simulink
         \begin{itemize}
-                \item Connect to BeagleBone Blue
-                \item Control motor drivers from web server
+            \item The microgrid simulation will allow us to virtually measure a power meter
+            \item An HVAC System in Simulink could be controlled with a Linear Quadratic Regulator (LQR) based algorithm that can regulate the building temperature
         \end{itemize}
-        \item Smart Meter
+        \item If time allows, we will also have the BEMS Core ping a weather service for updates on severe weather as well
+    \end{itemize}
+\end{frame}
+
+\begin{frame}{Background Study}{}
+    \begin{itemize} % Break down more (talk about BEMOSS possibly) and the LoBEMS project
+        \item An existing BEMS described in~\cite{Mataloto2019} incorporates its own sensors for temperature, humidity, luminosity, air quality, and motion.
+The data from these sensors is then fed to the BEMS core where decisions are made for the HVAC system and lighting of a building.
+The sensor data is transferred to the BEMS though the IoT, like our own BEMS core.
+        \item One of the works in the literature discusses Model Predictive Control (MPC) which is a modern process control algorithm capable of taking into account current and previous time values to improve building automation~\cite{Mayer2017}.
+A multilevel hierarchy is presented to split control of a building into two levels: the energy supply level and user level.
+Example usage of this control scheme provided are temperature control of a building and its corresponding zones and interaction with a smart grid.
+Studies were performed on a commercial building with the building's energy supply system and hierarchy model predictive controller implemented in Matlab.
+    \end{itemize}
+\end{frame}
+
+\begin{frame}{Background Study}{}
+\begin{figure}
+    \centering
+    \includegraphics[scale=0.45]{figs/img/pvBESSystem.png}
+    \caption{Photovoltaic (Battery Energy Storage) BES system simulated in \cite{Barchi2018}}
+    \label{fig:pvBESSystem}
+\end{figure}
+\end{frame}
+
+\begin{frame}{Functional Requirements}{}
     \begin{itemize}
-                \item Cannot physically implement this
-                \item MATLAB has ability to simulate power meters
+        \item The minimum viable product will be to connect to a Wemo Insight Smart Plug and a BeagleBone Blue
+        \begin{itemize}
+            \item The WeMo Plug will simply be turned on and off from the Web Server. The BEMS Core will also record its power usage
+            \item The only functionality needed on the BeagleBone Blue will be PWM input to the motor drivers
         \end{itemize}
+        \item A database (Apache Cassandra) will be implemented for recording power usage
     \end{itemize}
@@
 \begin{frame}{System Architecture}{}
+    % Functional Block Diagram
     \begin{figure}
@@
 
-% System Architecture - Inputs
-\begin{frame}{System Architecture - Inputs}{} %Elliot
+\begin{frame}{System Architecture - Inputs}{}
+    % What are we using to build this?
     \begin{itemize}
-        \item Users will adjust the operation of a device (turn up temperature of AC unit or turn on/off a light)
-        \item Smart Power meters (BEMS core will need to receive power data from MATLAB scripts) will provide real-time power consumption for the entire building
-        \item Connected devices will give status updates when prompted by the BEMS Core
-        \item The BEMS core will scan a weather service website to receive updates on severe weather that may impact power transmission
+        \item Users
+            \begin{itemize}
+                \item Adjust the operation of a device (turn up the temperature of an AC unit, for instance)
+                \item Turn a device on or off
+            \end{itemize}
+        \item Smart power meters will be able to connect the platform and give real-time updates of the building's overall power usage
+        \item Connected Devices
+            \begin{itemize}
+                \item The Wemo Switch and BeagleBone Blue will have master-slave relationship with the BEMS Core
+                \item The BEMS Core will send commands through the router to download power data
+            \end{itemize}
+        \item The BEMS Core regularly receives weather updates from a weather service
     \end{itemize}
@@
     \item BEMS core will output all data from connected devices to be accessed through the web server via a browser (accessed by any device that can browse the web)
-    \item All available data on any smart device will be able to be perused via the platform
+    \begin{itemize}
+        \item On/Off Status
+        \item PWM Setting
+    \end{itemize}
+    \item When prompted by user input, the BEMS core will run a python script to plot energy usage of a given device on a given day; this plot will appear on the active devices page
+    \item Warning on the Web Server home page about potential energy loss due to storms
 \end{itemize}
@@
 
-\begin{frame}{Modes of Operation}{}
+\begin{frame}{Preliminary Work - Design}{}
     \begin{itemize}
-        \item \textbf{Mode \#0: Device discovery mode}: networked IoT devices will be automatically discovered on the local building network
-        \item \textbf{Mode \#1: Manual device control mode}: the state of each active device will be controllable through an easy-to-use web interface and command line application
-        \item \textbf{Mode \#2: Power reporting mode}: a page will be available for reporting overall building power consumption and individual device power consumption
+        \item The platform incorporates multiple agents to help facilitate communication between various parts of the software
+        \item Discovery agent
+        \begin{itemize}
+            \item Traverses through available API files and uses the findDevicesAPI call to locate devices on the network
+            \item Later on auto discovery will be implemented to allow devices to be shown in the software whenever a new supported device joins the network
+        \end{itemize}
+        \item Control agent
+        \begin{itemize}
+            \item General agent for all supported devices, capable of retrieving and modifying the status of a device available on the network through API calls
+            \item Supports starting up a separate thread to periodically query the device for information like ON/OFF status and power consumption 
+        \end{itemize}
     \end{itemize}
@@
 
-\begin{frame}{End-Use Requirements}{}
+\begin{frame}{Preliminary Work - Design}{}
+    \begin{figure}
+        \centering
+        \includegraphics[scale=0.35]{figs/setDeviceToActiveFlow.pdf}
+        \caption{\texttt{DiscoveryAgent.setDeviceToActive()} flow chart}
+        \label{fig:setDeviceToActiveFlow}
+    \end{figure}
+\end{frame}
+
+\begin{frame}{Preliminary Work - Design}{}
+    \begin{figure}
+        \centering
+        \includegraphics[scale=0.3]{figs/searchForDevicesFlow.pdf}
+        \caption{\texttt{DiscoveryAgent.searchForDevices()} flow chart}
+        \label{fig:searchForDevicesFlow}
+    \end{figure}
+\end{frame}
+
+\begin{frame}{Preliminary Work - Design}{}
+    \begin{figure}
+        \centering
+        \includegraphics[scale=0.3]{figs/periodicQueryBehaviorFlow.pdf}
+        \caption{\texttt{ControlAgent.periodicQueryBehavior()} flow chart}
+        \label{fig:periodicQueryBehavior}
+    \end{figure}
+\end{frame}
+
+\begin{frame}{Device APIs}
     \begin{itemize}
-        \item Device behavior should be implemented to seamlessly support different status configurations
-        \item Users (building admins, employees, home owners) will have the ability to see a plot of the past energy usage of a device 
-        \item Python's Matplotlib package will form the basis for the plotting functionality 
-        \item Support for new devices should be easily developed through multiple layers of abstractions
+        \item setState - Setter for Wemo Insight Switch and motor controllers on Embedded Computer
+        \item getState - Returns power usage and on/off status for Wemo Insight Switch and PWM setting for Embedded Computer
+        \item findDevices - Returns URL of supported devices on the network
+        \item findMetadata - Returns manufacturer, name, and MAC address of supported devices
+        \item For Wemo Insight Switch, IP multicasting and Universal Plug and Play are used to send messages
+        \item We are using a Beaglebone Blue for an embedded computer and so far have only used IP multicasting for communication
     \end{itemize}
 \end{frame}
+
+\begin{frame}{Experimental Setup}
+    \begin{figure}
+        \centering
+        \includegraphics[scale=0.3]{figs/experimentalSetup.pdf}
+        \caption{Lab Setup for Testing and Development}
+        \label{fig:my_label}
+    \end{figure}
+\end{frame}
+
+\begin{frame}{Preliminary Work - Experimental Activities}{}
+    \begin{figure}
+        \centering
+        \includegraphics[scale=0.3]{figs/activeDevicesWithEmbeddedPicture.png}
+        \caption{Screenshot of Web Server (Active Devices Page)}
+        \label{fig:my_label}
+    \end{figure}
+\end{frame}
+
+\begin{frame}{Preliminary Work - Experimental Activities}{}
+    \begin{figure}
+        \centering
+        \includegraphics[scale=0.5]{figs/powerPlot2020-11-03.eps}
+        \caption{Plot of WeMo Switch power usage 2020-11-03}
+        \label{fig:powerPlotWeMoSwitch}
+    \end{figure}
+\end{frame}
+
+\begin{frame}{Preliminary Work - Experimental Activities}{}
+    \begin{itemize}
+        \item Up to this point, work has been completed on the web user interface which was developed with the Bootstrap CSS framework and the JQuery Javascript framework
+        \item When a request is sent to the active devices URL, the discovery agent will ping all possible supported devices on the network and newly discovered devices will appear on the active devices page
+        \item the refresh button will cause the position of the slide switch switch shown to change depending on whether the WeMo switch is on or off
+        \item The top nav bar will link to other pages including the home page, applications page, notifications and settings page (active devices is currently the only page implemented)
+    \end{itemize}
+\end{frame}
+
+\begin{frame}{Parts List}{}
+    \begin{itemize}
+        \item WeMo Insight Smart Plug
+        \item BeagleBone Blue
+        \begin{itemize}
+            \item Octavo OSD3358 Microprocessor
+            \item Wifi/Bluetooth
+            \item IMU/Barometer
+            \item Power Regulation and state-of-charge LEDs for a 2-cell LiPo
+            \item H-Bridges
+            \item Connectors for 4 DC motors and 8 Servos
+        \end{itemize}
+        \item JST-ZH connector (for BeagleBone Blue Motor Connections)
+        \item DC Motor
+        \item ECE department laptop
+        \item ECE department lab computers
+    \end{itemize}
+\end{frame}
+% https://www.lucidchart.com/pages/templates/network-diagram
+\begin{frame}{Timeline and Milestones}
+\begin{ganttchart}[
+hgrid,vgrid,x unit=.55cm, y unit title=.6cm,y unit chart=.4cm,milestone label font=\tiny,bar label font=\tiny, group label font=\small,bar/.append style={fill=green},bar incomplete/.append style={fill=red}]{3}{16}
+\gantttitle{Fall 2020}{14}\\
+\gantttitle{Sep}{2}
+\gantttitle{Oct}{4}
+\gantttitle{Nov}{4}
+\gantttitle{Dec}{4}\\
+\ganttgroup[progress = 100,group progress label font = \tiny,group progress label anchor = east]{WeMo Functionality}{3}{5} \\
+\ganttbar[progress = 100,bar progress label font = \tiny,bar progress label anchor = east]{Refresh Status on Web Server}{3}{5}\\
+\ganttbar[progress = 100,bar progress label font = \tiny, bar progress label anchor = east]{Record Power Usage}{3}{5}\\
+\ganttgroup[progress = 67,group progress label font = \tiny,group progress label anchor = east]{Data Logging Feature}{5}{10}\\
+\ganttbar[progress = 80,bar progress label font = \tiny,bar progress label anchor = east]{Support for Cassandra database}{5}{9}\\
+\ganttbar[progress = 0,bar progress label font = \tiny,bar progress label anchor = east]{Matplotlib Plot in UI}{10}{10}\\
+\ganttgroup[progress = 0,group progress label font = \tiny, group progress label anchor = east]{User Login}{11}{14}\\
+\ganttbar[progress = 0,bar progress label font = \tiny,bar progress label anchor = east]{Login Page}{11}{12}\\
+\ganttbar[progress = 0,bar progress label font = \tiny,bar progress label anchor = east]{Session Management}{13}{14}\\
+\ganttgroup[progress = 55,group progress label font = \tiny,group progress label anchor = east]{BeagleBone Functionality}{7}{14}\\
+\ganttbar[progress = 90,bar progress label font = \tiny,bar progress label anchor = east]{Communication with BEMS}{7}{11}\\
+\ganttbar[progress = 0,bar progress label font = \tiny,bar progress label anchor = east]{PWM Motor Control}{12}{13}\\
+\ganttbar[progress = 0,bar progress label font = \tiny,bar progress label anchor = east]{Record Power Usage}{14}{14}
+\end{ganttchart}
+\end{frame}
+
+\begin{frame}{Timeline and Milestones}
+\begin{ganttchart}[
+hgrid,vgrid,x unit=.45cm, y unit title=.6cm,y unit chart=.4cm,milestone label font=\tiny,bar label font=\tiny, group label font=\small,bar/.append style={fill=green},bar incomplete/.append style={fill=red}]{3}{16}
+\gantttitle{Spring 2021}{14}\\
+\gantttitle{Jan}{2}
+\gantttitle{Feb}{4}
+\gantttitle{Mar}{4}
+\gantttitle{Apr}{4}\\
+\ganttgroup[progress = 0,group progress label font = \tiny, group progress label anchor = east]{Simscape Microgrid}{3}{8}\\
+\ganttbar[progress = 0,bar progress label font = \tiny,group progress label anchor = east]{Setup Simscape Microgrid}{3}{5}\\
+\ganttbar[progress = 0,bar progress label font = \tiny,group progress label anchor = east]{Get Power Meter Data}{6}{8}\\
+\ganttgroup[progress = 0,group progress label font = \tiny,group progress label anchor = east]{HVAC Control}{9}{14} \\
+\ganttbar[progress = 0,bar progress label font = \tiny,bar progress label anchor = east]{Create HVAC system in Simscape}{9}{11} \\
+\ganttbar[progress = 0,bar progress label font = \tiny,bar progress label anchor = east]{Implement LQR Algorithm for HVAC Control}{12}{14} \\
+\ganttgroup[progress = 0,group progress label font = \tiny,group progress label anchor = east]{Weather Service Update}{15}{16}\\
+\ganttbar[progress = 0,bar progress label font = \tiny,group progress label anchor = east]{Receive Weather Data}{15}{15}\\
+\ganttbar[progress = 0,bar progress label font = \tiny,group progress label anchor = east]{Display Notification}{16}{16}
+\end{ganttchart}    
+\end{frame}
+
+% \begin{frame}{Timeline and Milestone}
+% \begin{ganttchart}[
+% hgrid,vgrid,x unit=.55cm, y unit title=.6cm,y unit chart=.4cm,milestone label font=\tiny,bar label font=\tiny, group label font=\small,bar/.append style={fill=green},bar incomplete/.append style={fill=red}]{1}{18}
+
+% \end{ganttchart}    
+% \end{frame}
 
@@
 % outline or table of contents.
-% \section*{Summary}
-% \begin{frame}{Summary} %Glenn
-%   \begin{itemize}
-%     \item Development of a platform to control devices
-%     \item Ability to read device status (power usage, state)
-%   \end{itemize}
-% \end{frame}
+\section*{Summary}
+\begin{frame}{Summary} %Brian
+  \begin{itemize}
+    \item Development of a platform to control devices
+    \item Ability to read device status (power usage, state)
+    \item Smart grid simulation using Simscape and Matlab
+    \item HVAC control algorithm using Linear Quadratic Regulator (LQR)
+  \end{itemize}
+\end{frame}
 % \begin{frame}{Summary}
@@
 
+\begin{frame}{References}
+    \bibliographystyle{IEEEtran}
+    \bibliography{bib/references.bib}
+\end{frame}
+
 \end{document}

### 2020-11-26 proposalPres.tex
Updated proposal presentation

@@
     \begin{itemize} % Break down more (talk about BEMOSS possibly) and the LoBEMS project
-        \item An existing BEMS described in~\cite{Mataloto2019} incorporates its own sensors for temperature, humidity, luminosity, air quality, and motion.
-The data from these sensors is then fed to the BEMS core where decisions are made for the HVAC system and lighting of a building.
-The sensor data is transferred to the BEMS though the IoT, like our own BEMS core.
-        \item One of the works in the literature discusses Model Predictive Control (MPC) which is a modern process control algorithm capable of taking into account current and previous time values to improve building automation~\cite{Mayer2017}.
-A multilevel hierarchy is presented to split control of a building into two levels: the energy supply level and user level.
-Example usage of this control scheme provided are temperature control of a building and its corresponding zones and interaction with a smart grid.
-Studies were performed on a commercial building with the building's energy supply system and hierarchy model predictive controller implemented in Matlab.
+        \item An existing BEMS described in~\cite{Mataloto2019} incorporates its own sensors for:
+        \begin{itemize}
+            \item temperature
+            \item humidity
+            \item luminosity
+            \item air quality
+            \item motion
+        \end{itemize}
+        \item The data from these sensors is fed to the BEMS core where decisions are made for the HVAC system and lighting of the building
+        \item While we will only be simulating HVAC with Simscape, our BEMS core is similar to this project in that we are using IoT as a communication platform
+    \end{itemize}
+\end{frame}
+
+\begin{frame}{Background Study}{}
+\begin{itemize}
+    \item MPC (Model Predictive Control) used in~\cite{Mayer2017} 
+    \item Building control split into two levels for building automation improvement
+    \item Examples of the usage of MPC given are temperature control and interaction with smart grids
 \end{itemize}    

### 2020-11-30 proposalPres.tex
Updated proposal pres

@@
         \begin{itemize}
-            \item Wemo and Beaglebone will be fully functional by end of semester
+            \item Wemo and Embedded Computer will be fully functional by end of semester
             \item User will be able to control these devices directly from the Web Server
@@
     \begin{itemize}
-        \item The minimum viable product will be to connect to a Wemo Insight Smart Plug and a BeagleBone Blue
+        \item The minimum viable product will be to connect to a Wemo Insight Smart Plug and a Embedded Computer (BeagleBone Blue)
         \begin{itemize}
@@
             \begin{itemize}
-                \item The Wemo Switch and BeagleBone Blue will have master-slave relationship with the BEMS Core
+                \item The Wemo Switch and Embedded Computer will have master-slave relationship with the BEMS Core
                 \item The BEMS Core will send commands through the router to download power data
@@
         \item getState - Returns power usage and on/off status for Wemo Insight Switch and PWM setting for Embedded Computer
-        \item findDevices - Returns URL of supported devices on the network
+        \item findDevices - Returns IP address of supported devices on the network
         \item findMetadata - Returns manufacturer, name, and MAC address of supported devices
@@
 \ganttbar[progress = 0,bar progress label font = \tiny,bar progress label anchor = east]{Session Management}{13}{14}\\
-\ganttgroup[progress = 55,group progress label font = \tiny,group progress label anchor = east]{BeagleBone Functionality}{7}{14}\\
+\ganttgroup[progress = 55,group progress label font = \tiny,group progress label anchor = east]{Embedded Computer Functionality}{7}{14}\\
 \ganttbar[progress = 90,bar progress label font = \tiny,bar progress label anchor = east]{Communication with BEMS}{7}{11}\\
@@
 \ganttbar[progress = 0,bar progress label font = \tiny,bar progress label anchor = east]{Implement LQR Algorithm for HVAC Control}{12}{14} \\
+\ganttgroup[progress=0,group progress label font=\tiny,group progress label anchor = east]{Auto Discovery}{15}{16}\\
 \ganttgroup[progress = 0,group progress label font = \tiny,group progress label anchor = east]{Weather Service Update}{15}{16}\\

### 2021-04-26 finalPresentation.tex

% Copyright 2004 by Till Tantau <tantau@users.sourceforge.net>.
%
% In principle, this file can be redistributed and/or modified under
% the terms of the GNU Public License, version 2.
%
% However, this file is supposed to be a template to be modified
% for your own needs. For this reason, if you use this file as a
% template and not specifically distribute it as part of a another
% package/program, I grant the extra permission to freely copy and
% modify this file as you see fit and even to delete this copyright
% notice. 
\UseRawInputEncoding
\documentclass{beamer}

% There are many different themes available for Beamer. A comprehensive
% list with examples is given here:
% http://deic.uab.es/~iblanes/beamer_gallery/index_by_theme.html
% You can uncomment the themes below if you would like to use a different
% one:
%\usetheme{AnnArbor}
%\usetheme{Antibes}
%\usetheme{Bergen}
%\usetheme{Berkeley}
%\usetheme{Berlin}
%\usetheme{Boadilla}
%\usetheme{boxes}
%\usetheme{CambridgeUS}
%\usetheme{Copenhagen}
%\usetheme{Darmstadt}
%\usetheme{default}
%\usetheme{Frankfurt}
%\usetheme{Goettingen}
%\usetheme{Hannover}
%\usetheme{Ilmenau}
%\usetheme{JuanLesPins}
%\usetheme{Luebeck}
\usetheme{Madrid}
%\usetheme{Malmoe}
%\usetheme{Marburg}
%\usetheme{Montpellier}
%\usetheme{PaloAlto}
%\usetheme{Pittsburgh}
%\usetheme{Rochester}
%\usetheme{Singapore}
%\usetheme{Szeged}
%\usetheme{Warsaw}

\usepackage{ragged2e}
\usepackage{multicol}
\usepackage{pgfgantt}
%\usepackage{todonotes}
\usepackage{media9}
\usepackage{subfigure}
\usepackage{wrapfig}
% Customize Warsaw color 
\setbeamercolor*{palette primary}{use=structure,fg=white,bg=blue!50!black}
\setbeamercolor*{palette secondary}{use=structure,fg=white,bg=blue!60!black}
\setbeamercolor*{palette tertiary}{use=structure,fg=white,bg=blue!70!black}

% Customize Warsaw block title and background colors
\setbeamercolor{block title}{bg=red!50!black,fg=white}

\setbeamertemplate{bibliography item}{\insertbiblabel}  % insert bibliography numbers instead of symbol
\setbeamertemplate{caption}[numbered] % adds the figure or table number to the caption.

\title[Final Presentation]{Intelligent Building Energy Management System}

% % A subtitle is optional and this may be deleted
% \subtitle{Product Proposal}

\author[B.~Lauer, E.~Watkins]{Brian~Lauer \and Elliot~Watkins \and
Advisor: Dr. Suruz Miah}
% - Give the names in the same order as the appear in the paper.
% - Use the \inst{?} command only if the authors have different
%   affiliation.

\institute[Bradley University] % (optional, but mostly needed)
{
  Department of Electrical and Computer Engineering\\
  Bradley University\\
  1501 W. Bradley Avenue\\
  Peoria, IL, 61625, USA
}
% - Use the \inst command only if there are several affiliations.
% - Keep it simple, no one is interested in your street address.

%\date[November~27,~2018]{Tuesday, November~27,~2018}
\date[April~27,~2021]{Tuesday, April~27,~2021}
%\date[December~4,~2018]{Tuesday, December~4,~2016}

% - Either use conference name or its abbreviation.
% - Not really informative to the audience, more for people (including
%   yourself) who are reading the slides online

\logo{\hfill\href{http://www.bradley.edu}{\includegraphics[width=0.75cm]{figs/logoBU1-Print}}}  % place logo in every page

\subject{Building Energy Management}
% This is only inserted into the PDF information catalog. Can be left
% out.

% If you have a file called "university-logo-filename.xxx", where xxx
% is a graphic format that can be processed by latex or pdflatex,
% resp., then you can add a logo as follows:

% \pgfdeclareimage[height=0.5cm]{university-logo}{university-logo-filename}
% \logo{\pgfuseimage{university-logo}}

% Delete this, if you do not want the table of contents to pop up at
% the beginning of each subsection:
\AtBeginSubsection[]
{
  \begin{frame}<beamer>{Outline}
    \tableofcontents[currentsection,currentsubsection]
  \end{frame}
}

% Let's get started
\begin{document}

\begin{frame}
  \titlepage
\end{frame}

% \begin{frame}{Outline} %
%   \tableofcontents%[pausesections]
%   % You might wish to add the option [pausesections]
% \end{frame}

% Section and subsections will appear in the presentation overview
% and table of contents.
\section{Introduction}
\section{Architecture}
\section{Embedded/Robotics Computer}
\section{WeMo Insight Switch}
\section{Overall Setup}
\section{Home Page}
\section{Active Devices Page}
\section{WeMo Power Plot}
\section{Scheduling/Applications Page}
\section{Conclusion}

\begin{frame}{Introduction}{} % Elliot
    % Applications of Building Energy Management
    \begin{multicols}{2}
        \begin{small}
            \begin{itemize}
                \item Problems that iBEMS will address
                    \begin{itemize}
                        \item Can help save on energy costs
                        \item Less impact on environment
                    \end{itemize}
                \item How can the IoT help?
                    \begin{itemize}
                        \item WiFi integrated into most buildings
                        \item Our Web-based approach simplifies development and end-user experience
                    \end{itemize}
                \item Overall Goal
                    \begin{itemize}
                        \item Create a platform in which users can login and access 2 or 3 IoT devices connected to a building’s energy supply
                        \item Allow the user to closely monitor energy usage for a residential building.
                    \end{itemize}
            \end{itemize}
        \end{small}
        \begin{figure}
        \centering
        \includegraphics[scale=0.4]{figs/BEMS_Image.jpg}
        \caption{General BEMS}
        \label{fig:high_level_arch}
    \end{figure}
    \end{multicols}
\end{frame}

\begin{frame}{Architecture}{} % Brian
    \begin{multicols}{2}
        \begin{figure}
            \centering
            \includegraphics[scale=0.3]{figs/highLevelArchitecture.pdf}
            \caption{High Level Architecture}
            \label{fig:high_level_arch}
        \end{figure}
        \textsc{}
        \begin{itemize}
            \item iBEMS currently has support for 2 IoT devices (WeMo Insight Switch and embedded computer) and can download weather data for the user
            \item A microgrid with a smart meter will be simulated in the near future
        \end{itemize}        
    \end{multicols}
\end{frame}

\begin{frame}{Architecture}{} % Brian
    \begin{multicols}{2}
        \begin{figure}
            \centering
            \includegraphics[scale=0.4]{figs/functionalBlockDiagram.pdf}
            \caption{Functional Block Diagram}
            \label{fig:functional_bd}
        \end{figure}

        \begin{small}
            \begin{itemize}
                \item iBEMS receives input from users, connected devices, and will automatically download weather data
                \item The core of iBEMS consists of a web server, a database and software agents which handle interactions with connected devices
                \item Power data, device status, and schedules for each device will be output to the web server. Additionally, connected devices respond to commands from the iBEMS
            \end{itemize}
        \end{small}
    \end{multicols}
\end{frame}

\begin{frame}{Operational Modes}{}
    \begin{enumerate}
        \setcounter{enumi}{-1}
        \item Startup menu
        \item Login - system administrators can add and configure users
        \item Home - view weather data
        \item Controlling devices
        \item Scheduling devices
    \end{enumerate}
\end{frame}

\begin{frame}{System Components}{}
    \begin{figure}
        \centering
        \includegraphics[scale=0.4]{figs/overallDiagram.pdf}
        \caption{Interconnection between system components}
        \label{fig:systemComponentInterconnection}
    \end{figure}
\end{frame}

\begin{frame}{Control Agent Functionality}{}
    \begin{figure}
        \centering
        \includegraphics[scale=0.6]{figs/controlAgentUML.pdf}
        \caption{Control Agent Class Diagram}
        \label{fig:controlAgentClass}
    \end{figure}
\end{frame}

\begin{frame}{Discovery Agent Functionality}{}
    \begin{figure}
        \centering
        \includegraphics[scale=0.6]{figs/discoveryAgentUML.pdf}
        \caption{Discovery Agent Class Diagram}
        \label{fig:discoveryAgentClass}
    \end{figure}
\end{frame}

\begin{frame}{Scheduling Agent Functionality}{}
    \begin{figure}
        \centering
        \includegraphics[scale=0.6]{figs/schedulingAgentUML.pdf}
        \caption{Scheduling Agent Class Diagram}
        \label{fig:schedulingAgentClass}
    \end{figure}
\end{frame}

\begin{frame}{Agent and Web Server Communication}{}
    \begin{figure}
        \centering
        \includegraphics[scale=0.5]{figs/pubSubAgents.pdf}
        \caption{Publish Subscribe Model}
        \label{fig:pubSubModel}
    \end{figure}
    \begin{itemize}
        \item Agents and web server use the ZeroMQ
        messaging library
        \item Python wrapper used
    \end{itemize}
\end{frame}

\begin{frame}{Embedded Computer Receiver Program}{}
    \begin{figure}
        \centering
        \includegraphics[scale=0.45]{figs/Beaglebone_Receiver_Diagram.png}
        \caption{Receiver Running on Embedded Computer}
        \label{fig:Beaglebone_Receiver_Diagram}
    \end{figure}
\end{frame}

\begin{frame}{Embedded Computer Circuit for Power Usage Data}{}
    \begin{figure}
        \centering
        \includegraphics[scale=0.7]{figs/Beaglebone_Circuit.png}
        \caption{Circuit to Measure Power Usage}
        \label{fig:Beaglebone_Circuit}
    \end{figure}
    \begin{itemize}
        \item The embedded computer does not have the ability to measure power, but it does have ADC
        \item Here, the power from the motor driver is being run through a resistor. The ADC reads the voltage across the resistor and since resistance is known, current can be calculated for 1 motor
    \end{itemize}
\end{frame}

\begin{frame}{Embedded/Robotics Computer}{} % Elliot
    \begin{multicols}{2}
        \begin{figure}
            \centering
            \includegraphics[scale=0.04]{figs/notConnectedSBC.jpg}
            \caption{Embedded Computer Not Connected}
            \label{fig:not_connected_bb}
        \end{figure}

        \begin{figure}
            \centering
            \includegraphics[scale=0.04]{figs/connectedSBC.jpg}
            \caption{Embedded Computer Connected}
            \label{fig:connected_bb}
        \end{figure}
    \end{multicols}
    \begin{small}
        \begin{itemize}
            \item Embedded computer accepts control commands and sends data to the server
            \item Red LED indicates the embedded computer is not connected and green LED indicates the embedded computer is connected
        \end{itemize}
    \end{small}
\end{frame}

% \begin{frame}{Frame Title}
%     \begin{figure}
%         \centering
%         \includegraphics{}
%         \caption{Caption}
%         \label{fig:my_label}
%     \end{figure}
% \end{frame}

\begin{frame}{WeMo Insight Switch}{} % Elliot 
    \begin{multicols}{2}
        \begin{figure}
            \centering
            \includegraphics[scale=0.045]{figs/wemoView.jpg}
            \caption{WeMo Insight Smart Plug}
            \label{fig:wemo}
        \end{figure}
        \textsc{}
        \begin{itemize}
            \item Appliance is plugged into the WeMo Switch
            \item WeMo Switch can internally turn power on and off
            \item iBEMS will control the WeMo Switch remotely
        \end{itemize}
    \end{multicols}
\end{frame}

\begin{frame}{Overall Setup}{} % Elliot 
    \begin{figure}
        \centering
        \includegraphics[scale=0.04]{figs/overallView.jpg}
        \caption{Overall View}
        \label{fig:my_label}
    \end{figure}
    Tested the WeMo Insight Switch with a bank of lights and the embedded computer with a robot chassis

\end{frame}

\begin{frame}{Startup Menu}
    \begin{multicols}{2}
        \begin{figure}
            \centering
            \includegraphics[scale=0.4]{figs/bemsGUI.png}
            \caption{Desktop GUI}
            \label{fig:desktopgui}
        \end{figure}
        \begin{figure}
            \centering
            \includegraphics[scale=0.5]{figs/bemsGUIError.png}
            \caption{Popup Error}
            \label{fig:popuperror}
        \end{figure}
    \end{multicols}
    \begin{itemize}
        \item Clicking "Start iBEMS" will lauch the web server and all 3 agents as well as launch the computer's web browser and load the login page automatically
        \item If the user accidentally clicks "Start iBEMS" while it already running, a warning message will appear to prevent errors
        \item Clicking "Stop iBEMS" will stop the web server and agents and close the web browser
    \end{itemize}
\end{frame}

\begin{frame}{Startup Menu Functions}{}
    \begin{figure}
        \centering
        \includegraphics[scale=0.45]{figs/GUI_Diagram.png}
        \caption{Diagram for Startup Menu Functionality}
        \label{fig:GUI_Diagram}
    \end{figure}
\end{frame}

% System Architecture Diagram
\begin{frame}{Home Page}{} % Brian
    % High-Level Architecture Figure
    \begin{figure}
        \centering
        \includegraphics[scale=0.2]{figs/Home_screen.png}
        \caption{Home Screen}
        \label{fig:Home_screen}
    \end{figure}

    \begin{small}
    \begin{itemize}
        \item This will be loaded when iBEMS is first booted and it simply shows some current data about the weather 
        \item The Home Page is also accessible by clicking the Home Icon in the upper left corner
    \end{itemize}
    \end{small}
\end{frame}

\begin{frame}{Active Devices Page}{} % Elliot 
    \begin{multicols}{2}
        \begin{figure}
            \centering
            \includegraphics[scale=0.13]{figs/ActiveDevices_screen.png}
            \caption{Active Devices Page}
            \label{fig:active_devices}
        \end{figure}
        %\textsc{}
        \begin{itemize}
            \item Page allows users to directly control available devices in real time
            \item WeMo Insight Smart Plug can be turned on and off
            \item PWM duty cycle of the embedded computer can be adjusted in increments of 0.1
        \end{itemize}
    \end{multicols}
\end{frame}

\begin{frame}{WeMo Power Plot}{} % Brian
    \begin{figure}
        \centering
        \includegraphics[scale=0.15]{figs/ActiveDevices_plot.png}
        \caption{Active Devices Plot}
        \label{fig:active_devices_plot}
    \end{figure}

    \begin{small}
        \begin{itemize}
            \item Clicking "View Status Plots" launches modal
            \item User can select any day and view the power usage
        \end{itemize}
    \end{small}
\end{frame}

\begin{frame}{Scheduling/Applications Page}{} % Elliot

    \begin{multicols}{2}
        \begin{figure}
            \centering
            \includegraphics[scale=0.15]{figs/Applications_screen.png}
            \caption{Scheduling Page}
            \label{fig:schedulingl}
        \end{figure}
        \textsc{}
        \begin{itemize}
            \item Clicking on "Applications" on the nav bar loads the weekly scheduling feature
            \item User can input whatever times they want with devices to be in a specified state (on/off for WeMo plug and duty cycle for the embedded computer)
        \end{itemize}
    \end{multicols}
\end{frame}

\begin{frame}{Conclusion}{} % Elliot
    \begin{multicols}{2}
        \begin{figure}
            \centering
            \includegraphics[scale=0.8]{figs/logo.pdf}
            \label{fig:logo}
        \end{figure}
        \begin{small}
            \begin{itemize}
                \item Advantages: open source, simple interface, modular agent-based code base
                \item Disadvantages: can only operate on a LAN, lacks features of a commercial BEMS system
                \item Challenges: adapting the platform for an enterprise network in a commercial building, security features 
            \end{itemize}
        \end{small}
    \end{multicols}
\end{frame}

\begin{frame}{Conclusion}{}
    Future Improvements:
    \begin{itemize}
        \item Refactor the user interface
        \item Granular user access control
        \item Refactor agent communication
        \item Intelligent algorithms
        \item Mobile app
        \item Persistent device information storage
    \end{itemize}
\end{frame}

\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:

### 2021-04-26 finalPresentation.tex
Updated finalPresentation.tex including circuit diagram

@@
 
-\title[Final Presentation]{Intelligent Building Energy Management System}
+\usepackage{siunitx}
+\sisetup{unitsep=\cdot}
+
+\usepackage{tikz}
+% load libraries
+\usetikzlibrary{backgrounds,calc,patterns,decorations.pathmorphing,decorations.markings,shapes,arrows,snakes,tikzmark}
+\usepackage[siunitx,smartlabels]{circuitikzgit}
+\def\smgrid{0.5}
+% For compact drawing of resistors and capacitors 1
+\ctikzset{resistors/scale=0.5,
+  capacitors/scale=0.6,
+  sources/scale=0.9} 
+\ctikzset{
+  amplifiers/fill=cyan,
+  sources/fill=green!50,
+  diodes/fill=red,
+  resistors/fill=violet,
+}
+
+\title[iBEMS]{Intelligent Building Energy Management System}
 
@@
 
-\author[B.~Lauer, E.~Watkins]{Brian~Lauer \and Elliot~Watkins \and
+\author[B.~Lauer, E.~Watkins]{Brian~Lauer \and Elliot~Watkins\\
 Advisor: Dr. Suruz Miah}
@@
 % the beginning of each subsection:
-\AtBeginSubsection[]
+\AtBeginSection[]
 {
@@
 
-% \begin{frame}{Outline} %
-%   \tableofcontents%[pausesections]
-%   % You might wish to add the option [pausesections]
-% \end{frame}
+\begin{frame}{Outline} %
+  \tableofcontents%[pausesections]
+  % You might wish to add the option [pausesections]
+\end{frame}
 
@@
 \section{Introduction}
-\section{Architecture}
-\section{Embedded/Robotics Computer}
-\section{WeMo Insight Switch}
-\section{Overall Setup}
-\section{Home Page}
-\section{Active Devices Page}
-\section{WeMo Power Plot}
-\section{Scheduling/Applications Page}
-\section{Conclusion}
 
@@
     % Applications of Building Energy Management
-    \begin{multicols}{2}
+    % \begin{multicols}{2}
+      % \begin{block}{}
+  \begin{columns}
+    \column{0.5\textwidth}
+    \begin{block}{}
       \begin{small}
@@
           \end{itemize}
-                \item Overall Goal
-                    \begin{itemize}
-                        \item Create a platform in which users can login and access 2 or 3 IoT devices connected to a building’s energy supply
-                        \item Allow the user to closely monitor energy usage for a residential building.
-                    \end{itemize}
         \end{itemize}
       \end{small}
+    \end{block}
+    \column{0.5\textwidth}
+    {\small
+      \begin{block}{Overall Goal}
+        Overall Goal:
+        \begin{itemize}
+        \item Create a platform in which users can login and access $2$ or $3$ IoT devices connected to a building's energy supply
+        \item Allow user to closely monitor energy usage for residential building
+        \end{itemize}
+      \end{block}
+      }
     \begin{figure}
       \centering
-        \includegraphics[scale=0.4]{figs/BEMS_Image.jpg}
+      \includegraphics[scale=0.25]{figs/BEMS_Image.jpg}
       \caption{General BEMS}
@@
     \end{figure}
-    \end{multicols}
+  \end{columns}
+
+      % \end{block}
+    % \end{multicols}
 \end{frame}
 
+\section{Architecture}
 \begin{frame}{Architecture}{} % Brian
@@
 
+\section{Embedded/Robotics Computer}
 \begin{frame}{Embedded Computer Receiver Program}{}
@@
 \begin{frame}{Embedded Computer Circuit for Power Usage Data}{}
-    \begin{figure}
-        \centering
-        \includegraphics[scale=0.7]{figs/Beaglebone_Circuit.png}
-        \caption{Circuit to Measure Power Usage}
-        \label{fig:Beaglebone_Circuit}
-    \end{figure}
+    \begin{circuitikz}[american]
+      \tikzstyle{every node} = [font = \tiny]
+      % \usetikzlibrary{patterns}
+
+      \draw
+      (0,0) to[sqV,invert,l=PWM Signal from embedded computer] ++(0,4*\smgrid)
+      to[Telmech=M,n=motor,fill=red!20] ++(4*\smgrid,0)
+      to[C,l=$1~{[}\micro\farad{]}$,*-*] ++(0,-4*\smgrid) to[short]++(-4*\smgrid,0); 
+      \draw
+      (4*\smgrid,4*\smgrid) to[short,-*]++(3*\smgrid,0)
+      to[short,-o]++(2*\smgrid,0)node[right]{Embedded Computer ADC (Ch\#0)};
+      \draw
+      (7*\smgrid,4*\smgrid) to[R,l=$2~{[}\ohm{]}$,-*]++(0,-4*\smgrid)
+      to[short]++(-4*\smgrid,0);
+      \draw
+      (7*\smgrid,0) to[short,-o]++(2*\smgrid,0) node[right]{Embedded
+        Computer ADC (Ground)};
+    \end{circuitikz}
+
+    % \begin{figure}
+    %     \centering
+    %     \includegraphics[scale=0.7]{figs/Beaglebone_Circuit.png}
+    %     \caption{Circuit to Measure Power Usage}
+    %     \label{fig:Beaglebone_Circuit}
+    % \end{figure}
     \begin{itemize}
@@
 % \end{frame}
+\section{WeMo Insight Switch}
 
@@
 
-\begin{frame}{Overall Setup}{} % Elliot 
+\section{Overall Experimental Setup}
+\begin{frame}{Overall Experimental Setup}{} % Elliot 
     \begin{figure}
@@
 \end{frame}
+\section{Home Page}
 
@@
 
+\section{Conclusion}
 \begin{frame}{Conclusion}{} % Elliot
-    \begin{multicols}{2}
+  \begin{columns}
+    \column{0.5\textwidth}
     \begin{figure}
@@
     \end{figure}
-        \begin{small}
+    \column{0.5\textwidth}
     \begin{itemize}
@@
     \end{itemize}
-        \end{small}
-    \end{multicols}
+  \end{columns}  
 \end{frame}
 
-\begin{frame}{Conclusion}{}
-    Future Improvements:
+\begin{frame}
+  \begin{block}{Further Improvements}
     \begin{itemize}
@@
     \end{itemize}
+  \end{block}
 \end{frame}

### 2021-04-27 finalReportPres.tex
updated pres

--- 2021-04-26 finalPresentation.tex
@@
 \usetikzlibrary{backgrounds,calc,patterns,decorations.pathmorphing,decorations.markings,shapes,arrows,snakes,tikzmark}
-\usepackage[siunitx,smartlabels]{circuitikzgit}
+\usepackage[siunitx,smartlabels]{circuitikz}
 \def\smgrid{0.5}
@@
   \begin{columns}
-    \column{0.5\textwidth}
+    \column{0.45\textwidth}
     \begin{block}{}
@@
       \begin{block}{Overall Goal}
-        Overall Goal:
         \begin{itemize}
@@
   \end{columns}
-
-      % \end{block}
-    % \end{multicols}
 \end{frame}
@@
 \begin{frame}{Architecture}{} % Brian
-    \begin{multicols}{2}
+    \begin{columns}
+        \column{0.5\textwidth}
+        {\small
         \begin{figure}
@@
         \end{figure}
-        \textsc{}
+        }
+        \column{0.45\textwidth}
+        {\small
+            \begin{block}{}
                 \begin{itemize}
                     \item iBEMS currently has support for 2 IoT devices (WeMo Insight Switch and embedded computer) and can download weather data for the user
-            \item A microgrid with a smart meter will be simulated in the near future
+                    \item A microgrid with a smart meter could theoretically simulated and connected to by the BEMS core
                 \end{itemize}
-    \end{multicols}
+            \end{block}
+        }
+    \end{columns}
 \end{frame}
@@
 \begin{frame}{Architecture}{} % Brian
-    \begin{multicols}{2}
+    \begin{columns}
+    \column{0.5\textwidth}
         \begin{figure}
@@
         \end{figure}
-
+    \column{0.45\textwidth}
+        \begin{block}{}
             \begin{small}
@@
             \end{small}
-    \end{multicols}
+        \end{block}
+    \end{columns}
 \end{frame}
@@
 \begin{frame}{Operational Modes}{}
+    \begin{columns}
+    \column{0.5\textwidth}
+      \begin{figure}
+        \centering
+        \includegraphics[scale=0.4]{figs/operationalModes.pdf}
+        \caption{Operation Modes Interaction}
+        \label{fig:functional_bd}
+      \end{figure}
+    \column{0.45\textwidth}
+      \begin{block}{}
         \begin{enumerate}
@@
         \end{enumerate}
+    \end{block}
+    \end{columns}
+
 \end{frame}
 
-\begin{frame}{System Components}{}
+\begin{frame}{Agent Communication Architecture}{}
     \begin{figure}
@@
         \label{fig:systemComponentInterconnection}
-    \end{figure}
-\end{frame}
-
-\begin{frame}{Control Agent Functionality}{}
-    \begin{figure}
-        \centering
-        \includegraphics[scale=0.6]{figs/controlAgentUML.pdf}
-        \caption{Control Agent Class Diagram}
-        \label{fig:controlAgentClass}
-    \end{figure}
-\end{frame}
-
-\begin{frame}{Discovery Agent Functionality}{}
-    \begin{figure}
-        \centering
-        \includegraphics[scale=0.6]{figs/discoveryAgentUML.pdf}
-        \caption{Discovery Agent Class Diagram}
-        \label{fig:discoveryAgentClass}
-    \end{figure}
-\end{frame}
-
-\begin{frame}{Scheduling Agent Functionality}{}
-    \begin{figure}
-        \centering
-        \includegraphics[scale=0.6]{figs/schedulingAgentUML.pdf}
-        \caption{Scheduling Agent Class Diagram}
-        \label{fig:schedulingAgentClass}
     \end{figure}
@@
 
-\section{Embedded/Robotics Computer}
-\begin{frame}{Embedded Computer Receiver Program}{}
-    \begin{figure}
-        \centering
-        \includegraphics[scale=0.45]{figs/Beaglebone_Receiver_Diagram.png}
-        \caption{Receiver Running on Embedded Computer}
-        \label{fig:Beaglebone_Receiver_Diagram}
-    \end{figure}
-\end{frame}
+\section{Hardware}
+% \section{Embedded/Robotics Computer}
 
@@
       \draw
-      (0,0) to[sqV,invert,l=PWM Signal from embedded computer] ++(0,4*\smgrid)
+      (0,0) to[sqV,invert,l=Motor Drive Voltage from H-Bridge] ++(0,4*\smgrid)
       to[Telmech=M,n=motor,fill=red!20] ++(4*\smgrid,0)
@@
 
-    % \begin{figure}
-    %     \centering
-    %     \includegraphics[scale=0.7]{figs/Beaglebone_Circuit.png}
-    %     \caption{Circuit to Measure Power Usage}
-    %     \label{fig:Beaglebone_Circuit}
-    % \end{figure}
+    \begin{block}{}
       \begin{itemize}
@@
       \end{itemize}
+    \end{block}
 \end{frame}
@@
     \end{multicols}
+    \begin{block}{}
       \begin{small}
@@
       \end{small}
+    \end{block}
 \end{frame}
 
-% \begin{frame}{Frame Title}
-%     \begin{figure}
-%         \centering
-%         \includegraphics{}
-%         \caption{Caption}
-%         \label{fig:my_label}
-%     \end{figure}
-% \end{frame}
-\section{WeMo Insight Switch}
-
 \begin{frame}{WeMo Insight Switch}{} % Elliot 
-    \begin{multicols}{2}
+    \begin{columns}
+    \column{0.5\textwidth}
       \begin{figure}
@@
       \end{figure}
-        \textsc{}
+    \column{0.4\textwidth}
+     \begin{block}{}
         \begin{itemize}
@@
         \end{itemize}
-    \end{multicols}
+     \end{block}
+    \end{columns}
 \end{frame}
 
-\section{Overall Experimental Setup}
+% \section{Overall Experimental Setup}
 \begin{frame}{Overall Experimental Setup}{} % Elliot 
@@
     \end{figure}
+    \begin{block}{}
       Tested the WeMo Insight Switch with a bank of lights and the embedded computer with a robot chassis
+    \end{block}
+\end{frame}
 
+\section{Software Implementation}
+
+\begin{frame}{Control Agent Functionality}{}
+    \begin{figure}
+        \centering
+        \includegraphics[scale=0.3]{figs/periodicQueryBehaviorFlow.pdf}
+        \caption{periodicQueryBehavior Flow Chart}
+        \label{fig:periodicQueryBehavior}
+    \end{figure}
 \end{frame}
-\section{Home Page}
+
+\begin{frame}{Discovery Agent Functionality}{}
+    \begin{figure}
+        \centering
+        \includegraphics[scale=0.4]{figs/setDeviceToActiveFlow.pdf}
+        \caption{setDeviceToActive Flow Chart}
+        \label{fig:setDeviceToActive}
+    \end{figure}
+\end{frame}
+
+\begin{frame}{Discovery Agent Functionality}{}
+    \begin{figure}
+        \centering
+        \includegraphics[scale=0.3]{figs/searchForDevicesFlow.pdf}
+        \caption{searchForDevices Flow Chart}
+        \label{fig:searchForDevices}
+    \end{figure}
+\end{frame}
+
+\begin{frame}{Embedded Computer Receiver Program}{}
+    \begin{figure}
+        \centering
+        \includegraphics[scale=0.30]{figs/Beaglebone_Receiver_Diagram.pdf}
+        \caption{Receiver Running on Embedded Computer}
+        \label{fig:Beaglebone_Receiver_Diagram}
+    \end{figure}
+\end{frame}
 
@@
             \centering
-            \includegraphics[scale=0.4]{figs/bemsGUI.png}
+            \includegraphics[scale=0.2]{figs/BEMS_GUI_Linux.png}
             \caption{Desktop GUI}
@@
             \centering
-            \includegraphics[scale=0.5]{figs/bemsGUIError.png}
+            \includegraphics[scale=0.35]{figs/BEMS_GUI_Linux_Warning.png}
             \caption{Popup Error}
@@
     \end{multicols}
+    \begin{block}{}
       \begin{itemize}
@@
     \end{itemize}
+    \end{block}
 \end{frame}
@@
         \centering
-        \includegraphics[scale=0.45]{figs/GUI_Diagram.png}
+        \includegraphics[scale=0.4]{figs/GUI_Diagram.pdf}
         \caption{Diagram for Startup Menu Functionality}
@@
     \end{figure}
-
+    \begin{block}{}
       \begin{small}
@@
       \end{small}
+    \end{block}
 \end{frame}
@@
 \begin{frame}{Active Devices Page}{} % Elliot 
-    \begin{multicols}{2}
+    \begin{columns}
+    \column{0.5\textwidth}
       \begin{figure}
@@
         \end{figure}
-        %\textsc{}
+    \column{0.45\textwidth}
+        \begin{block}{}
           \begin{itemize}
@@
         \end{itemize}
-    \end{multicols}
+        \end{block}
+    \end{columns}
 \end{frame}
@@
 
-    \begin{multicols}{2}
+    \begin{columns}
+    \column{0.5\textwidth}
       \begin{figure}
@@
         \end{figure}
-        \textsc{}
+        \column{0.45\textwidth}
+        \begin{block}{}
           \begin{itemize}
@@
     \end{figure}
-    \column{0.5\textwidth}
+    \column{0.45\textwidth}
+    \begin{block}{}
       \begin{itemize}
@@
     \end{itemize}
+    \end{block}
   \end{columns}  
@@
 
-\begin{frame}
+\begin{frame}{Conclusion}{}
   \begin{block}{Further Improvements}

### 2021-04-30 parts/02-abstract.tex
Added final report files

% A B S T R A C T
% ---------------

\begin{center}\textbf{Abstract}\end{center}

%This paper proposes a strategy for testing and comparing three control algorithms, LQR, LQG, and ADP, to control two two-DOF helicopters from a mobile device.  We will be using Raspberry Pi 3's as terminals for the wireless communication and MATLAB as our primary coding language.

Smart building energy management and/or monitoring has recently emerged as a
promising task due to global climate change issues. Such a task has received thorough attention
due to the advent of emerging Internet-of-Things (IoT) technology. Numerous building energy
management systems are commercially available in the market. Most of them lack modularity
or are driven by an overwhelming degree of manual configurations for performing building
automation. In this project, we develop a modular IoT-based framework for a smart building
energy management system (BEMS). The proposed framework is open-source and leverages the
features of decentralized multi-agent systems. The principal component of the framework is the
BEMS core that implements building automation features, such as an optimal scheduler,
displaying weather information, detecting new IoT devices, monitoring energy consumption,
and remotely controlling operation of IoT devices.
\cleardoublepage
%\newpage

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../finalReportMainV1"
%%% End:

### 2021-04-30 parts/03-acknowledgements.tex
Added final report files

% A C K N O W L E D G E M E N T S
% -------------------------------

\begin{center}\textbf{Acknowledgements}\end{center}

    \par Thanks to Dr. Suruz Miah for his advisement and preliminary work on this project.
    \par Thanks to Mr. Christopher Mattus for his assistance in setting up our lab environment.
    \par Thank you to everyone else who helped make this project possible and successful.

\cleardoublepage
%\newpage

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../finalReportMainV1"
%%% End:

### 2021-04-30 parts/10-introduction.tex
Added final report files

%======================================================================
\chapter{Introduction}
\label{ch: Chapter1}
%======================================================================

\section{Project Description}
The Internet of Things is a large network of embedded devices like sensors, wearables, and appliances capable of receiving control commands and reporting data over the Internet. Many industries take advantage of this infrastructure to improve process flow and efficiency. One of these industries is the commercial and industrial sector which often employ building automation or management systems to help better manage processes or devices in a building like air conditioning systems, lights or industrial machines. Technological advancements have allowed devices to become connected to a building network through communication protocols like WiFi, Ethernet, Modbus, or BACnet which enables them to be more easily controlled from a central system.
\medbreak\noindent
Our overall goal is to create a platform in which users can login and access devices connected to a building's energy supply. This will allow the user to closely monitor energy usage throughout a commercial or residential building. Additionally, the user will be able to control devices connected to the platform, allowing precise control over the building's energy use. The minimum viable product of this project will be to connect to 1 to 3 devices via the the platform and control them.

\section{Prior Work}
The previous senior project group worked on creating a remote motor control system with a Raspberry Pi and XBee module. To supply power directly to the motor and XBee with a single power supply, they used a buck-boost converter capable of stepping down power supply voltage to 3.3 V. They implemented a Python script that uses the Linux command \texttt{nmap} to search for the Raspberry Pi on the network. The Raspberry Pi connects to the transmitter XBee via a serial connection to transmit commands to the receiver XBee mounted to the motor. They were able to simply toggle the motor on and off and partially implemented this functionality in BEMOSS (Building Energy Management Open Source Software). A second portion of their project was implementing an HVAC control algorithm capable of controlling the temperature of a home with the Linear Quadratic Regulator control algorithm.

During a research project with Dr. Miah, the DC motor interface was successfully implemented into the BEMOSS platform which required adding a great deal of code to the platform to fully implement the device as BEMOSS does not support adding new devices currently. The research also consisted of adding a new logo to the platform for the motor. A possible improvement our platform will make is helping developers on the project to add new devices more easily.

One of the improvements our project makes over the previous is the use of UDP multicasting which does not require any superuser privileges to locate an embedded computer (Beaglebone Blue). This implementation is also more convenient because it does not require installing any packages as multicasting is natively supported by most embedded Linux systems. If in the future, multiple embedded computers are needed to be discovered, the multicasting system works elegantly as each device can simply listen on a provided multicast group which consists of an IP address and port number.

\section{Background Study}
A great deal of research has been conducted in the field of building energy management. Multiple different platforms have been developed that demonstrate the vast amount of features and possibilities that exist in developing these types of software.

One such platform is BEMOSS from the Virginia Polytechnic Institute and State University Advanced Research Institute. BEMOSS features include being open-source, allowing for multiple communication technologies, and supporting many common IoT devices. This system allows for monitoring and controlling a variety of devices securely.

Another open-source platform is rEMpy or residential Energy Management in python. The main focus of this platform developed by a team of researchers at Universit\`{a} Politecnica delle Marche in Ancona, Italy was to simulate the energy flow of a residential home. With the data collected from simulations, it was possible for them to use forecasting and prediction algorithms to predict various quantities like energy usage and power consumption over a given time period. Their energy management system consists of a well-defined structure with components like a user interface, database, and optimal scheduler that communicates with modules like a prediction and thermal model. In terms of software technologies, it uses the Django web framework which provides a lot of built-in functionality for web development like a user-authentication system and object-relational mapping. Adapting the project to this framework could be a great way to help improve security and optimize database queries \cite{fagiani2017}.

One of the works in the literature discusses Model Predictive Control (MPC) which is a modern process control algorithm capable of taking into account current and previous time values to improve building automation~\cite{Mayer2017}. A multilevel hierarchy is presented to split control of a building into two levels: the energy supply level and user level. Example usage of this control scheme provided are temperature control of a building and its corresponding zones and interaction with a smart grid. Studies were performed on a commercial building with the building's energy supply system and hierarchy model predictive controller implemented in Matlab.

In~\cite{8246800}, the authors describe similar functional requirements to our own BEMS Core. They periodically gather power consumption and device status data and send that data to a database. We are doing exactly what they describe using the Apache Cassandra database. The authors also use an "analytics [sic] engine to process [the data] and generate reports, graphs, and charts." Our system only generates a power consumption plot for a given day, but we are still meeting this same requirement - just on a smaller scale. The communication with devices and power consumption reports are to be accessible through a web-based application that is easy to use. Again, our implementation is simple and very intuitive for the end-user. Finally, these authors mention a user-login feature. They explain that their system would include multiple levels of accessibility based on the user privileges. Although our system does not currently have a user-login feature, it simply uses a router to access devices that are also connected to the router. Since this is a closed system, users need only protect their router with a secure password.

A control scheme in~\cite{Barchi2018} is presented to manage a photovoltaic array and battery energy storage system. Tests were conducted in a shopping mall with an electronic load to emulate the power consumption of the building. Potentially, a similar technique could be used to model the energy demand of a house in Simulink or Simscape model. Through their scheme, an intelligent BEMS is used to collect measurable data like power, voltage, and current and stored for offline analysis later. Their platform collects data every five minutes compared to the 20 second polling rate currently configured in our platform. A control algorithm was presented proving that grid energy is consumed more heavily during periods of low power demand rather than PV power.

% \section{Problem Statement}
% Despite several open-source building energy management platforms, such as BEMOSS, available in the market, the need for an effective and efficient open-source building energy management platform that takes into account the planning and technical challenges in integrating different load controllers
% with the microgrid as well as the smart grids is quite prominent. The proposed energy management platform is expected to address the huge energy demand in residential and commercial buildings despite limited number of sources of energy by incorporating learning, control, and estimation strategies as discussed in the following section.

% A high level architecture of the proposed building energy management system integrating different components of power systems and smart devices is shown in Figure 2. A microgrid is connected to the main grid through a Point of Common Coupling (PCC) to enable or disable islanded mode operation. Various renewable DERs are connected within the microgrid which have the capability of either supplying energy directly to the main grid or storing energy in energy storage devices such as batteries or supercapacitors. The core system will facilitate communication between many different building systems and electrical devices within a building. Examples of different systems include lighting systems and HVAC systems. Smart meters can enable two-way communication between an energy supplier and the BEMS. Various IoT appliances and devices in the building including washing machines, refrigerators, smart TVs, dishwashers, and WiFi-enabled PHEV chargers can be configured for communication with the central system to help optimize electrical consumption. Uncontrollable loads like computers and microwaves may be monitored for power consumption statistics and temperature measuring devices can be connected for determining proper HVAC operation. Utility operators, Ameren, for instance, can be utilized for demand response purposes. Lastly, mobile devices including smart phones and tablets can be used to remotely monitor data from the BEMS core. Usually, a building energy management system is primarily aimed in minimizing energy consumption through building automation strategies and the usage of energy management policies
% and algorithms. The building energy management platform, BEMOSS, developed by researchers at the Virginia Tech research lab, focuses mainly on incorporating building automation strategies, which is currently being used as a starting point for the proposed BEMS platform. The existing BEMOSS platform, for example, contains features for controlling electronic/electrical devices such as scheduling, power consumption monitoring, device control, and usage monitoring. However, no learning, control, and estimation strategies have been developed to help buildings lower energy costs, address the energy demand and smart integration microgrid and smart grid, which proves to be a potential shortcoming of the current BEMOSS.

The ultimate goal of this research is to design and develop a new building energy management
platform incorporating learning, control, and estimation strategies, which is expected to remedy the
shortcomings of some existing platforms, BEMOSS, for instance.

%----------------------------------------------------------------------
\section{Report Organization}
%----------------------------------------------------------------------
This report is organised into 5 chapters.  Chapter \ref{ch: Chapter1} discusses what this project hopes to accomplish and what similar projects have completed. Chapter \ref{ch: Chapter2} explains the architecture. Chapter \ref{ch: Chapter3} provides a brief explanation of the control algorithms and architectures used. Chapter \ref{ch: Chapter4} contains the results from our simulations. Chapter \ref{ch: Chapter5} concludes the paper and provides insight into future directions.

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../finalReportMainV1"
%%% End:

### 2021-04-30 parts/20-iBEMSArchitecture.tex
Added final report files

\chapter{iBEMS Architecture}
\label{ch: Chapter2}

\begin{figure}[H]
    \centering
    \includegraphics[scale=0.8]{figs/highLevelArchitecture.pdf}
    \caption{High Level Architecture of the Proposed System}
    \label{fig:highLevelArchitecture}
\end{figure}

At the center of the iBEMS architecture is the iBEMS core. This core interacts with multiple peripherals including IoT devices and a weather API over the internet. Over the course of this project, we managed to develop support for 2 IoT devices displayed in Figure~\ref{fig:highLevelArchitecture}. These devices are the WeMo Insight Switch and an embedded computer known as the Beaglebone Blue. Our initial plan for the smart meter shown in Figure~\ref{fig:highLevelArchitecture} was to use it in a Simscape model of a microgrid. However, we did not list this as a requirement for the project, so we decided not to implement it due to time constraints. The core is also able to connect the internet to download weather data for Peoria, Illinois through OpenWeatherMap.

\section{Low Level Architecture}
\begin{figure}[H]
    \centering
    \includegraphics[scale=0.8]{figs/functionalBlockDiagram.pdf}
    \caption{Functional Block Diagram}
    \label{fig:functional_bd}
\end{figure}

Figure~\ref{fig:functional_bd} gives lower level detail on the system architecture. The inputs include the user input through the web server, the device status updates (On/Off, power usage, etc...) and the weather data. The iBEMS Core itself consists of a Flask Web Server, 2 databases (Apache Cassandra and SQLite), and 3 software agents (Discovery, Control, and Scheduling).
\medbreak
The Flask web server is built using a Python web framework titled Flask which allows programmers to develop a dynamic web server capable of rendering data to HTML pages. The benefit of this framework over other Python web frameworks like Django is the large amount of customization available. For example, the developers can create a completely custom user login system. For now, the server is capable of being accessed only on the server computer running Ubuntu Linux. In the future, support could be added to allow any user on the LAN to access the web server. Other web frameworks use object relational mapping directly to access the relevant databases. However, our system uses direct queries with both SQLite and the Cassandra query language to query the database.
\medbreak
We used 2 different databases to store information on. The Apache Cassandra database was better suited for the time series data such as device status and power usage. This database was therefore utilized a lot by the Control and Scheduling Agents. The SQLite database hold parameters that do not change over time like device ID's, IP addresses, and MAC addresses which made it amendable to the processes in the Discovery Agent. A possible improvement to this project could be to only utilize 1 database for development simplicity.
\medbreak
The first agent that is used by the iBEMS Core on startup is the discovery agent. It is responsible for reaching out on the network and finding all devices that the iBEMS Core has support for. This process involves retrieving the following parameters: IP address, Port number, MAC address, Manufacturer, Name, and API.
Once all available devices are connected, the Control agent is used to change the status of each device and collect power usage data in real time. Finally, the scheduling will take input from the user and place the corresponding scheduling periods in the Apache Cassandra database. Then, a thread is created to poll the current device status at regular intervals and updates the status if it does not match the defined status in the Apache Cassandra database.

\begin{figure}[H]
    \centering
    \includegraphics[scale=0.6]{figs/overallDiagram.pdf}
    \caption{Interconnection between system components}
    \label{fig:systemComponentInterconnection}
\end{figure}

Figure~\ref{fig:systemComponentInterconnection} provides an explanation of how the components of the system interact with each other. The Apache Cassandra database and SQLite database are accessible from the web server, control agent, discovery agent, and scheduling agent. The web server queries the time series database and metadata database for vastly different purposes. Power plotting requires querying the Apache Cassandra database. To distinguish between the different devices on the front end, the metadata database is used. The agents utilize the Apache Cassandra database for storing and extracting time-series data. The agents use the metadata database to distinguish between different devices.

\section{Modes of Operation}

\begin{figure}[H]
    \centering
    \includegraphics[scale=0.9]{figs/operationalModes.pdf}
    \caption{Operation Modes Interaction}
    \label{fig:functional_bd}
\end{figure}

There are 5 general modes of operation in iBEMS. In Mode 0, before iBEMS is even launched, the user must open the Startup Menu, which is a desktop graphical user interface (GUI). This is a simple GUI with only 2 buttons for starting and stopping iBEMS. Upon clicking "Start iBEMS," the login page will load where the user can enter a valid username and password to use iBEMS. Once a valid username and password is entered, the home screen will be shown which displays the weather data being downloaded from the OpenWeatherMap API. This information include temperature in Fahrenheit and Celsius, wind speed in MPH, humidity, and cloud coverage. At this point, a navigation bar is available to view "Active Devices" page and the "Scheduling" page. "Active Devices" corresponds to Mode 3 for controlling devices in real time. The user will also be able to view power plots in this mode as well. Lastly, the "Scheduling" page is Mode 4 for creating schedules for all connected devices.

\section{Hardware}

\begin{circuitikz}[american]
    \tikzstyle{every node} = [font = \tiny]
      % \usetikzlibrary{patterns}
      \draw
      (0,0) to[sqV,invert,l=Motor Drive Voltage from H-Bridge] ++(0,4*\smgrid)
      to[Telmech=M,n=motor,fill=red!20] ++(4*\smgrid,0)
      to[C,l=$1~{[}\mu F{]}$,*-*] ++(0,-4*\smgrid) to[short]++(-4*\smgrid,0); 
      \draw
      (4*\smgrid,4*\smgrid) to[short,-*]++(3*\smgrid,0)
      to[short,-o]++(2*\smgrid,0)node[right]{Embedded Computer ADC (Ch\#0)};
      \draw
      (7*\smgrid,4*\smgrid) to[R,l=$2~{[}\Omega{]}$,-*]++(0,-4*\smgrid)
      to[short]++(-4*\smgrid,0);
      \draw
      (7*\smgrid,0) to[short,-o]++(2*\smgrid,0) node[right]{Embedded
        Computer ADC (Ground)};
\end{circuitikz}

A large feature of this project was being able to record power usage from the connected IoT devices. The embedded computer does not have a built-in capability to measure its own power usage, so this circuit was needed to make that possible. Essentially, this circuit will measure the current being used to drive one of the motors on the robot chassis. The on-board Analog-to-Digital-Converter (ADC) can be used to read the voltage across the resistor and since the resistance is known, the current can be calculated as $I = V/R$. Also, the voltage from the H-Bridge to drive the motors on the embedded computer is known so the power consumed by 1 motor is $Motor Drive Voltage * I$. For the specific robot chassis used in this project, there are 4 motors, so multiplying the power found from this circuit by 4 will give an approximation of the total power used by the robot. For other robots with different power sources besides a Lipo battery,

% \pagebreak
\begin{figure}[H]
    \centering
    \includegraphics[scale=0.1]{figs/notConnectedSBC.jpg}
    \caption{Embedded Computer Not Connected}
    \label{fig:not_connected_bb}
\end{figure}

Figure~\ref{fig:not_connected_bb} shows the embedded computer mounted on the robot chassis with the circuit shown on page 9. It can also be seen that the embedded computer lights up the on-board red LED when disconnected. Figure~\ref{fig:connected_bb} shows that the embedded computer lights up the green LED when it is connected as an extra indication of its connection status.

\begin{figure}[H]
    \centering
    \includegraphics[scale=0.1]{figs/connectedSBC.jpg}
    \caption{Embedded Computer Connected}
    \label{fig:connected_bb}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[scale=0.085]{figs/wemoView.jpg}
    \caption{WeMo Insight Smart Plug}
    \label{fig:wemo}
\end{figure}

The other supported device is the WeMo Insight Switch as seen in Figure~\ref{fig:wemo}. This device was easy to develop support for as it is meant for building energy management. It simply plugs into a 120 volt 3-prong outlet and any typical household appliance running on 120 volts can be plugged into it. Internal circuitry allows the WeMo to be controlled remotely (turn On/Off) and to record power usage of whatever is plugged into.

\begin{figure}[H]
    \centering
    \includegraphics[scale=0.1]{figs/overallView.jpg}
    \caption{Overall View}
    \label{fig:overallView}
\end{figure}

In order to test these devices, we plugged a bank of 6 light bulbs into the WeMo Insight Switch as seen in Figure~\ref{fig:overallView}. The embedded computer's functionality was tested with the circuit and robot chassis described earlier.

### 2021-04-30 parts/30-Implementation.tex
Added final report files

\chapter{Implementation}
\label{ch: Chapter3}

\section{Agent and Web Server Communication}

% Talk about Zero MQ
All three agents communicate with each other and the web server using the Zero MQ asynchronous messaging library [citation here]. Essentially, this library works as a way to implement inter process communication without a message broker. In other words, different processes are able to communicate with each other without any central bus. This is convenient as fewer processes are needed for the system to function. Lowering the number of overall processes lowers the RAM and CPU usage of the software. The library is ported to many different programming languages; however we are using the Python port titled Pyzmq to implement in our code base. 
\begin{figure}[H]
    \centering
    \includegraphics{figs/pubSubAgents.pdf}
    \caption{Publish Subscribe Communication using ZeroMQ}
    \label{fig:pubSubAgents}
\end{figure}
More specifically, the publish subscribe model of communication is used where each agent communicates via a socket where each socket responds to a specific topic. The topics and port numbers are listed below along with their corresponding agents in Table~\ref{tab:pubsubspecs}.
\begin{table}[H]
    \centering
    \begin{tabular}{|c|c|c|}
        \hline
        Agent & Topic & Port Number\\
        \hline
        Discovery Agent & "discovery" & 5556\\
        Scheduling Agent & "scheduling" & 5556\\
        Control Agent & "control" & 5556\\
        \hline
    \end{tabular}
    \caption{Publish/Subscribe Communication Specifications}
    \label{tab:pubsubspecs}
\end{table}
In order to send data between the different processes, the topic, method, and data are delimited in a particular way. This method is shown below as follows
\begin{verbatim}
    topic method/args
\end{verbatim}
A space cannot be included between the method name and arguments as this interferes with the Python \texttt{split} method for extracting the fields. The \texttt{topic} is the string described previously, the \texttt{method} is the name of the desired method to be called on the agent object, and \texttt{args} is the arguments supplied to the desired method. In order to send a message to an agent, the \texttt{publish} method defined in the \texttt{pubsub} module should be called. An optional argument titled \texttt{cycleCount} is available which will allow the publish message to be sent multiple times. During testing, it was found that during the transmission of some messages, this was necessary due to the way ZeroMQ is implemented.

\section{Agent Functionality}
The agents contained in the software are associated with a Python class of the same name. Each class is instantiated and run with specifications declared in Table~\ref{tab:pubsubspecs}. Some of the methods defined in each class will be described in the following subsections.

\subsection{Control Agent Functionality}
The flow chart of method \texttt{setDeviceStatus} is shown in Figure~\ref{fig:setDeviceStatus}. The purpose of this method is to set the status of the desired device. When the method is called, the data dictionary is obtained which contains the device ID. With this device ID, the API type can be determined using the SQLite database. Subsequently, the appropriate device API module can be imported. If the power state exists as a key in the device data dictionary, the power state of the WeMo Insight Switch will be set as ON or OFF. If the duty cycle key exists, the duty cycle of the single board computer motor drivers is set. If the shutdown key is set, the single board computer is shutdown. In order to reconnect to the single board computer, the board must be started and receiver program ran. If necessary, the device must be reconnected to the WiFi network.  
\begin{figure}[H]
    \centering
    \includegraphics[scale=0.5]{figs/setDeviceStatus.pdf}
    \caption{setDeviceStatus Flow Chart}
    \label{fig:setDeviceStatus}
\end{figure}
To obtain necessary data quantities from the device, the \texttt{getDeviceStatus} method is defined. Once the proper data parameters are obtained, the \texttt{getState} function defined in the devices API module can be called with the data parameters like power state and status. Once the agent has finished sending these to the device, a request is sent to the web server to inform the server that it completed searching for the required device data.

\begin{figure}[H]
    \centering
    \includegraphics[scale=0.5]{figs/getDeviceStatus.pdf}
    \caption{getDeviceStatus Flow Chart}
    \label{fig:getDeviceStatus}
\end{figure}

Every device connected to iBEMS will have a thread associated with it started from the control agent. This thread will run the \texttt{periodicQueryBehavior} method to periodically query for device data and store in the corresponding Cassandra database table. A user specified delay is placed in the class's module to prevent the thread from overwhelming the system.
\begin{figure}[H]
    \centering
    \includegraphics[scale=0.5]{figs/periodicQueryBehavior.pdf}
    \caption{periodicQueryBehavior Flow Chart}
    \label{fig:periodicQueryBehavior}
\end{figure}
To reduce latency, the device status is retrieved directly from the API module in the \texttt{periodicQueryBehavior} method rather than calling \texttt{getDeviceStatus} as this prevents the API from being imported unnecessarily.

\subsection{Discovery Agent Functionality}
The purpose of the discovery agent is to search for devices that respond to the supported APIs by the software. A flow chart demonstrating the \texttt{searchForDevices} method is shown in Figure~\ref{fig:searchForDevices}. This method is called whenever the active devices page is loaded. The algorithm could be improved to help page load times. All the device APIs are loaded in the \texttt{findDevices} function defined in each device's API module is called which will return a list of found URLs. Once the device's URL is determined, it's metadata can be passed to the \texttt{setDeviceToActive} method which will set up the device in the two databases.

\begin{figure}[H]
    \centering
    \includegraphics[scale=0.5]{figs/searchForDevices.pdf}
    \caption{searchForDevices Flow Chart}
    \label{fig:searchForDevices}
\end{figure}
The \texttt{setDeviceToActive} shown in Figure~\ref{fig:setDeviceToActive} will first check to make sure the device is not already in the active devices table. Then, it will add the device to the active devices table, create a table in the Cassandra database for storing time-series data, send a message to the scheduling agent to check for schedule updates, and send a message to the control agent to start collecting data.
\begin{figure}[H]
    \centering
    \includegraphics[scale=0.5]{figs/setDeviceToActive.pdf}
    \caption{setDeviceToActive Flow Chart}
    \label{fig:setDeviceToActive}
\end{figure}

\subsection{Scheduling Agent Functionality}
The scheduling agent is able to update the device status of each device dependent on whether a schedule is set for the specific time period and day. One of the methods that is called, \texttt{updateScheduleFromServer} is invoked when the user presses the "Update Schedule" button from the UI on the scheduling page. A flow chart of this method is shown in Figure~\ref{fig:updateScheduleFromServer}. When this method is called the desired schedule is loaded in as a dictionary and parsed to extract the necessary periods and given day. First the times are stored in military time in the database for more convenient storage and parsing later on. Then, a table is created in the Apache Cassandra database for the device for the provided data and the device ID is embedded. The table's data is destroyed to ensure there are no errors regarding overlapping schedules. Lastly, all the scheduling periods extracted from the dictionary are stored as rows in the table. 
\begin{figure}[H]
    \centering
    \includegraphics[scale=0.5]{figs/updateScheduleFromServer.pdf}
    \caption{updateScheduleFromServer Flow Chart}
    \label{fig:updateScheduleFromServer}
\end{figure}
A second method that is run inside each device thread is \texttt{periodicDeviceUpdateMethod} which is started when the discovery agent sets the discovered device to active. By first loading the device's API name, the scheduling agent can begin checking for scheduling periods inside an infinite loop. The status dictionary is queried from the Cassandra database and loaded into a dictionary. All these scheduling periods are looped over for the current day while constantly checking whether the current time in seconds is within the starting and ending time. A conversion of both starting and ending time to seconds is necessary as it is challenging to work with these quantities in standard and military time when comparing times. If the current time does lie inside the scheduling period, the device's state is set dependent on the API. 
\begin{figure}[H]
    \centering
    \includegraphics[scale=0.5]{figs/periodicDeviceUpdateMethod.pdf}
    \caption{periodicDeviceUpdateMethod Flow Chart}
    \label{fig:periodicDeviceUpdateMethod}
\end{figure}

\section{Desktop GUI Functionality}
The functionality of the desktop GUI launched when the user runs the Python script titled \texttt{GUI.py} is shown in Figure~\ref{fig:desktopgui}. Packages used to construct the GUI include tkinter which is a Python interface for the Tcl/Tk GUI toolkit. When the GUI is started up, the title, buttons, and labels are created along with ties to the callback functions \texttt{startCallback} and \texttt{stopCallback}. The \texttt{startCallback} function is called when the user presses the "Start iBEMS" button. This function first checks whether iBEMS is already running by checking for processes already running on the machine including the web server itself and the three agents. This is performed using the command \texttt{ps -aux}. After this has been completed, an error popup is shown preventing another instance of the software from running. This prevents errors associated with copies of agents and web servers running simultaneously. To properly stop the software, the "Stop iBEMS" button will shutdown the software by first finding the process ID's associated with the agents and web server. To perform this, it will place the output of \texttt{ps -aux | grep [process]} into a text file where "process" is the name of the target process. A file descriptor of the process status output text file is instantiated and all the lines are read in to be parsed. Each process output is split by spaces and the second element in the list is denoted as the process id. Then, using the \texttt{kill} command, these processes are killed. 
\begin{figure}[H]
    \centering
    \includegraphics[scale=0.6]{figs/GUI_Diagram.pdf}
    \caption{Python desktop GUI Functionality}
    \label{fig:desktopgui}
\end{figure}

\section{Embedded Computer}

\begin{figure}[H]
    \centering
    \includegraphics[scale=0.5]{figs/Beaglebone_Receiver_Diagram.pdf}
    \caption{Receiver Running on Embedded Computer}
    \label{fig:Beaglebone_Receiver_Diagram}
\end{figure}

The embedded computer needed some software to be able to connect to and communicate with the iBEMS Core. To achieve this, a program consisting of 2 functions for connecting and communicating is used.
\medbreak
The first of these functions is \texttt{connect\_to\_iBEMS}. This function first turns on the red LED on the embedded computer to indicate it is not yet connected. Then it creates a socket using a multicast IP address that the corresponding API in the iBEMS core will be looking for. Once the socket is created, the embedded computer will enter a loop and wait for the iBEMS core to make the initial connection. When that connection is made, it will exit the loop, save the IP address of the iBEMS core, send a confirmation message, then turn on the green LED before closing the multicast socket.
\medbreak
The second function, \texttt{communicate\_with\_iBEMS} will open another socket but with the IP address of the iBEMS core found in \texttt{connect\_to\_iBEMS}. It will then enter a indefinite loop to continually receive data from the iBEMS core. There are 4 different messages that the iBEMS core sends to the embedded computer. First, it will check if the iBEMS core is telling it to shut down with the command "Shutdown." If so, the embedded computer will immediately shut down. Second, if the data sent by iBEMS is "status," the embedded computer will take a reading from the circuit described in Chapter~\ref{ch: Chapter2} section 3. In case the user decides to shut down the iBEMS core without turning off the embedded computer, another message "disconnect" will be sent in which case the embedded computer will exit \texttt{communicate\_with\_iBEMS} and start the entire program over again. Finally, if iBEMS is not sending any of the above options, it means that the user is sending a new duty cycle to drive the motors with. Since iBEMS only sends messages with the string data type, this has to be converted to a float in order to call the motor driver function.

### 2021-04-30 parts/40-ExperimentalResults.tex
Added final report files

\chapter{Experimental Results}
\label{ch: Chapter4}

As part of this project, we developed a working prototype. As explained in Chapter~\ref{ch: Chapter2} section 2, the first mode is the startup menu:

\begin{figure}[H]
    \centering
    \includegraphics[scale=0.5]{figs/BEMS_GUI_Linux.png}
    \caption{Desktop GUI}
    \label{fig:desktopgui}
\end{figure}

\noindent
Here, the user will simply click the "Start iBEMS" button to launch the web server and agents. When the user is finished, all agents and the web server can be shut down by clicking "Stop iBEMS." In case the user accidentally clicks the "Start iBEMS" button while iBEMS is already running, then the following error message will appear:

\begin{figure}[H]
    \centering
    \includegraphics[scale=0.5]{figs/BEMS_GUI_Linux_Warning.png}
    \caption{Popup Error}
    \label{fig:popuperror}
\end{figure}

\noindent
After launching iBEMS, the web browser will open and the user will presented with the login page:

\begin{figure}[H]
    \centering
    \includegraphics[scale=0.5]{figs/Login.png}
    \caption{Login Page}
    \label{fig:Home_screen}
\end{figure}

\noindent
where the user can enter in their username and password. Currently, iBEMS does not have a robust user login. It actually just has 1 username and password that is defined in the code. When the user enters the valid username and password, the home page will load automatically, where the weather data can be seen:

\begin{figure}[H]
    \centering
    \includegraphics[scale=0.35]{figs/Home_screen.png}
    \caption{Home Page}
    \label{fig:Home_screen}
\end{figure}

The home screen (mode 2) does not have any interactive functionality other than to load another page by selecting one on the navigation bar.

\begin{figure}[H]
    \centering
    \includegraphics[scale=0.35]{figs/ActiveDevices_screen.png}
    \caption{Active Devices Page}
    \label{fig:active_devices}
\end{figure}

Figure~\ref{fig:active_devices} shows the active devices page (mode 3) which is loaded upon clicking "Active Devices" in the navigation bar. Here, all the connected devices are shown in order of when they connected to iBEMS. As mentioned previously, control of the WeMo Insight Switch is limited to turning it on and off while the embedded computer's motor speed can be controlled by submitting different duty cycles. Additionally, the embedded computer can be completely turned off by clicking the "Shutdown" button. Both supported devices also log their power usage at regular intervals. A plot of these power usage data points can be viewed by clicking "View Status Plots."

\begin{figure}[H]
    \centering
    \includegraphics[scale=0.35]{figs/ActiveDevices_plot.png}
    \caption{Active Devices Plot}
    \label{fig:active_devices_plot}
\end{figure}

After clicking "View Status Plots," a modal will pop up for the user to further interact with. By default, power usage data points for the current day are loaded at first, but another day can be selected by clicking on the calendar icon in the lower right corner. The plot is then updated by clicking "Update Plots." This is done by collecting data from the Apache Cassandra database and simply plotting all the points found for the specified day. Underneath the plot, the total energy consumed for the specified day is displayed. That total energy is found using the trapezoid method for integration on the plot.

\begin{figure}[H]
    \centering
    \includegraphics[scale=0.35]{figs/Applications_screen.png}
    \caption{Scheduling Page}
    \label{fig:schedulingl}
\end{figure}

Mode 4, or the scheduling page, can be loaded by clicking the "Device Scheduling" button in the navigation bar. Much like the active devices page, each connected device is listed in order of when they connected to iBEMS. Instead of directly controlling the devices, the user can enter in time periods when they want each device to maintain a specified status. For example, the WeMo Insight Switch can be scheduled to be on from 5 to 8 P.M. on Fridays. Likewise, the embedded computer can be scheduled to maintain a duty cycle of 0.5 for the same time period every Friday. Scheduled times can be added with the "Add new Period" and deleted by clicking the red "X" by the corresponding time period.

### 2021-04-30 parts/50-Conclusion.tex
Added final report files

\chapter{Conclusion}
\label{ch: Chapter5}

\section{Advantages}
iBEMS is open source, easy-to-use, and was developed using a modular, agent-based code base. Being open source makes it freely available to anyone who has the supported devices and wants to begin managing their home energy usage. The simple interface is easy to figure out for less tech-savvy users and the modular code base makes this system relatively easy for others to continue development.

\section{Disadvantages}
Despite its advantages, potential users should be aware of the rather obvious disadvantages at this point. A typical commercial building energy management system will include many more features like predicting future energy use and supporting more devices.

\section{Challenges}
The biggest challenges we foresee for future developers are adapting iBEMS to an enterprise network and adding the security necessary to do so. As mentioned before, iBEMS currently only works when all devices are connected through a single router. Scaling iBEMS up to an enterprise network with multiple access points will be an immensely complicated upgrade. Further more, security will be needed to make sure only select clients on an enterprise network will be able to login to iBEMS and have control over the connected devices. This will involve a much more robust login feature and possibly encrypting the messages being sent to and from the devices and iBEMS core.

\section{Future Work}
One of the main ways to improve the software is to refactor the user interface as the current interface is fairly primitive. Adding elements like collapsible drop down menus and a collapsible side bar would make the interface more professional and user-friendly. BEMOSS could be used as a reference in this process. Secondly, a better and more robust user login system could help decrease the risk of security breaches. Granular access control to different parts of the site could help ensure that only certain groups of individuals have access to certain features. An efficient way to implement this would be to use the add-on to Flask known as flask-login. To improve the overall reliability and speed of the software, a better agent communication protocol could be researched and implemented. Many problems are visible with the use of ZeroMQ as exceptions are thrown occasionally when device status updates are sent in quick succession to the control agent. Potentially, there exists a better solution than publish-subscribe. Intelligent algorithms device power usage over a long span of time. One of the major issues with the software is lack of device data persistence across system restarts. Developers in the future could help alleviate this problem by refactoring the device storage system in the Cassandra database.

### 2021-04-30 parts/A-Installation.tex
Added final report files

\chapter{Installation}
\label{ap: appendixA}

This appendix provides the steps for installing iBEMS on Ubuntu or any supported distribution of Linux.

\section{Cloning the repository}
The first step is to clone the repository with the command.
\begin{verbatim}
    git clone -b master https://github.com/ejwatkins
    /seniorProject1-2020-21-Code.git
\end{verbatim}
This will clone the master branch of the private Github repository owned by Elliot Watkins. It is recommended to run this command in the Unix user's home directory to find it easily.
\begin{figure}[H]
    \centering
    \includegraphics[scale=0.4]{figs/cloneiBEMS.png}
    \caption{Cloning iBEMS}
    \label{fig:cloneibems}
\end{figure}
If no errors occurred, terminal output similar to Figure~\ref{fig:cloneibems} will appear. A directory titled \texttt{seniorProject-2020-21-Code} will appear in the user's home directory.

\section{Creating the virtual environment}
Before the system can be properly installed, a Python 3 virtual environment must be created. After changing into the source code directory, this can be performed with the command
\begin{verbatim}
    python3 -m venv venv
\end{verbatim}
The final argument supplies the name of the directory the virtual environment will be placed in. For now, the name of the directory must be \texttt{venv} as this path name is hard coded in the source code. No terminal output should be generated when running this command if the proper version of Python 3 is installed along with the virtual environment package. If no errors occur, output similar to that of Figure~\ref{fig:createvenv} will be shown.

\begin{figure}[H]
    \centering
    \includegraphics[scale=0.4]{figs/createvenv.png}
    \caption{Creating the virtual environment}
    \label{fig:createvenv}
\end{figure}

\section{Running the installation script}
Once the venv is created, the platform will be able to be properly installed by running the command
\begin{verbatim}
    ./install.sh
\end{verbatim}
If this script does not have executable permission for the current user, the following command will change the permissions of the file to allow it to be run by any normal user:
\begin{verbatim}
    chmod u+x install.sh
\end{verbatim}
This script will run through and install any necessary Python packages via the \texttt{requirements.txt} file, install the Apache Cassandra database, and place necessary project directories on the PYTHONPATH. Output similar to that in Figure~\ref{fig:runinstall} will be produced.

\begin{figure}[H]
    \centering
    \includegraphics[scale=0.4]{figs/runinstall.png}
    \caption{Running the installation script}
    \label{fig:runinstall}
\end{figure}
An error regarding the installation of the \texttt{mpld3} package may be visible. However, this can be ignored as this package is not used in the current version of the software.
\medbreak\noindent
At this point, the software can be started with the \texttt{GUI.py} Python script.

### 2021-04-30 parts/B-HowToRun.tex
Added final report files

\chapter{How to Run}
\label{ap: appendixB}

This appendix describes the few steps that are required to get the software running on the user's Linux machine.

\section{Running the Python GUI}
In the top level directory of the project, there should be a file titled \texttt{GUI.py} which will act as the main entry point into the project. To run this file, it can be run either as an executable with
\begin{verbatim}
    ./GUI.py
\end{verbatim}
or as a Python script with
\begin{verbatim}
    python3 GUI.py
\end{verbatim}
The output GUI is shown in Figure~\ref{fig:desktopGUI}
\begin{figure}[H]
    \centering
    \includegraphics[scale=0.5]{figs/desktopGUI.png}
    \caption{Desktop GUI}
    \label{fig:desktopGUI}
\end{figure}

\section{Running the software}
By clicking on the "Start iBEMS" button shown in Figure~\ref{fig:desktopGUI}, the software will be launched in a new terminal shown in Figure~\ref{fig:runningterminal}.
\begin{figure}[H]
    \centering
    \includegraphics[scale=0.4]{figs/runningterminal.png}
    \caption{Running terminal}
    \label{fig:runningterminal}
\end{figure}

### 2021-05-01 parts/10-introduction.tex
Initial feedback by Dr. Miah

@@
 \section{Project Description}
-The Internet of Things is a large network of embedded devices like sensors, wearables, and appliances capable of receiving control commands and reporting data over the Internet.
-Many industries take advantage of this infrastructure to improve process flow and efficiency.
-One of these industries is the commercial and industrial sector which often employ building automation or management systems to help better manage processes or devices in a building like air conditioning systems, lights or industrial machines.
-Technological advancements have allowed devices to become connected to a building network through communication protocols like WiFi, Ethernet, Modbus, or BACnet which enables them to be more easily controlled from a central system.
-\medbreak\noindent
-Our overall goal is to create a platform in which users can login and access devices connected to a building's energy supply.
-This will allow the user to closely monitor energy usage throughout a commercial or residential building.
-Additionally, the user will be able to control devices connected to the platform, allowing precise control over the building's energy use.
-The minimum viable product of this project will be to connect to 1 to 3 devices via the the platform and control them.
+The Internet of Things is a large network of embedded devices
+\replace{like}{, such as} sensors,
+wearables, and appliances capable of receiving control commands and reporting
+data over the Internet. Many industries take advantage of this infrastructure to
+improve process flow and efficiency. One of these industries is the commercial
+and industrial sector which often employ building automation or management
+systems to help better manage processes or devices in a building like air
+conditioning systems, lights or industrial machines. Technological advancements
+have allowed devices to become connected to a building network through
+communication protocols like WiFi, Ethernet, Modbus, or BACnet which enables
+them to be more easily controlled from a central system.
+
+Our overall goal is to create a platform in which users can login and access devices
+connected to a building's energy supply. This will allow the user to closely
+monitor energy usage throughout a commercial or residential building.
+Additionally, the user will be able to control devices connected to the
+platform, allowing precise control over the building's energy use. The minimum
+viable product of this project will be to connect to 1 to 3 devices via the the
+platform and control them.
 
@@
 
-During a research project with Dr.
-Miah, the DC motor interface was successfully implemented into the BEMOSS platform which required adding a great deal of code to the platform to fully implement the device as BEMOSS does not support adding new devices currently.
-The research also consisted of adding a new logo to the platform for the motor.
-A possible improvement our platform will make is helping developers on the project to add new devices more easily.
+During a research project led by Miah \textit{et al.,} the DC motor interface was successfully
+implemented into the BEMOSS platform which required adding a great deal of
+\add{source} code
+to the platform to fully implement the device as BEMOSS does not support adding
+new devices currently. The research also consisted of adding a new
+\add{features, such as } logo to the
+platform for the motor. A possible improvement our platform will make is helping
+developers on the project to add new devices more easily.
 
-One of the improvements our project makes over the previous is the use of UDP multicasting which does not require any superuser privileges to locate an embedded computer (Beaglebone Blue).
-This implementation is also more convenient because it does not require installing any packages as multicasting is natively supported by most embedded Linux systems.
-If in the future, multiple embedded computers are needed to be discovered, the multicasting system works elegantly as each device can simply listen on a provided multicast group which consists of an IP address and port number.
+One of the improvements our project makes over the previous is the use of UDP
+\add{(user datagram protocol)} multicasting which does not require any superuser privileges to locate an
+embedded computer (Beaglebone Blue\add{, for example}). This implementation is also more convenient
+because it does not require installing any packages as multicasting is natively
+supported by most embedded Linux systems. If in the future, multiple embedded
+computers are needed to be discovered, the multicasting system works elegantly
+as each device can simply listen on a provided multicast group which consists of
+an IP address and port number.
 
@@
 
-One such platform is BEMOSS from the Virginia Polytechnic Institute and State University Advanced Research Institute.
-BEMOSS features include being open-source, allowing for multiple communication technologies, and supporting many common IoT devices.
-This system allows for monitoring and controlling a variety of devices securely.
+One such platform is the BEMOSS from the Virginia Polytechnic Institute and State
+University Advanced Research Institute. BEMOSS features include being
+open-source, allowing for multiple communication technologies, and supporting
+many common IoT devices. This system allows for monitoring and controlling a
+variety of devices securely\todo[inline]{Need citation here}.
 
-Another open-source platform is rEMpy or residential Energy Management in python.
-The main focus of this platform developed by a team of researchers at Universit\`{a} Politecnica delle Marche in Ancona, Italy was to simulate the energy flow of a residential home.
-With the data collected from simulations, it was possible for them to use forecasting and prediction algorithms to predict various quantities like energy usage and power consumption over a given time period.
+Another open-source platform is rEMpy or residential Energy Management in
+Python. The main focus of this platform developed by a team of researchers at
+Universit\`{a} Politecnica delle Marche in Ancona, Italy was to simulate the
+energy flow of a residential home. With the data collected from simulations, it
+was possible for them to use forecasting and prediction algorithms to predict
+various quantities \replace{like}{, such as} energy usage and power consumption over a given time period.
 Their energy management system consists of a well-defined structure with components like a user interface, database, and optimal scheduler that communicates with modules like a prediction and thermal model.
 In terms of software technologies, it uses the Django web framework which provides a lot of built-in functionality for web development like a user-authentication system and object-relational mapping.
-Adapting the project to this framework could be a great way to help improve security and optimize database queries \cite{fagiani2017}.
+Adapting the project to this framework could be a great way to help improve security and optimize database queries~\cite{fagiani2017}.
 
-One of the works in the literature discusses Model Predictive Control (MPC) which is a modern process control algorithm capable of taking into account current and previous time values to improve building automation~\cite{Mayer2017}.
-A multilevel hierarchy is presented to split control of a building into two levels: the energy supply level and user level.
-Example usage of this control scheme provided are temperature control of a building and its corresponding zones and interaction with a smart grid.
-Studies were performed on a commercial building with the building's energy supply system and hierarchy model predictive controller implemented in Matlab.
+One of the works in the literature discusses Model Predictive Control (MPC)
+which is a modern process control algorithm capable of taking into account
+current and previous time values to improve building
+automation~\cite{Mayer2017}. A multilevel hierarchy is presented to split
+control of a building into two levels: the energy supply level and user level.
+Example usage of this control scheme provided are temperature control of a
+building and its corresponding zones and interaction with a smart grid. Studies
+were performed on a commercial building with the building's energy supply system
+and hierarchy model predictive controller implemented in Matlab.
 
-In~\cite{8246800}, the authors describe similar functional requirements to our own BEMS Core.
-They periodically gather power consumption and device status data and send that data to a database.
-We are doing exactly what they describe using the Apache Cassandra database.
-The authors also use an "analytics [sic] engine to process [the data] and generate reports, graphs, and charts." Our system only generates a power consumption plot for a given day, but we are still meeting this same requirement - just on a smaller scale.
-The communication with devices and power consumption reports are to be accessible through a web-based application that is easy to use.
-Again, our implementation is simple and very intuitive for the end-user.
-Finally, these authors mention a user-login feature.
-They explain that their system would include multiple levels of accessibility based on the user privileges.
-Although our system does not currently have a user-login feature, it simply uses a router to access devices that are also connected to the router.
-Since this is a closed system, users need only protect their router with a secure password.
+In~\cite{8246800}, \remove{the }authors describe similar functional requirements to our
+own BEMS Core. They periodically gather power consumption and device status data
+and send that data to a database. We are doing exactly what they describe using
+the Apache Cassandra database. The authors also use an "analytics [sic] engine
+to process [the data] and generate reports, graphs, and charts." Our system only
+generates a power consumption plot for a given day, but we are still meeting
+this same requirement - just on a smaller scale. The communication with devices
+and power consumption reports are to be accessible through a web-based
+application that is easy to use. Again, our implementation is simple and very
+intuitive for the end-user. Finally, these authors mention a user-login feature.
+They explain that their system would include multiple levels of accessibility
+based on the user privileges. Although our system does not currently have a
+user-login feature, it simply uses a router to access devices that are also
+connected to the router. Since this is a closed system, users need only protect
+their router with a secure password.
 
-A control scheme in~\cite{Barchi2018} is presented to manage a photovoltaic array and battery energy storage system.
-Tests were conducted in a shopping mall with an electronic load to emulate the power consumption of the building.
-Potentially, a similar technique could be used to model the energy demand of a house in Simulink or Simscape model.
-Through their scheme, an intelligent BEMS is used to collect measurable data like power, voltage, and current and stored for offline analysis later.
+A control scheme in~\cite{Barchi2018} is presented to manage a photovoltaic
+array and battery energy storage system. Tests were conducted in a shopping mall
+with an electronic load to emulate the power consumption of the building.
+Potentially, a similar technique could be used to model the energy demand of a
+house in Simulink or Simscape model. Through their scheme, an intelligent BEMS
+is used to collect measurable data \replace{like}{, such as} power, voltage, and current and stored for offline analysis later.
 Their platform collects data every five minutes compared to the 20 second polling rate currently configured in our platform.
@@
 %----------------------------------------------------------------------
-This report is organised into 5 chapters.
-Chapter \ref{ch: Chapter1} discusses what this project hopes to accomplish and what similar projects have completed.
-Chapter \ref{ch: Chapter2} explains the architecture.
-Chapter \ref{ch: Chapter3} provides a brief explanation of the control algorithms and architectures used.
-Chapter \ref{ch: Chapter4} contains the results from our simulations.
-Chapter \ref{ch: Chapter5} concludes the paper and provides insight into future directions.
+This report is organised into 5 chapters.  Chapter \ref{ch: Chapter1} discusses
+what this project hopes to accomplish and what similar projects have completed.
+Chapter \ref{ch: Chapter2} explains the architecture. Chapter \ref{ch: Chapter3}
+provides a brief explanation of the control algorithms and architectures used.
+Chapter \ref{ch: Chapter4} contains the results from \replace{our simulations}{a
+few experiments}. Chapter \ref{ch: Chapter5} concludes the \replace{paper}{report} and provides insight into future directions.
 
@@
 %%% mode: latex
-%%% TeX-master: "../finalReportMainV1"
+%%% TeX-master: "../finalReport"
 %%% End:

### 2021-05-01 parts/20-iBEMSArchitecture.tex
Initial feedback by Dr. Miah

@@
 
-\begin{figure}[H]
+At the center of the iBEMS architecture is the iBEMS core. This core interacts
+with multiple peripherals including IoT devices and a weather API over the
+internet. Over the course of this project, we managed to develop support for 2
+IoT devices displayed in Figure~\ref{fig:highLevelArchitecture}. %
+%
+\begin{figure}
   \centering
-    \includegraphics[scale=0.8]{figs/highLevelArchitecture.pdf}
+  \includegraphics[scale=0.3]{figs/highLevelArchitecture.pdf}
   \caption{High Level Architecture of the Proposed System}
@@
 \end{figure}
-
-At the center of the iBEMS architecture is the iBEMS core.
-This core interacts with multiple peripherals including IoT devices and a weather API over the internet.
-Over the course of this project, we managed to develop support for 2 IoT devices displayed in Figure~\ref{fig:highLevelArchitecture}.
-These devices are the WeMo Insight Switch and an embedded computer known as the Beaglebone Blue.
-Our initial plan for the smart meter shown in Figure~\ref{fig:highLevelArchitecture} was to use it in a Simscape model of a microgrid.
-However, we did not list this as a requirement for the project, so we decided not to implement it due to time constraints.
-The core is also able to connect the internet to download weather data for Peoria, Illinois through OpenWeatherMap.
+%
+These devices are the WeMo Insight Switch and an embedded computer known as the Beaglebone
+Blue. Our initial plan for the smart meter shown in
+Figure~\ref{fig:highLevelArchitecture} was to use it in a Simscape model of a
+microgrid. However, we did not list this as a requirement for the project, so we
+decided not to implement it due to time constraints. The core is also able to
+connect the internet to download weather data for Peoria, Illinois through
+OpenWeatherMap.
 
 \section{Low Level Architecture}
-\begin{figure}[H]
+
+Figure~\ref{fig:functional_bd} gives lower level detail on the system
+architecture. %
+%
+\begin{figure}
   \centering
-    \includegraphics[scale=0.8]{figs/functionalBlockDiagram.pdf}
+  \includegraphics[scale=0.3]{figs/functionalBlockDiagram.pdf}
   \caption{Functional Block Diagram}
@@
 \end{figure}
+%
+The inputs include the user input through the web server, the device status
+updates (On/Off, power usage, etc...) and the weather data. The iBEMS Core
+itself consists of a Flask Web Server, 2 databases (Apache Cassandra and
+SQLite), and 3 software agents (Discovery, Control, and Scheduling).
 
-Figure~\ref{fig:functional_bd} gives lower level detail on the system architecture.
-The inputs include the user input through the web server, the device status updates (On/Off, power usage, etc...) and the weather data.
-The iBEMS Core itself consists of a Flask Web Server, 2 databases (Apache Cassandra and SQLite), and 3 software agents (Discovery, Control, and Scheduling).
-\medbreak
-The Flask web server is built using a Python web framework titled Flask which allows programmers to develop a dynamic web server capable of rendering data to HTML pages.
-The benefit of this framework over other Python web frameworks like Django is the large amount of customization available.
-For example, the developers can create a completely custom user login system.
-For now, the server is capable of being accessed only on the server computer running Ubuntu Linux.
-In the future, support could be added to allow any user on the LAN to access the web server.
-Other web frameworks use object relational mapping directly to access the relevant databases.
-However, our system uses direct queries with both SQLite and the Cassandra query language to query the database.
-\medbreak
-We used 2 different databases to store information on.
-The Apache Cassandra database was better suited for the time series data such as device status and power usage.
+The Flask web server is built using a Python web framework titled Flask which
+allows programmers to develop a dynamic web server capable of rendering data to
+HTML pages. The benefit of this framework over other Python web frameworks like
+Django is the large amount of customization available. For example, the
+developers can create a completely custom user login system. For now, the server
+is capable of being accessed only on the server computer running Ubuntu Linux.
+In the future, support could be added to allow any user on the LAN to access the
+web server. Other web frameworks use object relational mapping directly to
+access the relevant databases. However, our system uses direct queries with both
+SQLite and the Cassandra query language to query the database. \medbreak We used
+2 different databases to store information on. The Apache Cassandra database was
+better suited for the time series data such as device status and power usage.
 This database was therefore utilized a lot by the Control and Scheduling Agents.
-The SQLite database hold parameters that do not change over time like device ID's, IP addresses, and MAC addresses which made it amendable to the processes in the Discovery Agent.
-A possible improvement to this project could be to only utilize 1 database for development simplicity.
-\medbreak
-The first agent that is used by the iBEMS Core on startup is the discovery agent.
-It is responsible for reaching out on the network and finding all devices that the iBEMS Core has support for.
-This process involves retrieving the following parameters: IP address, Port number, MAC address, Manufacturer, Name, and API.
-Once all available devices are connected, the Control agent is used to change the status of each device and collect power usage data in real time.
-Finally, the scheduling will take input from the user and place the corresponding scheduling periods in the Apache Cassandra database.
-Then, a thread is created to poll the current device status at regular intervals and updates the status if it does not match the defined status in the Apache Cassandra database.
+The SQLite database hold parameters that do not change over time like device
+ID's, IP addresses, and MAC addresses which made it amendable to the processes
+in the Discovery Agent. A possible improvement to this project could be to only
+utilize 1 database for development simplicity. \medbreak The first agent that is
+used by the iBEMS Core on startup is the discovery agent. It is responsible for
+reaching out on the network and finding all devices that the iBEMS Core has
+support for. This process involves retrieving the following parameters: IP
+address, Port number, MAC address, Manufacturer, Name, and API. Once all
+available devices are connected, the Control agent is used to change the status
+of each device and collect power usage data in real time. Finally, the
+scheduling will take input from the user and place the corresponding scheduling
+periods in the Apache Cassandra database. Then, a thread is created to poll the
+current device status at regular intervals and updates the status if it does not
+match the defined status in the Apache Cassandra database.
 
-\begin{figure}[H]
+Figure~\ref{fig:systemComponentInterconnection} provides an explanation of how
+the components of the system interact with each other. %
+%
+\begin{figure}
   \centering
@@
 \end{figure}
-
-Figure~\ref{fig:systemComponentInterconnection} provides an explanation of how the components of the system interact with each other.
+%
 The Apache Cassandra database and SQLite database are accessible from the web server, control agent, discovery agent, and scheduling agent.
@@
 
-\begin{figure}[H]
+\begin{figure}
   \centering
-    \includegraphics[scale=0.9]{figs/operationalModes.pdf}
+  \includegraphics[scale=0.4]{figs/operationalModes.pdf}
   \caption{Operation Modes Interaction}
-    \label{fig:functional_bd}
+  \label{fig:operationalModes}
 \end{figure}
 
-There are 5 general modes of operation in iBEMS.
+There are 5 general modes of operation in iBEMS as shown in Figure~\ref{fig:operationalModes}.
 In Mode 0, before iBEMS is even launched, the user must open the Startup Menu, which is a desktop graphical user interface (GUI).
@@
 
+A large feature of this project was being able to record power usage from the
+connected IoT devices. The embedded computer does not have a built-in capability
+to measure its own power usage, so this circuit was needed to make that
+possible. Essentially, this circuit will measure the current being used to drive
+one of the motors on the robot chassis. The on-board Analog-to-Digital-Converter
+(ADC) can be used to read the voltage across the resistor and since the
+resistance is known, the current can be calculated as $I = V/R$. Also, the
+voltage from the H-Bridge to drive the motors on the embedded computer is known
+so the power consumed by 1 motor is $Motor Drive Voltage * I$. For the specific
+robot chassis used in this project, there are 4 motors, so multiplying the power
+found from this circuit by 4 will give an approximation of the total power used
+by the robot. For other robots with different power sources besides a Lipo
+battery. See Figure~\ref{fig:motorInterfaceCircuit} for details of the interface
+circuit for computer power usage by the DC motor.
+
+\begin{figure}
+  \centering
   \begin{circuitikz}[american]
@@
   \end{circuitikz}
-
-A large feature of this project was being able to record power usage from the connected IoT devices.
-The embedded computer does not have a built-in capability to measure its own power usage, so this circuit was needed to make that possible.
-Essentially, this circuit will measure the current being used to drive one of the motors on the robot chassis.
-The on-board Analog-to-Digital-Converter (ADC) can be used to read the voltage across the resistor and since the resistance is known, the current can be calculated as $I = V/R$.
-Also, the voltage from the H-Bridge to drive the motors on the embedded computer is known so the power consumed by 1 motor is $Motor Drive Voltage * I$.
-For the specific robot chassis used in this project, there are 4 motors, so multiplying the power found from this circuit by 4 will give an approximation of the total power used by the robot.
-For other robots with different power sources besides a Lipo battery,
+  \caption{Interface circuit to calculate power consumption of a DC motor
+    running from the embedded computer copmuter.}
+  \label{fig:motorInterfaceCircuit}
+\end{figure}
 
@@
 
-In order to test these devices, we plugged a bank of 6 light bulbs into the WeMo Insight Switch as seen in Figure~\ref{fig:overallView}.
-The embedded computer's functionality was tested with the circuit and robot chassis described earlier.
+In order to test these devices, we plugged a bank of 6 light bulbs into the WeMo
+Insight Switch as seen in Figure~\ref{fig:overallView}. The embedded computer's
+functionality was tested with the circuit and robot chassis described earlier.
+
+%%% Local Variables:
+%%% mode: latex
+%%% TeX-master: "../finalReport"
+%%% End:

### 2021-05-01 parts/30-Implementation.tex
Initial feedback by Dr. Miah

@@
 % Talk about Zero MQ
-All three agents communicate with each other and the web server using the Zero MQ asynchronous messaging library [citation here].
-Essentially, this library works as a way to implement inter process communication without a message broker.
-In other words, different processes are able to communicate with each other without any central bus.
-This is convenient as fewer processes are needed for the system to function.
-Lowering the number of overall processes lowers the RAM and CPU usage of the software.
-The library is ported to many different programming languages; however we are using the Python port titled Pyzmq to implement in our code base.
-\begin{figure}[H]
+All three agents communicate with each other and the web server using the Zero
+MQ asynchronous messaging library\todo{citation here}. Essentially, this library
+works as a way to implement inter process communication without a message
+broker. In other words, different processes are able to communicate with each
+other without any central bus. This is convenient as fewer processes are needed
+for the system to function. Lowering the number of overall processes lowers the
+RAM and CPU usage of the software. The library is ported to many different
+programming languages; however we are using the Python port titled Pyzmq to
+implement in our code base.
+%
+\begin{figure}
     \centering
-    \includegraphics{figs/pubSubAgents.pdf}
+    \includegraphics[width=0.4\textwidth]{figs/pubSubAgents.pdf}
     \caption{Publish Subscribe Communication using ZeroMQ}
@@
 \end{figure}
-More specifically, the publish subscribe model of communication is used where each agent communicates via a socket where each socket responds to a specific topic.
-The topics and port numbers are listed below along with their corresponding agents in Table~\ref{tab:pubsubspecs}.
-\begin{table}[H]
+%
+\todo[inline]{Figures are cited in the text}
+
+More specifically, the publish subscribe model of communication is used where
+each agent communicates via a socket where each socket responds to a specific
+topic. The topics and port numbers are listed below along with their
+corresponding agents in Table~\ref{tab:pubsubspecs}. %
+%
+\begin{table}
     \centering
@@
 \end{table}
-In order to send data between the different processes, the topic, method, and data are delimited in a particular way. This method is shown below as follows
+%
+In order to send data between the different processes, the topic, method, and
+data are delimited in a particular way. This method is shown below as follows: %
+%
 \begin{verbatim}
@@
 \end{verbatim}
-A space cannot be included between the method name and arguments as this interferes with the Python \texttt{split} method for extracting the fields.
-The \texttt{topic} is the string described previously, the \texttt{method} is the name of the desired method to be called on the agent object, and \texttt{args} is the arguments supplied to the desired method.
-In order to send a message to an agent, the \texttt{publish} method defined in the \texttt{pubsub} module should be called.
-An optional argument titled \texttt{cycleCount} is available which will allow the publish message to be sent multiple times.
-During testing, it was found that during the transmission of some messages, this was necessary due to the way ZeroMQ is implemented.
+%
+A space cannot be included between the method name and arguments as this
+interferes with the Python \texttt{split} method for extracting the fields. The
+\texttt{topic} is the string described previously, the \texttt{method} is the
+name of the desired method to be called on the agent object, and \texttt{args}
+is the arguments supplied to the desired method. In order to send a message to
+an agent, the \texttt{publish} method defined in the \texttt{pubsub} module
+should be called. An optional argument titled \texttt{cycleCount} is available
+which will allow the publish message to be sent multiple times. During testing,
+it was found that during the transmission of some messages, this was necessary
+due to the way ZeroMQ is implemented.
 
 \section{Agent Functionality}
-The agents contained in the software are associated with a Python class of the same name.
-Each class is instantiated and run with specifications declared in Table~\ref{tab:pubsubspecs}.
-Some of the methods defined in each class will be described in the following subsections.
+The agents contained in the software are associated with a Python class of the
+same name. Each class is instantiated and run with specifications declared in
+Table~\ref{tab:pubsubspecs}. Some of the methods defined in each class will be
+described in the following subsections.
 
 \subsection{Control Agent Functionality}
-The flow chart of method \texttt{setDeviceStatus} is shown in Figure~\ref{fig:setDeviceStatus}.
-The purpose of this method is to set the status of the desired device.
-When the method is called, the data dictionary is obtained which contains the device ID.
-With this device ID, the API type can be determined using the SQLite database.
-Subsequently, the appropriate device API module can be imported.
-If the power state exists as a key in the device data dictionary, the power state of the WeMo Insight Switch will be set as ON or OFF.
-If the duty cycle key exists, the duty cycle of the single board computer motor drivers is set.
-If the shutdown key is set, the single board computer is shutdown.
-In order to reconnect to the single board computer, the board must be started and receiver program ran.
-If necessary, the device must be reconnected to the WiFi network.
-\begin{figure}[H]
+The flow chart of method \texttt{setDeviceStatus} is shown in
+Figure~\ref{fig:setDeviceStatus}. The purpose of this method is to set the
+status of the desired device. When the method is called, the data dictionary is
+obtained which contains the device ID. With this device ID, the API type can be
+determined using the SQLite database. Subsequently, the appropriate device API
+module can be imported. If the power state exists as a key in the device data
+dictionary, the power state of the WeMo Insight Switch will be set as ON or OFF.
+If the duty cycle key exists, the duty cycle of the single board computer motor
+drivers is set. If the shutdown key is set, the single board computer is
+shutdown. In order to reconnect to the single board computer, the board must be
+started and receiver program ran. If necessary, the device must be reconnected
+to the WiFi network. %
+%
+\begin{figure}
     \centering
@@
 \end{figure}
-To obtain necessary data quantities from the device, the \texttt{getDeviceStatus} method is defined.
-Once the proper data parameters are obtained, the \texttt{getState} function defined in the devices API module can be called with the data parameters like power state and status.
-Once the agent has finished sending these to the device, a request is sent to the web server to inform the server that it completed searching for the required device data.
+%
+\todo[inline]{Figures are not cited in the text}
 
-\begin{figure}[H]
+To obtain necessary data quantities from the device, the
+\texttt{getDeviceStatus} method is defined. Once the proper data parameters are
+obtained, the \texttt{getState} function defined in the devices API module can
+be called with the data parameters \replace{like}{, such as} power state and
+status. Once the agent has finished sending these to the device, a request is
+sent to the web server to inform the server that it completed searching for the
+required device data. %
+
+%
+\begin{figure}
     \centering
@@
 Since iBEMS only sends messages with the string data type, this has to be converted to a float in order to call the motor driver function.
+
+%%% Local Variables:
+%%% mode: latex
+%%% TeX-master: "../finalReport"
+%%% End:

### 2021-05-04 parts/10-introduction.tex
Updated report

@@
 \section{Project Description}
-The Internet of Things is a large network of embedded devices
-\replace{like}{, such as} sensors,
-wearables, and appliances capable of receiving control commands and reporting
+The Internet of Things is a large network of embedded devices such as sensors, wearables, and appliances capable of receiving control commands and reporting
 data over the Internet. Many industries take advantage of this infrastructure to
@@
 During a research project led by Miah \textit{et al.,} the DC motor interface was successfully
-implemented into the BEMOSS platform which required adding a great deal of
-\add{source} code
+implemented into the BEMOSS platform which required adding a great deal of source code
 to the platform to fully implement the device as BEMOSS does not support adding
 new devices currently. The research also consisted of adding a new
-\add{features, such as } logo to the
+features such a logo to the
 platform for the motor. A possible improvement our platform will make is helping
@@
 
-One of the improvements our project makes over the previous is the use of UDP
-\add{(user datagram protocol)} multicasting which does not require any superuser privileges to locate an
-embedded computer (Beaglebone Blue\add{, for example}). This implementation is also more convenient
+One of the improvements our project makes over the previous is the use of UDP (user datagram protocol) multicasting which does not require any superuser privileges to locate an
+embedded computer (Beaglebone Blue, for example). This implementation is also more convenient
 because it does not require installing any packages as multicasting is natively
@@
 many common IoT devices. This system allows for monitoring and controlling a
-variety of devices securely\todo[inline]{Need citation here}.
+variety of devices securely~\cite{BEMOSS}.
 
@@
 was possible for them to use forecasting and prediction algorithms to predict
-various quantities \replace{like}{, such as} energy usage and power consumption over a given time period.
+various quantities such as energy usage and power consumption over a given time period.
 Their energy management system consists of a well-defined structure with components like a user interface, database, and optimal scheduler that communicates with modules like a prediction and thermal model.
@@
 
-In~\cite{8246800}, \remove{the }authors describe similar functional requirements to our
+In~\cite{8246800}, authors describe similar functional requirements to our
 own BEMS Core. They periodically gather power consumption and device status data
 and send that data to a database. We are doing exactly what they describe using
-the Apache Cassandra database. The authors also use an "analytics [sic] engine
-to process [the data] and generate reports, graphs, and charts." Our system only
+the Apache Cassandra database. The authors also use an \say{analytics [sic] engine
+to process [the data] and generate reports, graphs, and charts.} Our system only
 generates a power consumption plot for a given day, but we are still meeting
@@
 house in Simulink or Simscape model. Through their scheme, an intelligent BEMS
-is used to collect measurable data \replace{like}{, such as} power, voltage, and current and stored for offline analysis later.
+is used to collect measurable data such as power, voltage, and current and stored for offline analysis later.
 Their platform collects data every five minutes compared to the 20 second polling rate currently configured in our platform.
@@
 provides a brief explanation of the control algorithms and architectures used.
-Chapter \ref{ch: Chapter4} contains the results from \replace{our simulations}{a
-few experiments}. Chapter \ref{ch: Chapter5} concludes the \replace{paper}{report} and provides insight into future directions.
+Chapter \ref{ch: Chapter4} contains the results from a few experiments. Chapter \ref{ch: Chapter5} concludes the report and provides insight into future directions.
 

### 2021-05-04 parts/20-iBEMSArchitecture.tex
Updated report

@@
 This is a simple GUI with only 2 buttons for starting and stopping iBEMS.
-Upon clicking "Start iBEMS," the login page will load where the user can enter a valid username and password to use iBEMS.
+Upon clicking \say{Start iBEMS}, the login page will load where the user can enter a valid username and password to use iBEMS.
 Once a valid username and password is entered, the home screen will be shown which displays the weather data being downloaded from the OpenWeatherMap API.
 This information include temperature in Fahrenheit and Celsius, wind speed in MPH, humidity, and cloud coverage.
-At this point, a navigation bar is available to view "Active Devices" page and the "Scheduling" page.
-"Active Devices" corresponds to Mode 3 for controlling devices in real time.
+At this point, a navigation bar is available to view \say{Active Devices} page and the \say{Scheduling} page.
+\say{Active Devices} corresponds to Mode 3 for controlling devices in real time.
 The user will also be able to view power plots in this mode as well.
-Lastly, the "Scheduling" page is Mode 4 for creating schedules for all connected devices.
+Lastly, the \say{Scheduling} page is Mode 4 for creating schedules for all connected devices.
 

### 2021-05-04 parts/30-Implementation.tex
Updated report

@@
 All three agents communicate with each other and the web server using the Zero
-MQ asynchronous messaging library\todo{citation here}. Essentially, this library
+MQ asynchronous messaging library. Essentially, this library
 works as a way to implement inter process communication without a message
-broker. In other words, different processes are able to communicate with each
+broker~\cite{zeromq}. In other words, different processes are able to communicate with each
 other without any central bus. This is convenient as fewer processes are needed
@@
 \end{figure}
-%
-\todo[inline]{Figures are cited in the text}
 
@@
 \end{figure}
-%
-\todo[inline]{Figures are not cited in the text}
 
 To obtain necessary data quantities from the device, the
-\texttt{getDeviceStatus} method is defined. Once the proper data parameters are
+\texttt{getDeviceStatus} method, defined in Figure~\ref{fig:getDeviceStatus}, is called. Once the proper data parameters are
 obtained, the \texttt{getState} function defined in the devices API module can
-be called with the data parameters \replace{like}{, such as} power state and
+be called with the data parameters such as power state and
 status. Once the agent has finished sending these to the device, a request is
@@
 The scheduling agent is able to update the device status of each device dependent on whether a schedule is set for the specific time period and day.
-One of the methods that is called, \texttt{updateScheduleFromServer} is invoked when the user presses the "Update Schedule" button from the UI on the scheduling page.
+One of the methods that is called, \texttt{updateScheduleFromServer} is invoked when the user presses the \say{Update Schedule} button from the UI on the scheduling page.
 A flow chart of this method is shown in Figure~\ref{fig:updateScheduleFromServer}.
@@
 \end{figure}
-A second method that is run inside each device thread is \texttt{periodicDeviceUpdateMethod} which is started when the discovery agent sets the discovered device to active.
+A second method that is run inside each device thread is \texttt{periodicDeviceUpdateMethod}, defined in Figure~\ref{fig:periodicDeviceUpdateMethod}, is started when the discovery agent sets the discovered device to active.
 By first loading the device's API name, the scheduling agent can begin checking for scheduling periods inside an infinite loop.
@@
 When the GUI is started up, the title, buttons, and labels are created along with ties to the callback functions \texttt{startCallback} and \texttt{stopCallback}.
-The \texttt{startCallback} function is called when the user presses the "Start iBEMS" button.
+The \texttt{startCallback} function is called when the user presses the \say{Start iBEMS} button.
 This function first checks whether iBEMS is already running by checking for processes already running on the machine including the web server itself and the three agents.
@@
 This prevents errors associated with copies of agents and web servers running simultaneously.
-To properly stop the software, the "Stop iBEMS" button will shutdown the software by first finding the process ID's associated with the agents and web server.
-To perform this, it will place the output of \texttt{ps -aux | grep [process]} into a text file where "process" is the name of the target process.
+To properly stop the software, the \say{Stop iBEMS} button will shutdown the software by first finding the process ID's associated with the agents and web server.
+To perform this, it will place the output of \texttt{ps -aux | grep [process]} into a text file where \say{process} is the name of the target process.
 A file descriptor of the process status output text file is instantiated and all the lines are read in to be parsed.
@@
 There are 4 different messages that the iBEMS core sends to the embedded computer.
-First, it will check if the iBEMS core is telling it to shut down with the command "Shutdown." If so, the embedded computer will immediately shut down.
-Second, if the data sent by iBEMS is "status," the embedded computer will take a reading from the circuit described in Chapter~\ref{ch: Chapter2} section 3.
-In case the user decides to shut down the iBEMS core without turning off the embedded computer, another message "disconnect" will be sent in which case the embedded computer will exit \texttt{communicate\_with\_iBEMS} and start the entire program over again.
+First, it will check if the iBEMS core is telling it to shut down with the command \say{Shutdown}.
+If so, the embedded computer will immediately shut down.
+Second, if the data sent by iBEMS is \say{status}, the embedded computer will take a reading from the circuit described in Chapter~\ref{ch: Chapter2} section 3.
+In case the user decides to shut down the iBEMS core without turning off the embedded computer, another message \say{disconnect} will be sent in which case the embedded computer will exit \texttt{communicate\_with\_iBEMS} and start the entire program over again.
 Finally, if iBEMS is not sending any of the above options, it means that the user is sending a new duty cycle to drive the motors with.

### 2021-05-04 parts/40-ExperimentalResults.tex
Initial feedback by Dr. Miah
Updated report

@@
 \noindent
-Here, the user will simply click the "Start iBEMS" button to launch the web server and agents.
-When the user is finished, all agents and the web server can be shut down by clicking "Stop iBEMS." In case the user accidentally clicks the "Start iBEMS" button while iBEMS is already running, then the following error message will appear:
+Here, the user will simply click the \say{Start iBEMS} button to launch the web
+server and agents. When the user is finished, all agents and the web server can
+be shut down by clicking \say{Stop iBEMS}. In case the user accidentally clicks the
+\say{Start iBEMS} button while iBEMS is already running, then the following error
+message will appear:
 
@@
 
-Figure~\ref{fig:active_devices} shows the active devices page (mode 3) which is loaded upon clicking "Active Devices" in the navigation bar.
+Figure~\ref{fig:active_devices} shows the active devices page (mode 3) which is loaded upon clicking \say{Active Devices} in the navigation bar.
 Here, all the connected devices are shown in order of when they connected to iBEMS.
 As mentioned previously, control of the WeMo Insight Switch is limited to turning it on and off while the embedded computer's motor speed can be controlled by submitting different duty cycles.
-Additionally, the embedded computer can be completely turned off by clicking the "Shutdown" button.
+Additionally, the embedded computer can be completely turned off by clicking the \say{Shutdown} button.
 Both supported devices also log their power usage at regular intervals.
-A plot of these power usage data points can be viewed by clicking "View Status Plots."
+A plot of these power usage data points can be viewed by clicking \say{View Status Plots}.
 
@@
 
-After clicking "View Status Plots," a modal will pop up for the user to further interact with.
-By default, power usage data points for the current day are loaded at first, but another day can be selected by clicking on the calendar icon in the lower right corner.
-The plot is then updated by clicking "Update Plots." This is done by collecting data from the Apache Cassandra database and simply plotting all the points found for the specified day.
-Underneath the plot, the total energy consumed for the specified day is displayed.
-That total energy is found using the trapezoid method for integration on the plot.
-
-\begin{figure}[H]
+After clicking \say{View Status Plots}, a modal will pop up for the user to further
+interact with. By default, power usage data points for the current day are
+loaded at first, but another day can be selected by clicking on the calendar
+icon in the lower right corner. The plot is then updated by clicking \say{Update
+Plots}. This is done by collecting data from the Apache Cassandra database and
+simply plotting all the points found for the specified day. Underneath the plot,
+the total energy consumed for the specified day is displayed. That total energy
+is found using the trapezoid method for integration on the plot. %
+%
+\begin{figure}
     \centering
@@
 \end{figure}
+%
 
-Mode 4, or the scheduling page, can be loaded by clicking the "Device Scheduling" button in the navigation bar.
-Much like the active devices page, each connected device is listed in order of when they connected to iBEMS.
-Instead of directly controlling the devices, the user can enter in time periods when they want each device to maintain a specified status.
-For example, the WeMo Insight Switch can be scheduled to be on from 5 to 8 P.M.
-on Fridays.
-Likewise, the embedded computer can be scheduled to maintain a duty cycle of 0.5 for the same time period every Friday.
-Scheduled times can be added with the "Add new Period" and deleted by clicking the red "X" by the corresponding time period.
+Mode 4, or the scheduling page, can be loaded by clicking the \say{Device
+Scheduling} button in the navigation bar. Much like the active devices page,
+each connected device is listed in order of when they connected to iBEMS.
+Instead of directly controlling the devices, the user can enter in time periods
+when they want each device to maintain a specified status. For example, the WeMo
+Insight Switch can be scheduled to be on from 5 to 8 P.M. on Fridays. Likewise,
+the embedded computer can be scheduled to maintaian a duty cycle of 0.5 for the
+same time period every Friday. Scheduled times can be added with the \say{Add new
+Period} and deleted by clicking the red \say{X} by the corresponding time period.
+
+%%% Local Variables:
+%%% mode: latex
+%%% TeX-master: "../finalReport"
+%%% End:

### 2021-05-07 parts/10-introduction.tex
Updated report

@@
 to the platform to fully implement the device as BEMOSS does not support adding
-new devices currently. The research also consisted of adding a new
-features such a logo to the
+new devices currently. The research also consisted of adding new
+features such as a logo to the
 platform for the motor. A possible improvement our platform will make is helping
-developers on the project to add new devices more easily.
+developers on the project add new devices more easily.
 
@@
 
-One such platform is the BEMOSS from the Virginia Polytechnic Institute and State
+One such platform is BEMOSS from the Virginia Polytechnic Institute and State
 University Advanced Research Institute. BEMOSS features include being
@@
 various quantities such as energy usage and power consumption over a given time period.
-Their energy management system consists of a well-defined structure with components like a user interface, database, and optimal scheduler that communicates with modules like a prediction and thermal model.
+Their energy management system consists of a well-defined structure with components like a user interface, database, and optimal scheduler that communicate with modules like a prediction and thermal model.
 In terms of software technologies, it uses the Django web framework which provides a lot of built-in functionality for web development like a user-authentication system and object-relational mapping.
@@
 They explain that their system would include multiple levels of accessibility
-based on the user privileges. Although our system does not currently have a
-user-login feature, it simply uses a router to access devices that are also
-connected to the router. Since this is a closed system, users need only protect
-their router with a secure password.
+based on the user privileges.
 

### 2021-05-07 parts/20-iBEMSArchitecture.tex
Updated report

@@
 access the relevant databases. However, our system uses direct queries with both
-SQLite and the Cassandra query language to query the database. \medbreak We used
+SQLite and the Cassandra query language to query the databases. \medbreak We used
 2 different databases to store information on. The Apache Cassandra database was
@@
 periods in the Apache Cassandra database. Then, a thread is created to poll the
-current device status at regular intervals and updates the status if it does not
+current device status at regular intervals and update the status if it does not
 match the defined status in the Apache Cassandra database.
@@
 Once a valid username and password is entered, the home screen will be shown which displays the weather data being downloaded from the OpenWeatherMap API.
-This information include temperature in Fahrenheit and Celsius, wind speed in MPH, humidity, and cloud coverage.
-At this point, a navigation bar is available to view \say{Active Devices} page and the \say{Scheduling} page.
+This information includes temperature in Fahrenheit and Celsius, wind speed in MPH, humidity, and cloud coverage.
+At this point, a navigation bar is available to view the \say{Active Devices} page and the \say{Scheduling} page.
 \say{Active Devices} corresponds to Mode 3 for controlling devices in real time.
@@
 connected IoT devices. The embedded computer does not have a built-in capability
-to measure its own power usage, so this circuit was needed to make that
+to measure its own power usage, so a circuit was needed to make that
 possible. Essentially, this circuit will measure the current being used to drive
@@
 found from this circuit by 4 will give an approximation of the total power used
-by the robot. For other robots with different power sources besides a Lipo
-battery. See Figure~\ref{fig:motorInterfaceCircuit} for details of the interface
+by the robot. \add{For other robots with different power sources besides a Lipo
+battery.} See Figure~\ref{fig:motorInterfaceCircuit} for details of the interface
 circuit for computer power usage by the DC motor.
@@
 It simply plugs into a 120 volt 3-prong outlet and any typical household appliance running on 120 volts can be plugged into it.
-Internal circuitry allows the WeMo to be controlled remotely (turn On/Off) and to record power usage of whatever is plugged into.
+Internal circuitry allows the WeMo to be controlled remotely (turn On/Off) and to record power usage of whatever it is plugged into.
 

### 2021-05-07 parts/30-Implementation.tex
Updated report

@@
 The algorithm could be improved to help page load times.
-All the device APIs are loaded in the \texttt{findDevices} function defined in each device's API module is called which will return a list of found URLs.
+All the device APIs are loaded by the \texttt{findDevices} function which will return a list of found URLs.
 Once the device's URL is determined, it's metadata can be passed to the \texttt{setDeviceToActive} method which will set up the device in the two databases.
@@
 \end{figure}
-The \texttt{setDeviceToActive} shown in Figure~\ref{fig:setDeviceToActive} will first check to make sure the device is not already in the active devices table.
+The \texttt{setDeviceToActive} method shown in Figure~\ref{fig:setDeviceToActive} will first check to make sure the device is not already in the active devices table.
 Then, it will add the device to the active devices table, create a table in the Cassandra database for storing time-series data, send a message to the scheduling agent to check for schedule updates, and send a message to the control agent to start collecting data.
@@
 First the times are stored in military time in the database for more convenient storage and parsing later on.
-Then, a table is created in the Apache Cassandra database for the device for the provided data and the device ID is embedded.
-The table's data is destroyed to ensure there are no errors regarding overlapping schedules.
+Then, a table is created in the Apache Cassandra database where the device ID and day are embedded in the name.
+The previous table's data is destroyed to ensure there are no errors regarding overlapping schedules.
 Lastly, all the scheduling periods extracted from the dictionary are stored as rows in the table.
@@
 \end{figure}
-A second method that is run inside each device thread is \texttt{periodicDeviceUpdateMethod}, defined in Figure~\ref{fig:periodicDeviceUpdateMethod}, is started when the discovery agent sets the discovered device to active.
+A second method that is run inside each device thread is \texttt{periodicDeviceUpdateMethod}, defined in Figure~\ref{fig:periodicDeviceUpdateMethod}, which is started when the discovery agent sets the discovered device to active.
 By first loading the device's API name, the scheduling agent can begin checking for scheduling periods inside an infinite loop.
@@
 The second function, \texttt{communicate\_with\_iBEMS} will open another socket but with the IP address of the iBEMS core found in \texttt{connect\_to\_iBEMS}.
-It will then enter a indefinite loop to continually receive data from the iBEMS core.
+It will then enter an indefinite loop to continually receive data from the iBEMS core.
 There are 4 different messages that the iBEMS core sends to the embedded computer.

### 2021-05-07 parts/C-WemoSetup.tex
Updated report

\chapter{WeMo Insight Switch Setup}
\label{ap: appendixC}

This appendix describes the steps required to connect the WeMo Switch to a WiFi network. A prerequisite requires downloading the Wemo app from Google Play or the Apple App Store. In order to initiate the connection process, the WeMo must be plugged into an outlet while holding down the the reset button for 5 seconds. This should allow the WeMo to broadcast its own WiFi network titled \say{WeMo.Insight.23A}. This WiFi network must be connected to allow the device to be paired with the desired network.

\section{Create a WeMo account}
If the app was recently downloaded, a screen shown in Figure~\ref{fig:signInWemo} is displayed where the user can either create an account or sign in with an existing account.
\begin{figure}[H]
\centering
\includegraphics[scale=0.09]{figs/wemoApp/signInWemo.png}
\caption{WeMo app sign-in page}
\label{fig:signInWemo}
\end{figure}

\section{Name the device}
A screen will appear asking the user to enter the friendly name of the device as in Figure~\ref{fig:nameDevice}
\begin{figure}[H]
\centering
\includegraphics[scale=0.09]{figs/wemoApp/nameDevice.png}
\caption{Name device page}
\label{fig:nameDevice}
\end{figure}

\section{Pair WiFi network with the WeMo}
If the plug's WiFi network is connected to on the user's phone, the user will be prompted to connect to the desired WiFi network. Once this pairing is complete the screen in Figure~\ref{fig:completedSetup} will appear.
\begin{figure}[H]
\centering
\includegraphics[scale=0.09]{figs/wemoApp/setupComplete.png}
\caption{Completed setup}
\label{fig:completedSetup}
\end{figure}

\section{Control the WeMo}
If everything was setup successfully, the user should be able to turn on and off the WeMo and see the power usage as in Figure~\ref{fig:smartPlutControl}.
\begin{figure}[H]
\centering
\includegraphics[scale=0.09]{figs/wemoApp/wemoAppControl.png}
\caption{Control the smart plug}
\label{fig:smartPlutControl}
\end{figure}

If any problems were encountered during the setup process, the user can go to\\
\href{https://www.wemo.com/support/}{https://www.wemo.com/support/}. Also, the paper manual provided with the WeMo box can provide additional support as it provides a comprehensive step-by-step process.

### 2021-05-08 parts/40-ExperimentalResults.tex
Updated file paths and added figures

@@
     \centering
-    \includegraphics[scale=0.5]{figs/BEMS_GUI_Linux.png}
+    \includegraphics[scale=0.5]{figs/GUI/BEMS_GUI_Linux.png}
     \caption{Desktop GUI}
@@
     \centering
-    \includegraphics[scale=0.5]{figs/BEMS_GUI_Linux_Warning.png}
+    \includegraphics[scale=0.5]{figs/GUI/BEMS_GUI_Linux_Warning.png}
     \caption{Popup Error}
@@
     \centering
-    \includegraphics[scale=0.5]{figs/Login.png}
+    \includegraphics[scale=0.5]{figs/webServer/Login.png}
     \caption{Login Page}
@@
     \centering
-    \includegraphics[scale=0.35]{figs/Home_screen.png}
+    \includegraphics[scale=0.35]{figs/webServer/Home_screen.png}
     \caption{Home Page}
@@
     \centering
-    \includegraphics[scale=0.35]{figs/ActiveDevices_screen.png}
+    \includegraphics[scale=0.35]{figs/webServer/ActiveDevices_screen.png}
     \caption{Active Devices Page}
@@
     \centering
-    \includegraphics[scale=0.35]{figs/ActiveDevices_plot.png}
+    \includegraphics[scale=0.35]{figs/webServer/ActiveDevices_plot.png}
     \caption{Active Devices Plot}
@@
     \centering
-    \includegraphics[scale=0.35]{figs/Applications_screen.png}
+    \includegraphics[scale=0.35]{figs/webServer/Applications_screen.png}
     \caption{Scheduling Page}

### 2021-05-08 parts/20-iBEMSArchitecture.tex
Updated file paths and added figures
Updated figs
Updated report

@@
 %
-\begin{figure}
+\begin{figure}[H]
   \centering
-  \includegraphics[scale=0.3]{figs/highLevelArchitecture.pdf}
+  \includegraphics[scale=0.3]{figs/overallConnectionDiagram.pdf}
   \caption{High Level Architecture of the Proposed System}
@@
 found from this circuit by 4 will give an approximation of the total power used
-by the robot. \add{For other robots with different power sources besides a Lipo
-battery.} See Figure~\ref{fig:motorInterfaceCircuit} for details of the interface
-circuit for computer power usage by the DC motor.
+by the robot. See Figure~\ref{fig:motorInterfaceCircuit} for details of the interface
+circuit for computer power usage by the DC motor. Also see Figure~\ref{fig:bb_connections} for how the circuit is connected to the embedded computer and robot chassis.
 
-\begin{figure}
+\begin{figure}[H]
   \centering
@@
 
+\begin{figure}[H]
+    \centering
+    \includegraphics[scale=0.6]{figs/beaglebone/connections.pdf}
+    \caption{Connections between Embedded Computer, circuit, and robot chassis}
+    \label{fig:bb_connections}
+\end{figure}
+
 % \pagebreak
@@
     \centering
-    \includegraphics[scale=0.1]{figs/notConnectedSBC.jpg}
+    \includegraphics[scale=0.07]{figs/beaglebone/notConnectedSBC.jpg}
     \caption{Embedded Computer Not Connected}
@@
     \centering
-    \includegraphics[scale=0.1]{figs/connectedSBC.jpg}
+    \includegraphics[scale=0.07]{figs/beaglebone/connectedSBC.jpg}
     \caption{Embedded Computer Connected}
@@
     \centering
-    \includegraphics[scale=0.085]{figs/wemoView.jpg}
+    \includegraphics[scale=0.07]{figs/wemo/wemoView.jpg}
     \caption{WeMo Insight Smart Plug}
@@
     \centering
-    \includegraphics[scale=0.1]{figs/overallView.jpg}
+    \includegraphics[scale=0.07]{figs/overallView.jpg}
     \caption{Overall View}

### 2021-05-08 parts/D-EmbeddedComputerSetup.tex
Updated report

\chapter{Embedded Computer Setup}
\label{ap: appendixD}

This appendix describes the steps required to connect an embedded computer to the iBEMS Core.

\section{Connect to router}
In our project, we used a BeagleBone Blue for the embedded computer. To connect to your specific router, first plug in the BeagleBone Blue to your computer with a microUSB cable. Then open a terminal and install \say{screen} with the command \say{sudo apt install screen}. You will then need to find the USB driver being used for the beaglebone with \say{dmesg}. Scroll through the information until you find the BeagleBone:

\begin{figure}[H]
\centering
\includegraphics[scale=0.4]{figs/beaglebone/findUSBdriver.png}
\caption{Finding USB Driver}
\label{fig:bb_findUSB}
\end{figure}

In Figure~\ref{fig:bb_findUSB}, it can be seen that \say{ttyACM0} is the USB driver being used.

With that knowledge, you can now enter the command \say{sudo screen /dev/ttyACM0} to login into the Beaglebone Blue. Enter username \say{debian} and password \say{temppwd} to login.
\medbreak
Once you are logged into the Beaglebone Blue, follow these instructions to connect to your router:
\href{http://www.strawsondesign.com/\#!manual-wifi}{http://www.strawsondesign.com/\#!manual-wifi}.

\section{Copy Necessary Files}
Now that the Beaglebone Blue is connected to the router, you need to copy some files to it. First, find the IP address of the BeagleBone Blue with the command \say{ifconfig wlan0}:

\begin{figure}[H]
\centering
\includegraphics[scale=0.4]{figs/beaglebone/findIPaddress.png}
\caption{Finding IP Address}
\label{fig:bb_findIP}
\end{figure}

Figure~\ref{fig:bb_findIP} shows the output of \say{ifconfig wlan0} and it can be seen that the IP address in this case is \texttt{192.168.1.107}.
\medbreak
You can now open a new native linux terminal and go the the \say{seniorProject1-2020-21-Code} directory. Once there, copy the necessary files with commands:
\\
\say{scp BeagleboneReceiver.py debian@192.168.1.107:/home/debian},
\\
\say{scp BeagleBoneSupportFiles/LED.py debian@192.168.1.107:/home/debian},
\\
\say{scp BeagleBoneSupportFiles/PWM.py debian@192.168.1.107:/home/debian}.
You may get a warning message about the authenticity of the host, but simply type \say{yes} as response to this warning.

\section{Running the BeagleBone Receiver}
With the necessary files on the BeagleBone Blue, you can go back the BeagleBone Blue terminal and enter the command \say{python3 BeagleboneReceiver.py}. Finally, you can start iBEMS and it will connect to the Beaglebone Blue automatically.

### 2021-05-08 finalReportPres.tex
Added files for presentation
Removed filed, updated flie paths

@@
 
-\begin{frame}{Agent and Web Server Communication}{}
-    \begin{figure}
-        \centering
-        \includegraphics[scale=0.5]{figs/pubSubAgents.pdf}
-        \caption{Publish Subscribe Model}
-        \label{fig:pubSubModel}
-    \end{figure}
-    \begin{itemize}
-        \item Agents and web server use the ZeroMQ
-        messaging library
-        \item Python wrapper used
-    \end{itemize}
-\end{frame}
+% \begin{frame}{Agent and Web Server Communication}{}
+%     \begin{figure}
+%         \centering
+%         \includegraphics[scale=0.5]{figs/pubSubAgents.pdf}
+%         \caption{Publish Subscribe Model}
+%         \label{fig:pubSubModel}
+%     \end{figure}
+%     \begin{itemize}
+%         \item Agents and web server use the ZeroMQ
+%         messaging library
+%         \item Python wrapper used
+%     \end{itemize}
+% \end{frame}
 
@@
             \centering
-            \includegraphics[scale=0.04]{figs/notConnectedSBC.jpg}
+            \includegraphics[scale=0.04]{figs/beaglebone/notConnectedSBC.jpg}
             \caption{Embedded Computer Not Connected}
@@
             \centering
-            \includegraphics[scale=0.04]{figs/connectedSBC.jpg}
+            \includegraphics[scale=0.04]{figs/beaglebone/connectedSBC.jpg}
             \caption{Embedded Computer Connected}
@@
         \centering
-        \includegraphics[scale=0.045]{figs/wemoView.jpg}
+        \includegraphics[scale=0.045]{figs/wemo/wemoView.jpg}
         \caption{WeMo Insight Smart Plug}
@@
         \centering
-        \includegraphics[scale=0.3]{figs/periodicQueryBehaviorFlow.pdf}
+        \includegraphics[scale=0.3]{figs/agents/periodicQueryBehaviorFlow.pdf}
         \caption{periodicQueryBehavior Flow Chart}
@@
         \centering
-        \includegraphics[scale=0.4]{figs/setDeviceToActiveFlow.pdf}
+        \includegraphics[scale=0.4]{figs/agents/setDeviceToActiveFlow.pdf}
         \caption{setDeviceToActive Flow Chart}
@@
         \centering
-        \includegraphics[scale=0.3]{figs/searchForDevicesFlow.pdf}
+        \includegraphics[scale=0.3]{figs/agents/searchForDevicesFlow.pdf}
         \caption{searchForDevices Flow Chart}
@@
         \centering
-        \includegraphics[scale=0.30]{figs/Beaglebone_Receiver_Diagram.pdf}
+        \includegraphics[scale=0.30]{figs/beaglebone/Beaglebone_Receiver_Diagram.pdf}
         \caption{Receiver Running on Embedded Computer}
@@
             \centering
-            \includegraphics[scale=0.2]{figs/BEMS_GUI_Linux.png}
+            \includegraphics[scale=0.2]{figs/GUI/BEMS_GUI_Linux.png}
             \caption{Desktop GUI}
@@
             \centering
-            \includegraphics[scale=0.35]{figs/BEMS_GUI_Linux_Warning.png}
+            \includegraphics[scale=0.35]{figs/GUI/BEMS_GUI_Linux_Warning.png}
             \caption{Popup Error}
@@
         \centering
-        \includegraphics[scale=0.4]{figs/GUI_Diagram.pdf}
+        \includegraphics[scale=0.4]{figs/GUI/GUI_Diagram.pdf}
         \caption{Diagram for Startup Menu Functionality}
@@
         \centering
-        \includegraphics[scale=0.2]{figs/Home_screen.png}
+        \includegraphics[scale=0.2]{figs/webServer/Home_screen.png}
         \caption{Home Screen}
@@
             \centering
-            \includegraphics[scale=0.13]{figs/ActiveDevices_screen.png}
+            \includegraphics[scale=0.13]{figs/webServer/ActiveDevices_screen.png}
             \caption{Active Devices Page}
@@
         \centering
-        \includegraphics[scale=0.15]{figs/ActiveDevices_plot.png}
+        \includegraphics[scale=0.15]{figs/webServer/ActiveDevices_plot.png}
         \caption{Active Devices Plot}
@@
             \centering
-            \includegraphics[scale=0.15]{figs/Applications_screen.png}
+            \includegraphics[scale=0.15]{figs/webServer/Applications_screen.png}
             \caption{Scheduling Page}
@@
           \begin{itemize}
-            \item Clicking on "Applications" on the nav bar loads the weekly scheduling feature
+            \item Clicking on "Device Scheduling" on the nav bar loads the weekly scheduling feature
             \item User can input whatever times they want with devices to be in a specified state (on/off for WeMo plug and duty cycle for the embedded computer)

### 2021-07-19 paper1-IEEE-ROSE-2021.tex
Added paper1-IEEE-ROSE-2021.tex latex code for the paper

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts,bm,physics}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{caption}
\usepackage[list=true,labelformat=simple]{subcaption}
\captionsetup[sub]{skip=2pt}
\renewcommand\thesubfigure{(\alph{subfigure})}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage[colorinlistoftodos]{todonotes}
\usepackage{siunitx}
\usepackage{nohyperref}

\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

\title{ Towards the Development of an Intelligent Building Energy Management System -- iBEMS
  \thanks{The results presented in this paper were produced by a group of senior
    undergraduate students: Brian Lauer and Elliot Watkins }
}

\author{\IEEEauthorblockN{Brian Lauer, Elliot Watkins, and Md Suruz Miah}
\IEEEauthorblockA{\textit{Department of Electrical and Computer Engineering} \\
\textit{Bradley University}\\
Peoria, Illinois, United States of America \\
\{blauer, ejwatkins\}@mail.bradley.edu, smiah@bradley.edu}
}

\maketitle

\begin{abstract}

  Smart building energy management and/or monitoring has recently emerged as a
  promising task due to global climate change issues. Such a task has received
  thorough attention for the advent of emerging Internet-of-Things (IoT)
  technology. Numerous building energy management systems are commercially
  available in the market. Most of them lack modularity or are driven by an
  overwhelming degree of manual configurations for performing building
  automation. In this paper, we present the development of a modular IoT-based framework for an intelligent building energy management system (iBEMS). The proposed framework is open-source and leverages the features of decentralized multi-agent systems. The principal component of the framework is the BEMS core that implements building automation features, such as an optimal scheduler, displaying weather information, detecting new IoT devices, monitoring energy consumption, and remotely controlling operation of IoT devices.

\end{abstract}

\begin{IEEEkeywords}
  mobile robots, navigation, radio frequency identification, robotic cart 
\end{IEEEkeywords}

\section{Introduction}
\label{sec:introduction}

The Internet of Things (IoT) is a large network of embedded devices such as sensors, wearables, and appliances capable of receiving control commands and reporting
data over the Internet. Many industries take advantage of this infrastructure to
improve process flow and efficiency. One of these industries is the commercial
and industrial sector which often employ building automation or management
systems to help better manage processes or devices in a building like air
conditioning systems, lights or industrial machines. Technological advancements
have allowed devices to become connected to a building network through
communication protocols like WiFi, Ethernet, Modbus, or BACnet which enables
them to be more easily controlled from a central system.

The overall goal of this work is to create a platform in which users can login and access devices
connected to a building's energy supply. This will allow the user to closely
monitor energy usage throughout a commercial or residential building.
Additionally, the user will be able to control devices connected to the
platform, allowing precise control over the building's energy use. The minimum
viable product of this project will be to connect to 1 to 3 devices via the the
platform and control them.

% The previous senior project group worked on creating a remote motor control system with a Raspberry Pi and XBee module. To supply power directly to the motor and XBee with a single power supply, they used a buck-boost converter capable of stepping down power supply voltage to 3.3 V. They implemented a Python script that uses the Linux command \texttt{nmap} to search for the Raspberry Pi on the network. The Raspberry Pi connects to the transmitter XBee via a serial connection to transmit commands to the receiver XBee mounted to the motor. They were able to simply toggle the motor on and off and partially implemented this functionality in BEMOSS (Building Energy Management Open Source Software). A second portion of their project was implementing an HVAC control algorithm capable of controlling the temperature of a home with the Linear Quadratic Regulator control algorithm.

% During a research project led by Miah \textit{et al.,} the DC motor interface was successfully
% implemented into the BEMOSS platform which required adding a great deal of source code
% to the platform to fully implement the device as BEMOSS does not support adding
% new devices currently. The research also consisted of adding new
% features such as a logo to the
% platform for the motor. A possible improvement our platform will make is helping
% developers on the project add new devices more easily.

% One of the improvements our project makes over the previous is the use of UDP (user datagram protocol) multicasting which does not require any superuser privileges to locate an
% embedded computer (Beaglebone Blue, for example). This implementation is also more convenient
% because it does not require installing any packages as multicasting is natively
% supported by most embedded Linux systems. If in the future, multiple embedded
% computers are needed to be discovered, the multicasting system works elegantly
% as each device can simply listen on a provided multicast group which consists of
% an IP address and port number.

A great deal of research has been conducted in the field of building energy
management. Multiple different platforms have been developed that demonstrate
the vast amount of features and possibilities that exist in developing these
types of software. One such platform is
BEMOSS\footnote{\href{https://www.bemoss.org}{https://www.bemoss.org}} (Building
Energy Management Open Source Software) from the Virginia Polytechnic Institute
and State University Advanced Research Institute. BEMOSS features include being
open-source, allowing for multiple communication technologies, and supporting
many common IoT devices. This system allows for monitoring and controlling a
variety of devices securely.

Another open-source platform is rEMpy or residential Energy Management in
Python~\cite{FAGIANI2018131}. The main focus of this platform developed by a team of researchers at
Universit\`{a} Politecnica delle Marche in Ancona, Italy was to simulate the
energy flow of a residential home. With the data collected from simulations, it
was possible for them to use forecasting and prediction algorithms to predict
various quantities such as energy usage and power consumption over a given time period. Their energy management system consists of a well-defined structure with components like a user interface, database, and optimal scheduler that communicate with modules like a prediction and thermal model. In terms of software technologies, it uses the Django web framework which provides a lot of built-in functionality for web development like a user-authentication system and object-relational mapping. Adapting the project to this framework could be a great way to help improve security and optimize database queries~\cite{fagiani2017}.

Authors in~\cite{Mayer2017} discusses Model Predictive Control (MPC)
which is a modern process control algorithm capable of taking into account
current and previous time values to improve building
automation. A multilevel hierarchy is presented to split
control of a building into two levels: the energy supply level and user level.
Example usage of this control scheme provided are temperature control of a
building and its corresponding zones and interaction with a smart grid. Studies
were performed on a commercial building with the building's energy supply system
and hierarchy model predictive controller implemented in Matlab.

In~\cite{8246800}, authors describe similar functional requirements to our
own BEMS Core. They periodically gather power consumption and device status data
and send that data to a database. The communication with devices
and power consumption reports are to be accessible through a web-based
application that is easy to use. The implementation of the iBEMS platform presented herein is simple and very
intuitive for the end-user.

A control scheme in~\cite{Barchi2018} is presented to manage a photovoltaic
array and battery energy storage system. Tests were conducted in a shopping mall
with an electronic load to emulate the power consumption of the building.
Potentially, a similar technique could be used to model the energy demand of a
house in Simulink or Simscape model. Through their scheme, an intelligent BEMS
is used to collect measurable data such as power, voltage, and current and stored for offline analysis later. Their platform collects data every five minutes compared to the 20 second polling rate currently configured in our platform. A control algorithm was presented proving that grid energy is consumed more heavily during periods of low power demand rather than PV power.

The ultimate goal of the current work is to design and develop a new building energy management
platform incorporating learning, control, and estimation strategies, which is expected to remedy the
shortcomings of some existing platforms, BEMOSS, for instance.

\section{iBEMS Architecture}
\label{sec:iBEMS-Architecture}

At the center of the iBEMS architecture is the iBEMS core. This core interacts
with multiple peripherals including IoT devices and a weather API over the
internet. In this work, we developed the iBEMS to support for two 
IoT devices displayed in the high-level architecture shown in Fig.~\ref{fig:highLevelArchitecture}. %
%
\begin{figure}[htbp]
  \centering
  \includegraphics[scale=0.15]{figs/overallConnectionDiagram.pdf}
  \caption{High-level architecture of the proposed iBEMS.}
  \label{fig:highLevelArchitecture}
\end{figure}
%
These devices are the WeMo Insight Switch and an embedded computer known as the Beaglebone
Blue.  The core is also able to
connect the internet to download weather data for a local city through
OpenWeatherMap. Fig.~\ref{fig:functional_bd} gives the lower level functional block diagram of the system
architecture. %
%
\begin{figure}[htbp]
  \centering
  \includegraphics[scale=0.15]{figs/functionalBlockDiagram.pdf}
  \caption{Functional Block Diagram}
  \label{fig:functional_bd}
\end{figure}
%
The inputs include the user input through the web server, the device status
updates (On/Off, power usage, etc...) and the weather data. The iBEMS Core
itself consists of a Flask Web Server, 2 databases (Apache Cassandra and
SQLite), and 3 software agents (Discovery, Control, and Scheduling).

The Flask web server is built using a Python web framework titled Flask which
allows programmers to develop a dynamic web server capable of rendering data to
HTML pages. The benefit of this framework over other Python web frameworks like
Django is the large amount of customization available. For example, the
developers can create a completely custom user login system. For now, the server
is capable of being accessed only on the server computer running Ubuntu Linux.
In the future, support could be added to allow any user on the LAN to access the
web server. Other web frameworks use object relational mapping directly to
access the relevant databases. However, the current iBEMS uses direct queries with both
SQLite and the Cassandra query language to query the databases. We used
2 different databases to store information on. The Apache Cassandra database was
better suited for the time series data such as device status and power usage.
This database was therefore utilized a lot by the Control and Scheduling Agents.
The SQLite database hold parameters that do not change over time like device
ID's, IP addresses, and MAC addresses which made it amendable to the processes
in the Discovery Agent. The first agent that is
used by the iBEMS Core on startup is the discovery agent. It is responsible for
reaching out on the network and finding all devices that the iBEMS Core has
support for. This process involves retrieving the following parameters: IP
address, Port number, MAC address, Manufacturer, Name, and API. Once all
available devices are connected, the Control agent is used to change the status
of each device and collect power usage data in real time. Finally, the
scheduling will take input from the user and place the corresponding scheduling
periods in the Apache Cassandra database. Then, a thread is created to poll the
current device status at regular intervals and update the status if it does not
match the defined status in the Apache Cassandra database.

Fig.~\ref{fig:systemComponentInterconnection} provides an explanation of how
the components of the system interact with each other. %
%
\begin{figure}
  \centering
  \includegraphics[scale=0.15]{figs/overallDiagram.pdf}
  \caption{Interconnection between system components}
  \label{fig:systemComponentInterconnection}
\end{figure}
%
The Apache Cassandra database and SQLite database are accessible from the web server, control agent, discovery agent, and scheduling agent. The web server queries the time series database and metadata database for vastly different purposes. Power plotting requires querying the Apache Cassandra database. To distinguish between the different devices on the front end, the metadata database is used. The agents utilize the Apache Cassandra database for storing and extracting time-series data. The agents use the metadata database to distinguish between different devices.

% There are five general modes of operation in iBEMS shown in Fig.~\ref{fig:operationalModes}. In Mode 0, before iBEMS is even launched, the user must open the Startup Menu, which is a desktop graphical user interface (GUI). This is a simple GUI with only 2 buttons for starting and stopping iBEMS. Upon clicking \say{Start iBEMS}, the login page will load where the user can enter a valid username and password to use iBEMS. Once a valid username and password is entered, the home screen will be shown which displays the weather data being downloaded from the OpenWeatherMap API. This information includes temperature in Fahrenheit and Celsius, wind speed in MPH, humidity, and cloud coverage. At this point, a navigation bar is available to view the \say{Active Devices} page and the \say{Scheduling} page. \say{Active Devices} corresponds to Mode 3 for controlling devices in real time. The user will also be able to view power plots in this mode as well. Lastly, the \say{Scheduling} page is Mode 4 for creating schedules for all connected devices.

% \begin{figure}
%   \centering
%   \includegraphics[scale=0.4]{figs/operationalModes.pdf}
%   \caption{Operation Modes Interaction}
%   \label{fig:operationalModes}
% \end{figure}

% \section{Hardware}

% A large feature of this project was being able to record power usage from the
% connected IoT devices. The embedded computer does not have a built-in capability
% to measure its own power usage, so a circuit was needed to make that
% possible. Essentially, this circuit will measure the current being used to drive
% one of the motors on the robot chassis. The on-board Analog-to-Digital-Converter
% (ADC) can be used to read the voltage across the resistor and since the
% resistance is known, the current can be calculated as $I = V/R$. Also, the
% voltage from the H-Bridge to drive the motors on the embedded computer is known
% so the power consumed by 1 motor is $Motor Drive Voltage * I$. For the specific
% robot chassis used in this project, there are 4 motors, so multiplying the power
% found from this circuit by 4 will give an approximation of the total power used
% by the robot. See Figure~\ref{fig:motorInterfaceCircuit} for details of the interface
% circuit for computer power usage by the DC motor. Also see Figure~\ref{fig:bb_connections} for how the circuit is connected to the embedded computer and robot chassis.

% \begin{figure}[H]
%   \centering
%   \begin{circuitikz}[american]
%     \tikzstyle{every node} = [font = \tiny]
%     % \usetikzlibrary{patterns}
%     \draw
%     (0,0) to[sqV,invert,l=Motor Drive Voltage from H-Bridge] ++(0,4*\smgrid)
%     to[Telmech=M,n=motor,fill=red!20] ++(4*\smgrid,0)
%     to[C,l=$1~{[}\mu F{]}$,*-*] ++(0,-4*\smgrid) to[short]++(-4*\smgrid,0); 
%     \draw
%     (4*\smgrid,4*\smgrid) to[short,-*]++(3*\smgrid,0)
%     to[short,-o]++(2*\smgrid,0)node[right]{Embedded Computer ADC (Ch\#0)};
%     \draw
%     (7*\smgrid,4*\smgrid) to[R,l=$2~{[}\Omega{]}$,-*]++(0,-4*\smgrid)
%     to[short]++(-4*\smgrid,0);
%     \draw
%     (7*\smgrid,0) to[short,-o]++(2*\smgrid,0) node[right]{Embedded
%       Computer ADC (Ground)};
%   \end{circuitikz}
%   \caption{Interface circuit to calculate power consumption of a DC motor
%     running from the embedded computer copmuter.}
%   \label{fig:motorInterfaceCircuit}
% \end{figure}

% \begin{figure}[H]
%     \centering
%     \includegraphics[scale=0.6]{figs/beaglebone/connections.pdf}
%     \caption{Connections between Embedded Computer, circuit, and robot chassis}
%     \label{fig:bb_connections}
% \end{figure}

% % \pagebreak
% \begin{figure}[H]
%     \centering
%     \includegraphics[scale=0.07]{figs/beaglebone/notConnectedSBC.jpg}
%     \caption{Embedded Computer Not Connected}
%     \label{fig:not_connected_bb}
% \end{figure}

% Figure~\ref{fig:not_connected_bb} shows the embedded computer mounted on the robot chassis with the circuit shown on page 9. It can also be seen that the embedded computer lights up the on-board red LED when disconnected. Figure~\ref{fig:connected_bb} shows that the embedded computer lights up the green LED when it is connected as an extra indication of its connection status.

% \begin{figure}[H]
%     \centering
%     \includegraphics[scale=0.07]{figs/beaglebone/connectedSBC.jpg}
%     \caption{Embedded Computer Connected}
%     \label{fig:connected_bb}
% \end{figure}

% \begin{figure}[H]
%     \centering
%     \includegraphics[scale=0.07]{figs/wemo/wemoView.jpg}
%     \caption{WeMo Insight Smart Plug}
%     \label{fig:wemo}
% \end{figure}

% The other supported device is the WeMo Insight Switch as seen in Figure~\ref{fig:wemo}. This device was easy to develop support for as it is meant for building energy management. It simply plugs into a 120 volt 3-prong outlet and any typical household appliance running on 120 volts can be plugged into it. Internal circuitry allows the WeMo to be controlled remotely (turn On/Off) and to record power usage of whatever it is plugged into.

% \begin{figure}[H]
%     \centering
%     \includegraphics[scale=0.07]{figs/overallView.jpg}
%     \caption{Overall View}
%     \label{fig:overallView}
% \end{figure}

% In order to test these devices, we plugged a bank of 6 light bulbs into the WeMo
% Insight Switch as seen in Figure~\ref{fig:overallView}. The embedded computer's
% functionality was tested with the circuit and robot chassis described earlier.

\bibliographystyle{IEEEtran}
\bibliography{bib/references.bib}

\end{document}

### 2021-07-19 paper1-IEEE-ROSE-2021.tex
Added implementation section

@@
 \usepackage{nohyperref}
+\usepackage{dirtytalk}
 
@@
 
+\section{Software Implementation}
+\label{sec:SoftwareImplementation}
+
+To provide the ability to recognize and control devices at any moment, three agents are used.
+All three agents communicate with each other and the web server using the Zero MQ asynchronous messaging library.
+Essentially, this library works as a way to implement inter process communication without a message
+broker~\cite{zeromq}. In other words, different processes are able to communicate with each
+other without any central bus. This is convenient as fewer processes are needed for the system to function. Lowering the number of overall processes lowers the
+RAM and CPU usage of the software. The library is ported to many different programming languages; however we are using the Python port titled Pyzmq to
+implement in our code base.
+%
+\begin{figure}[htbp]
+    \centering
+    \includegraphics[width=0.4\textwidth]{figs/agents/pubSubAgents.pdf}
+    \caption{Publish Subscribe Communication using ZeroMQ}
+    \label{fig:pubSubAgents}
+\end{figure}
+
+More specifically, the publish subscribe model of communication is used where
+each agent communicates via a socket where each socket responds to a specific
+topic. The topics and port numbers are listed below along with their
+corresponding agents in Table~\ref{tab:pubsubspecs}. %
+%
+\begin{table}[htbp]
+    \centering
+    \begin{tabular}{|c|c|c|}
+        \hline
+        Agent & Topic & Port Number\\
+        \hline
+        Discovery Agent & "discovery" & 5556\\
+        Scheduling Agent & "scheduling" & 5556\\
+        Control Agent & "control" & 5556\\
+        \hline
+    \end{tabular}
+    \caption{Publish/Subscribe Communication Specifications}
+    \label{tab:pubsubspecs}
+\end{table}
+The agents contained in the software are associated with a Python class of the
+same name. Each class is instantiated and run with specifications declared in
+Table~\ref{tab:pubsubspecs}.
+
+The flow chart of method \texttt{setDeviceStatus} defined in the \texttt{ControlAgent} class is shown in
+Figure~\ref{fig:setDeviceStatus}. The purpose of this method is to set the
+status of the desired device. When the method is called, the data dictionary is
+obtained which contains the device ID. With this device ID, the API type can be
+determined using the SQLite database. Subsequently, the appropriate device API
+module can be imported. If the power state exists as a key in the device data
+dictionary, the power state of the WeMo Insight Switch will be set as ON or OFF.
+If the duty cycle key exists, the duty cycle of the single board computer motor
+drivers is set. If the shutdown key is set, the single board computer is
+shutdown. In order to reconnect to the single board computer, the board must be
+started and receiver program ran. If necessary, the device must be reconnected
+to the WiFi network. %
+
+\begin{figure}[htbp]
+    \centering
+    \includegraphics[scale=0.3]{figs/agents/setDeviceStatus.pdf}
+    \caption{setDeviceStatus Flow Chart}
+    \label{fig:setDeviceStatus}
+\end{figure}
+
+To obtain necessary data quantities from the device, the
+\texttt{getDeviceStatus} method defined in \texttt{ControlAgent}, defined in Figure~\ref{fig:getDeviceStatus}, is called. Once the proper data parameters are
+obtained, the \texttt{getState} function defined in the devices API module can
+be called with the data parameters such as power state and
+status. Once the agent has finished sending these to the device, a request is
+sent to the web server to inform the server that it completed searching for the
+required device data. %
+%
+\begin{figure}[htbp]
+    \centering
+    \includegraphics[scale=0.4]{figs/agents/getDeviceStatus.pdf}
+    \caption{getDeviceStatus Flow Chart}
+    \label{fig:getDeviceStatus}
+\end{figure}
+
+Every device connected to iBEMS will have a thread associated with it started from the control agent.
+This thread will run the \texttt{periodicQueryBehavior} method defined in \texttt{ControlAgent} to periodically query for device data and store in the corresponding Cassandra database table.
+A user specified delay is placed in the class's module to prevent the thread from overwhelming the system.
+
+\begin{figure}[htbp]
+    \centering
+    \includegraphics[scale=0.4]{figs/agents/periodicQueryBehavior.pdf}
+    \caption{periodicQueryBehavior Flow Chart}
+    \label{fig:periodicQueryBehavior}
+\end{figure}
+
+To reduce latency, the device status is retrieved directly from the API module in the \texttt{periodicQueryBehavior} method defined in \texttt{ControlAgent} rather than calling \texttt{getDeviceStatus} as this prevents the API from being imported unnecessarily.
+
+The scheduling agent is able to update the device status of each device dependent on whether a schedule is set for the specific time period and day.
+One of the methods that is called, \texttt{updateScheduleFromServer} is invoked when the user presses the \say{Update Schedule} button from the UI on the scheduling page.
+A flow chart of this method is shown in Figure~\ref{fig:updateScheduleFromServer}.
+When this method is called the desired schedule is loaded in as a dictionary and parsed to extract the necessary periods and given day.
+First the times are stored in military time in the database for more convenient storage and parsing later on.
+Then, a table is created in the Apache Cassandra database where the device ID and day are embedded in the name.
+The previous table's data is destroyed to ensure there are no errors regarding overlapping schedules.
+Lastly, all the scheduling periods extracted from the dictionary are stored as rows in the table.
+\begin{figure}[htbp]
+    \centering
+    \includegraphics[scale=0.3]{figs/agents/updateScheduleFromServer.pdf}
+    \caption{updateScheduleFromServer Flow Chart}
+    \label{fig:updateScheduleFromServer}
+\end{figure}
+A second method that is run inside each device thread is \texttt{periodicDeviceUpdateMethod}, defined in Figure~\ref{fig:periodicDeviceUpdateMethod}, which is started when the discovery agent sets the discovered device to active.
+By first loading the device's API name, the scheduling agent can begin checking for scheduling periods inside an infinite loop.
+The status dictionary is queried from the Cassandra database and loaded into a dictionary.
+All these scheduling periods are looped over for the current day while constantly checking whether the current time in seconds is within the starting and ending time.
+A conversion of both starting and ending time to seconds is necessary as it is challenging to work with these quantities in standard and military time when comparing times.
+If the current time does lie inside the scheduling period, the device's state is set dependent on the API.
+\begin{figure}[htbp]
+    \centering
+    \includegraphics[scale=0.3]{figs/agents/periodicDeviceUpdateMethod.pdf}
+    \caption{periodicDeviceUpdateMethod Flow Chart}
+    \label{fig:periodicDeviceUpdateMethod}
+\end{figure}
+
+\begin{figure}[htbp]
+    \centering
+    \includegraphics[scale=0.25]{figs/beaglebone/Beaglebone_Receiver_Diagram.pdf}
+    \caption{Receiver Running on Embedded Computer}
+    \label{fig:Beaglebone_Receiver_Diagram}
+\end{figure}
+
+The embedded computer needed some software to be able to connect to and communicate with the iBEMS Core. To achieve this, a program consisting of 2 functions for connecting and communicating is used.
+\medbreak
+The first of these functions is \texttt{connect\_to\_iBEMS}.
+This function first turns on the red LED on the embedded computer to indicate it is not yet connected.
+Then it creates a socket using a multicast IP address that the corresponding API in the iBEMS core will be looking for.
+Once the socket is created, the embedded computer will enter a loop and wait for the iBEMS core to make the initial connection.
+When that connection is made, it will exit the loop, save the IP address of the iBEMS core, send a confirmation message, then turn on the green LED before closing the multicast socket.
+\medbreak
+The second function, \texttt{communicate\_with\_iBEMS} will open another socket but with the IP address of the iBEMS core found in \texttt{connect\_to\_iBEMS}.
+It will then enter an indefinite loop to continually receive data from the iBEMS core.
+There are 4 different messages that the iBEMS core sends to the embedded computer.
+First, it will check if the iBEMS core is telling it to shut down with the command \say{Shutdown}.
+If so, the embedded computer will immediately shut down.
+Second, if the data sent by iBEMS is \say{status}, the embedded computer will take a reading from the power measurement circuit.
+In case the user decides to shut down the iBEMS core without turning off the embedded computer, another message \say{disconnect} will be sent in which case the embedded computer will exit \texttt{communicate\_with\_iBEMS} and start the entire program over again.
+Finally, if iBEMS is not sending any of the above options, it means that the user is sending a new duty cycle to drive the motors with.
+Since iBEMS only sends messages with the string data type, this has to be converted to a float in order to call the motor driver function.
+
 % There are five general modes of operation in iBEMS shown in Fig.~\ref{fig:operationalModes}.

### 2021-07-19 paper1-IEEE-ROSE-2021.tex
Added Experimental Results Section

@@
 
+\section{Experimental Results}
+The system was tested with a working prototype, in which the first mode is the startup menu:
+
+\begin{figure}[htbp]
+    \centering
+    \includegraphics[scale=0.2]{figs/GUI/BEMS_GUI_Linux.png}
+    \caption{Desktop GUI}
+    \label{fig:desktopgui}
+\end{figure}
+
+\noindent
+Here, the user will simply click the \say{Start iBEMS} button to launch the web server and agents.
+When the user is finished, all agents and the web server can be shut down by clicking \say{Stop iBEMS}.
+In case the user accidentally clicks the \say{Start iBEMS} button while iBEMS is already running, then the following error message will appear:
+
+\begin{figure}[htbp]
+    \centering
+    \includegraphics[scale=0.5]{figs/GUI/BEMS_GUI_Linux_Warning.png}
+    \caption{Popup Error}
+    \label{fig:popuperror}
+\end{figure}
+
+\noindent
+After launching iBEMS, the web browser will open and the user will be presented with the login page:
+
+\begin{figure}[htbp]
+    \centering
+    \includegraphics[scale=0.3]{figs/webServer/Login.png}
+    \caption{Login Page}
+    \label{fig:Home_screen}
+\end{figure}
+
+\noindent
+where the user can enter in their username and password.
+Currently, iBEMS does not have a robust user login.
+It actually just has 1 username and password that is defined in the code.
+When the user enters the valid username and password, the home page will load automatically, where the weather data can be seen:
+
+\begin{figure}[htbp]
+    \centering
+    \includegraphics[scale=0.2]{figs/webServer/Home_screen.png}
+    \caption{Home Page}
+    \label{fig:Home_screen}
+\end{figure}
+
+The home screen (mode 2) does not have any interactive functionality other than to load another page by selecting one on the navigation bar.
+
+\begin{figure}[htbp]
+    \centering
+    \includegraphics[scale=0.2]{figs/webServer/ActiveDevices_screen.png}
+    \caption{Active Devices Page}
+    \label{fig:active_devices}
+\end{figure}
+
+Figure~\ref{fig:active_devices} shows the active devices page (mode 3) which is loaded upon clicking \say{Active Devices} in the navigation bar.
+Here, all the connected devices are shown in order of when they connected to iBEMS.
+As mentioned previously, control of the WeMo Insight Switch is limited to turning it on and off while the embedded computer's motor speed can be controlled by submitting different duty cycles.
+Additionally, the embedded computer can be completely turned off by clicking the \say{Shutdown} button.
+Both supported devices also log their power usage at regular intervals.
+A plot of these power usage data points can be viewed by clicking \say{View Status Plots}.
+
+\begin{figure}[htbp]
+    \centering
+    \includegraphics[scale=0.2]{figs/webServer/ActiveDevices_plot.png}
+    \caption{Active Devices Plot}
+    \label{fig:active_devices_plot}
+\end{figure}
+
+After clicking \say{View Status Plots}, a modal will pop up for the user to further interact with.
+By default, power usage data points for the current day are loaded at first, but another day can be selected by clicking on the calendar icon in the lower right corner.
+The plot is then updated by clicking \say{Update Plots}.
+This is done by collecting data from the Apache Cassandra database and simply plotting all the points found for the specified day.
+Underneath the plot, the total energy consumed for the specified day is displayed.
+That total energy is found using the trapezoid method for integration on the plot.
+
+\begin{figure}[htbp]
+    \centering
+    \includegraphics[scale=0.2]{figs/webServer/Applications_screen.png}
+    \caption{Scheduling Page}
+    \label{fig:schedulingl}
+\end{figure}
+
+Mode 4, or the scheduling page, can be loaded by clicking the \say{Device Scheduling} button in the navigation bar.
+Much like the active devices page, each connected device is listed in order of when they connected to iBEMS.
+Instead of directly controlling the devices, the user can enter in time periods when they want each device to maintain a specified status.
+For example, the WeMo Insight Switch can be scheduled to be on from 5 to 8 P.M.
+on Fridays.
+Likewise, the embedded computer can be scheduled to maintain a duty cycle of 0.5 for the same time period every Friday.
+Scheduled times can be added with the \say{Add new Period} and deleted by clicking the red \say{X} by the corresponding time period.
+
 % There are five general modes of operation in iBEMS shown in Fig.~\ref{fig:operationalModes}.

### 2021-07-19 paper1-IEEE-ROSE-2021.tex
Added label for experimental results section
~

@@
 Essentially, this library works as a way to implement inter process communication without a message
-broker~\cite{zeromq}. In other words, different processes are able to communicate with each
+broker\footnote{\href{https://zeromq.org/}{https://zeromq.org/}}. In other words, different processes are able to communicate with each
 other without any central bus. This is convenient as fewer processes are needed for the system to function. Lowering the number of overall processes lowers the
@@
 \section{Experimental Results}
+\label{sec:iBEMS-Experimental Results}
 The system was tested with a working prototype, in which the first mode is the startup menu:
@@
 
-% There are five general modes of operation in iBEMS shown in Fig.~\ref{fig:operationalModes}.
-In Mode 0, before iBEMS is even launched, the user must open the Startup Menu, which is a desktop graphical user interface (GUI).
-This is a simple GUI with only 2 buttons for starting and stopping iBEMS.
-Upon clicking \say{Start iBEMS}, the login page will load where the user can enter a valid username and password to use iBEMS.
-Once a valid username and password is entered, the home screen will be shown which displays the weather data being downloaded from the OpenWeatherMap API.
-This information includes temperature in Fahrenheit and Celsius, wind speed in MPH, humidity, and cloud coverage.
-At this point, a navigation bar is available to view the \say{Active Devices} page and the \say{Scheduling} page.
-\say{Active Devices} corresponds to Mode 3 for controlling devices in real time.
-The user will also be able to view power plots in this mode as well.
-Lastly, the \say{Scheduling} page is Mode 4 for creating schedules for all connected devices.
-
-% \begin{figure}
-%   \centering
-%   \includegraphics[scale=0.4]{figs/operationalModes.pdf}
-%   \caption{Operation Modes Interaction}
-%   \label{fig:operationalModes}
-% \end{figure}
-
-% \section{Hardware}
-
-% A large feature of this project was being able to record power usage from the
-% connected IoT devices. The embedded computer does not have a built-in capability
-% to measure its own power usage, so a circuit was needed to make that
-% possible. Essentially, this circuit will measure the current being used to drive
-% one of the motors on the robot chassis. The on-board Analog-to-Digital-Converter
-% (ADC) can be used to read the voltage across the resistor and since the
-% resistance is known, the current can be calculated as $I = V/R$. Also, the
-% voltage from the H-Bridge to drive the motors on the embedded computer is known
-% so the power consumed by 1 motor is $Motor Drive Voltage * I$. For the specific
-% robot chassis used in this project, there are 4 motors, so multiplying the power
-% found from this circuit by 4 will give an approximation of the total power used
-% by the robot. See Figure~\ref{fig:motorInterfaceCircuit} for details of the interface
-% circuit for computer power usage by the DC motor. Also see Figure~\ref{fig:bb_connections} for how the circuit is connected to the embedded computer and robot chassis.
-
-% \begin{figure}[H]
-%   \centering
-%   \begin{circuitikz}[american]
-%     \tikzstyle{every node} = [font = \tiny]
-%     % \usetikzlibrary{patterns}
-%     \draw
-%     (0,0) to[sqV,invert,l=Motor Drive Voltage from H-Bridge] ++(0,4*\smgrid)
-%     to[Telmech=M,n=motor,fill=red!20] ++(4*\smgrid,0)
-%     to[C,l=$1~{[}\mu F{]}$,*-*] ++(0,-4*\smgrid) to[short]++(-4*\smgrid,0); 
-%     \draw
-%     (4*\smgrid,4*\smgrid) to[short,-*]++(3*\smgrid,0)
-%     to[short,-o]++(2*\smgrid,0)node[right]{Embedded Computer ADC (Ch\#0)};
-%     \draw
-%     (7*\smgrid,4*\smgrid) to[R,l=$2~{[}\Omega{]}$,-*]++(0,-4*\smgrid)
-%     to[short]++(-4*\smgrid,0);
-%     \draw
-%     (7*\smgrid,0) to[short,-o]++(2*\smgrid,0) node[right]{Embedded
-%       Computer ADC (Ground)};
-%   \end{circuitikz}
-%   \caption{Interface circuit to calculate power consumption of a DC motor
-%     running from the embedded computer copmuter.}
-%   \label{fig:motorInterfaceCircuit}
-% \end{figure}
-
-% \begin{figure}[H]
-%     \centering
-%     \includegraphics[scale=0.6]{figs/beaglebone/connections.pdf}
-%     \caption{Connections between Embedded Computer, circuit, and robot chassis}
-%     \label{fig:bb_connections}
-% \end{figure}
-
-% % \pagebreak
-% \begin{figure}[H]
-%     \centering
-%     \includegraphics[scale=0.07]{figs/beaglebone/notConnectedSBC.jpg}
-%     \caption{Embedded Computer Not Connected}
-%     \label{fig:not_connected_bb}
-% \end{figure}
-
-% Figure~\ref{fig:not_connected_bb} shows the embedded computer mounted on the robot chassis with the circuit shown on page 9.
-It can also be seen that the embedded computer lights up the on-board red LED when disconnected.
-Figure~\ref{fig:connected_bb} shows that the embedded computer lights up the green LED when it is connected as an extra indication of its connection status.
-
-% \begin{figure}[H]
-%     \centering
-%     \includegraphics[scale=0.07]{figs/beaglebone/connectedSBC.jpg}
-%     \caption{Embedded Computer Connected}
-%     \label{fig:connected_bb}
-% \end{figure}
-
-% \begin{figure}[H]
-%     \centering
-%     \includegraphics[scale=0.07]{figs/wemo/wemoView.jpg}
-%     \caption{WeMo Insight Smart Plug}
-%     \label{fig:wemo}
-% \end{figure}
-
-% The other supported device is the WeMo Insight Switch as seen in Figure~\ref{fig:wemo}.
-This device was easy to develop support for as it is meant for building energy management.
-It simply plugs into a 120 volt 3-prong outlet and any typical household appliance running on 120 volts can be plugged into it.
-Internal circuitry allows the WeMo to be controlled remotely (turn On/Off) and to record power usage of whatever it is plugged into.
-
-% \begin{figure}[H]
-%     \centering
-%     \includegraphics[scale=0.07]{figs/overallView.jpg}
-%     \caption{Overall View}
-%     \label{fig:overallView}
-% \end{figure}
-
-% In order to test these devices, we plugged a bank of 6 light bulbs into the WeMo
-% Insight Switch as seen in Figure~\ref{fig:overallView}. The embedded computer's
-% functionality was tested with the circuit and robot chassis described earlier.
-
 \bibliographystyle{IEEEtran}

### 2021-07-19 paper1-IEEE-ROSE-2021.tex
Complete paper

@@
   technology. Numerous building energy management systems are commercially
-  available in the market. Most of them lack modularity or are driven by an
+  available in the market. Among the major shortcomings of most of the existing building energy management systems are that, they either lack modularity or are driven by an
   overwhelming degree of manual configurations for performing building
   automation.
-In this paper, we present the development of a modular IoT-based framework for an intelligent building energy management system (iBEMS).
-The proposed framework is open-source and leverages the features of decentralized multi-agent systems.
-The principal component of the framework is the BEMS core that implements building automation features, such as an optimal scheduler, displaying weather information, detecting new IoT devices, monitoring energy consumption, and remotely controlling operation of IoT devices.
+
+  In this paper, we present the development of a modular IoT-based
+  framework for an intelligent building energy management system (iBEMS). The
+  proposed framework is open-source and leverages the features of decentralized
+  multi-agent systems. The principal component of the framework is the BEMS core
+  that implements building automation features, such as an optimal scheduler,
+  displaying weather information, detecting new IoT devices, monitoring energy
+  consumption, and remotely controlling operation of IoT devices.
+We developed and configured two IoT devices (WeMo switch and embedded mobile robot) that are supported with the the proposed intelligent building energy management platform.
+The iBEMS is tested in a laboratory environment.
+The performance of the proposed iBEMS is backed up by a set of experimental results.
 
@@
     \centering
-    \includegraphics[scale=0.3]{figs/agents/setDeviceStatus.pdf}
+    \includegraphics[scale=0.2]{figs/agents/setDeviceStatus.pdf}
     \caption{setDeviceStatus Flow Chart}
@@
     \centering
-    \includegraphics[scale=0.4]{figs/agents/getDeviceStatus.pdf}
+    \includegraphics[scale=0.3]{figs/agents/getDeviceStatus.pdf}
     \caption{getDeviceStatus Flow Chart}
@@
     \centering
-    \includegraphics[scale=0.4]{figs/agents/periodicQueryBehavior.pdf}
+    \includegraphics[scale=0.3]{figs/agents/periodicQueryBehavior.pdf}
     \caption{periodicQueryBehavior Flow Chart}
@@
     \centering
-    \includegraphics[scale=0.3]{figs/agents/updateScheduleFromServer.pdf}
+    \includegraphics[scale=0.2]{figs/agents/updateScheduleFromServer.pdf}
     \caption{updateScheduleFromServer Flow Chart}
@@
     \centering
-    \includegraphics[scale=0.3]{figs/agents/periodicDeviceUpdateMethod.pdf}
+    \includegraphics[scale=0.2]{figs/agents/periodicDeviceUpdateMethod.pdf}
     \caption{periodicDeviceUpdateMethod Flow Chart}
@@
     \centering
-    \includegraphics[scale=0.25]{figs/beaglebone/Beaglebone_Receiver_Diagram.pdf}
+    \includegraphics[scale=0.2]{figs/beaglebone/Beaglebone_Receiver_Diagram.pdf}
     \caption{Receiver Running on Embedded Computer}
@@
     \centering
-    \includegraphics[scale=0.5]{figs/GUI/BEMS_GUI_Linux_Warning.png}
+    \includegraphics[scale=0.3]{figs/GUI/BEMS_GUI_Linux_Warning.png}
     \caption{Popup Error}
@@
     \centering
-    \includegraphics[scale=0.3]{figs/webServer/Login.png}
+    \includegraphics[scale=0.2]{figs/webServer/Login.png}
     \caption{Login Page}
@@
 
+\section{Conclusion and Future Work}
+\label{sec:conclusion}
+
+We have presented a platform of an intelligent building energy management system,
+which is open source, and easy-to-use.
+It is also developed using a modular, agent-based code base.
+Being open source makes it freely available to anyone who has the supported devices and wants to begin managing their home energy usage.
+The simple interface is easy to figure out for less tech-savvy users and the modular code base makes this system relatively easy for others to continue development.
+Despite its advantages, potential users are to be aware of the rather obvious disadvantages at this point.
+A typical commercial building energy management system will include many more features like predicting future energy use and supporting more devices.
+
+One of the main ways to improve the software is to refactor the user interface as the current interface is fairly primitive.
+Adding elements like collapsible drop down menus and a collapsible side bar would make the interface more professional and user-friendly.
+To improve the overall reliability and speed of the software, a better agent communication protocol could be researched and implemented.
+Many problems are visible with the use of ZeroMQ as exceptions are thrown occasionally when device status updates are sent in quick succession to the control agent.
+Potentially, there exists a better solution than publish-subscribe.
+One of the major issues with the software is lack of device data persistence across system restarts.
+Developers in the future could help alleviate this problem by refactoring the device storage system in the Cassandra database.
+
 \bibliographystyle{IEEEtran}

### 2021-07-19 paperIEEE-IECON2021.tex
Paper submitted to IEEE IECON 2021

--- 2021-07-19 paper1-IEEE-ROSE-2021.tex
@@
 \begin{IEEEkeywords}
-  mobile robots, navigation, radio frequency identification, robotic cart 
+  Building energy management, embedded computer, internet of things, multi-agent systems, smart plug,  web server
 \end{IEEEkeywords}
@@
 platform and control them.
-
-% The previous senior project group worked on creating a remote motor control system with a Raspberry Pi and XBee module.
-To supply power directly to the motor and XBee with a single power supply, they used a buck-boost converter capable of stepping down power supply voltage to 3.3 V.
-They implemented a Python script that uses the Linux command \texttt{nmap} to search for the Raspberry Pi on the network.
-The Raspberry Pi connects to the transmitter XBee via a serial connection to transmit commands to the receiver XBee mounted to the motor.
-They were able to simply toggle the motor on and off and partially implemented this functionality in BEMOSS (Building Energy Management Open Source Software).
-A second portion of their project was implementing an HVAC control algorithm capable of controlling the temperature of a home with the Linear Quadratic Regulator control algorithm.
-
-% During a research project led by Miah \textit{et al.,} the DC motor interface was successfully
-% implemented into the BEMOSS platform which required adding a great deal of source code
-% to the platform to fully implement the device as BEMOSS does not support adding
-% new devices currently. The research also consisted of adding new
-% features such as a logo to the
-% platform for the motor. A possible improvement our platform will make is helping
-% developers on the project add new devices more easily.
-
-% One of the improvements our project makes over the previous is the use of UDP (user datagram protocol) multicasting which does not require any superuser privileges to locate an
-% embedded computer (Beaglebone Blue, for example). This implementation is also more convenient
-% because it does not require installing any packages as multicasting is natively
-% supported by most embedded Linux systems. If in the future, multiple embedded
-% computers are needed to be discovered, the multicasting system works elegantly
-% as each device can simply listen on a provided multicast group which consists of
-% an IP address and port number.
 
@@
   \centering
-  \includegraphics[scale=0.15]{figs/functionalBlockDiagram.pdf}
+  \includegraphics[scale=0.3]{figs/functionalBlockDiagram.pdf}
   \caption{Functional Block Diagram}
@@
   \centering
-  \includegraphics[scale=0.15]{figs/overallDiagram.pdf}
+  \includegraphics[scale=0.3]{figs/overallDiagram.pdf}
   \caption{Interconnection between system components}
@@
 \end{table}
+%
 The agents contained in the software are associated with a Python class of the
@@
 to the WiFi network. %
-
+%
 \begin{figure}[htbp]
@@
 \end{figure}
-
+%
 To obtain necessary data quantities from the device, the
@@
 \end{figure}
-
+%
 Every device connected to iBEMS will have a thread associated with it started from the control agent.
@@
 Lastly, all the scheduling periods extracted from the dictionary are stored as rows in the table.
+%
+%
 \begin{figure}[htbp]
     \centering
-    \includegraphics[scale=0.2]{figs/agents/updateScheduleFromServer.pdf}
+    \includegraphics[scale=0.3]{figs/agents/updateScheduleFromServer.pdf}
     \caption{updateScheduleFromServer Flow Chart}
@@
 \end{figure}
+%
 A second method that is run inside each device thread is \texttt{periodicDeviceUpdateMethod}, defined in Figure~\ref{fig:periodicDeviceUpdateMethod}, which is started when the discovery agent sets the discovered device to active.
@@
 If the current time does lie inside the scheduling period, the device's state is set dependent on the API.
+%
+%
 \begin{figure}[htbp]
@@
 \end{figure}
+%
 

### 2021-09-18 paperIEEE-IECON2021.tex
Moved architecture paragraph to implementation, added note about scalability

@@
 with multiple peripherals including IoT devices and a weather API over the
-internet. In this work, we developed the iBEMS to support for two 
-IoT devices displayed in the high-level architecture shown in Fig.~\ref{fig:highLevelArchitecture}. %
+internet. In this work, we developed the iBEMS to support two IoT devices displayed in the high-level architecture shown in Fig.~\ref{fig:highLevelArchitecture}. %
 %
@@
 Blue.  The core is also able to
-connect the internet to download weather data for a local city through
+connect to the internet to download weather data for a local city through
 OpenWeatherMap. Fig.~\ref{fig:functional_bd} gives the lower level functional block diagram of the system
@@
 
+Fig.~\ref{fig:systemComponentInterconnection} provides an explanation of how
+the components of the system interact with each other. %
+%
+\begin{figure}
+  \centering
+  \includegraphics[scale=0.3]{figs/overallDiagram.pdf}
+  \caption{Interconnection between system components}
+  \label{fig:systemComponentInterconnection}
+\end{figure}
+%
+The Apache Cassandra database and SQLite database are accessible from the web server, control agent, discovery agent, and scheduling agent.
+The web server queries the time series database and metadata database for vastly different purposes.
+Power plotting requires querying the Apache Cassandra database.
+To distinguish between the different devices on the front end, the metadata database is used.
+The agents utilize the Apache Cassandra database for storing and extracting time-series data.
+The agents use the metadata database to distinguish between different devices.
+
+\section{Software Implementation}
+\label{sec:SoftwareImplementation}
 The Flask web server is built using a Python web framework titled Flask which
@@
 match the defined status in the Apache Cassandra database.
-
-Fig.~\ref{fig:systemComponentInterconnection} provides an explanation of how
-the components of the system interact with each other. %
-%
-\begin{figure}
-  \centering
-  \includegraphics[scale=0.3]{figs/overallDiagram.pdf}
-  \caption{Interconnection between system components}
-  \label{fig:systemComponentInterconnection}
-\end{figure}
-%
-The Apache Cassandra database and SQLite database are accessible from the web server, control agent, discovery agent, and scheduling agent.
-The web server queries the time series database and metadata database for vastly different purposes.
-Power plotting requires querying the Apache Cassandra database.
-To distinguish between the different devices on the front end, the metadata database is used.
-The agents utilize the Apache Cassandra database for storing and extracting time-series data.
-The agents use the metadata database to distinguish between different devices.
-
-\section{Software Implementation}
-\label{sec:SoftwareImplementation}
 
@@
 Many problems are visible with the use of ZeroMQ as exceptions are thrown occasionally when device status updates are sent in quick succession to the control agent.
+Scalability is another issue that comes to mind as users will undoubtedly want to connect more than two devices.
 Potentially, there exists a better solution than publish-subscribe.

### 2021-09-24 paperIEEE-IECON2021.tex
Changed case of agents in paper

@@
 better suited for the time series data such as device status and power usage.
-This database was therefore utilized a lot by the Control and Scheduling Agents.
+This database was therefore utilized a lot by the control and scheduling agents.
 The SQLite database hold parameters that do not change over time like device
-ID's, IP addresses, and MAC addresses which made it amendable to the processes
-in the Discovery Agent. The first agent that is
+ID's, IP (Internet Protocol) addresses, and MAC addresses which made it amendable to the processes
+in the discovery agent. The first agent that is
 used by the iBEMS Core on startup is the discovery agent. It is responsible for
@@
 support for. This process involves retrieving the following parameters: IP
-address, Port number, MAC address, Manufacturer, Name, and API. Once all
-available devices are connected, the Control agent is used to change the status
+address, Port number, MAC address, Manufacturer, Name, and API.
+The discovery agent accomplishes this by cycling through all the API modules and calls the corresponding discovery method.
+IP multicasting via UDP (User Datagram Protocol) is used for finding all devices that respond to a specific multicast group and port.
+The device's local IP address can be obtained from the response and stored in the metadata database which can allow the system to obtain information from the device later on.
+Once all
+available devices are connected, the control agent is used to change the status
 of each device and collect power usage data in real time. Finally, the

### 2021-09-28 paperIEEE-IECON2021.tex
Added a few references in the paperIEEE-IECON2021.tex

@@
 The Internet of Things (IoT) is a large network of embedded devices such as sensors, wearables, and appliances capable of receiving control commands and reporting
-data over the Internet. Many industries take advantage of this infrastructure to
+data over the Internet~\cite{Ozadowicz2015,Dagdougui2019}. Many industries take advantage of this infrastructure to
 improve process flow and efficiency. One of these industries is the commercial
@@
 systems to help better manage processes or devices in a building like air
-conditioning systems, lights or industrial machines. Technological advancements
+conditioning systems, lights or industrial machines~\cite{Yang2015}. Technological advancements
 have allowed devices to become connected to a building network through
 communication protocols like WiFi, Ethernet, Modbus, or BACnet which enables
-them to be more easily controlled from a central system.
+them to be more easily controlled from a central system. Such technological
+advancements yield energy efficiency, demand management, and IoT data processing for intelligent building energy management promising~\cite{Yang2015,Reddy2019,Lee2019}.
 
